---
title: "Intervention"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-11"
author: ""

---

# ReadMe

- This is the analysis script for the CC vs CO Intervention study.  
- Date run: 11/11/25
- N = 105 before exclusions
- 2 between-subjects conditions
- DV: What would you to make someone x? (CC Intervention), what spell would you cast to give creature capacity x (CO Intervention), IV: Binary choice between CC vs CO item   
- Hypothesis: subjects choose CC item for CC interventions, and CO item for CO interventions

# Setup

## Load packages

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects,  
               gt,
               webshot2,
               knitr,
               performance,
               effectsize,
               tidyverse,
               simr,
               conflicted)
sessionInfo()

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), 
     ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)

```

## Global variables

```{r}
base_path <- here("code")

snapshots_item_selection_path <- paste0(base_path,
                                        "/analysis/1.5_item_selection/snapshots_experiment1_combined_analysis")
preceding_distances_path <- paste0(snapshots_item_selection_path,
                                   "/preceding_short_list.csv")
following_distances_path <- paste0(snapshots_item_selection_path,
                                   "/following_short_list.csv")

```

# Confirmatory Analysis - Prep

The main confirmatory analysis asks what proportion of subjects select the CC vs CO item in each condition. 

## Read data

```{r, warnings = FALSE}
data_path_cf <- paste0(base_path, "/data/5_magical_v_ordinary_intervention/JO-mbc-main-v2_intervention-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_cf, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    rename(
      CC_item = causal_itemA,
      CO_item = similar_itemA,
      selected_item = selected_choice
    ) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## Wrangle data

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_item) %>%
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()

dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% #exclude 1 subject who failed attn check
  filter(condition %in% c("ordinary", "magical")) %>%
  # mutate(condition = ifelse(condition == "ordinary", "CC", "CO")) %>%
  mutate(condition = ifelse(condition == "ordinary", "Ordinary", "Magical")) %>%
  mutate(response = ifelse(response == "causal", "CC", "CO")) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(CC_item, selected_item) ~ "CC",
    grepl(CO_item, selected_item) ~ "CO",
    TRUE ~ "other"
  )) %>% 
  mutate(response = as.factor(response)) %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  ungroup() %>% 
  select(subject_id, condition, itemB, CC_item, CO_item, response) %>% 
  mutate(CC_item = factor(CC_item, levels = desired_order),
         CO_item = factor(CO_item, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", 
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "body", 
                                 itemB == "become hungry" ~ "body",
                                 itemB == "feel scared"~ "body",
                                 itemB == "experience pain"~ "body",
                                 itemB == "get sick"~ "body"),
         domain_CC_item = case_when(CC_item == "hear something" ~ "mind", 
                                 CC_item == "choose what to do" ~ "mind",
                                 CC_item == "remember something" ~ "mind",
                                 CC_item == "think about something" ~ "mind",
                                 CC_item == "see something" ~ "mind",
                                 CC_item == "reach for something" ~ "action",
                                 CC_item == "sit down" ~ "action", 
                                 CC_item == "jump up and down" ~ "action",
                                 CC_item == "kick something" ~ "action",
                                 CC_item == "take a walk" ~ "action",
                                 CC_item == "get tired" ~ "body", 
                                 CC_item == "become hungry" ~ "body",
                                 CC_item == "feel scared"~ "body",
                                 CC_item == "experience pain"~ "body",
                                 CC_item == "get sick"~ "body"),
          domain_CO_item = case_when(CO_item == "hear something" ~ "mind", 
                                 CO_item == "choose what to do" ~ "mind",
                                 CO_item == "remember something" ~ "mind",
                                 CO_item == "think about something" ~ "mind",
                                 CO_item == "see something" ~ "mind",
                                 CO_item == "reach for something" ~ "action",
                                 CO_item == "sit down" ~ "action", 
                                 CO_item == "jump up and down" ~ "action",
                                 CO_item == "kick something" ~ "action",
                                 CO_item == "take a walk" ~ "action",
                                 CO_item == "get tired" ~ "body", 
                                 CO_item == "become hungry" ~ "body",
                                 CO_item == "feel scared"~ "body",
                                 CO_item == "experience pain"~ "body",
                                 CO_item == "get sick"~ "body")) 

rmarkdown::paged_table(dat)

```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

paste0("pre-exclusion N: ", d %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
summary(df_demographics$filename)
summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Summarize data

```{r}
# Condition-level summary, with cis 
dat_summarized_conditions <- dat %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se))

rmarkdown::paged_table(dat_summarized_conditions)

# Trial-level summary
dat_summarized_trials <- dat %>%
  tidyr::complete(response, nesting(condition, itemB, 
                                    CC_item, CO_item,
                                    domain_CC_item, domain_CO_item,
                                    domain_itemB), fill = list(count = 0)) %>% 
  group_by(condition, itemB) %>%
  mutate(total = n()) %>%  
  ungroup() %>% 
  group_by(condition, itemB, response) %>%
  mutate(
    count = n(),  
    total = first(total),  
    mean_proportion = count / total,
    se = sqrt(mean_proportion * (1 - mean_proportion) / total)) %>%
  distinct(condition, itemB, .keep_all = TRUE) %>%
  select(-subject_id) %>%
  ungroup() 

rmarkdown::paged_table(dat_summarized_trials)

```

# Confirmatory Analysis - Figures

## Figure with slope 

Black and white

```{r, fig.width = 3, fig.height = 5}
fig_slope <- dat_summarized_conditions %>%
  mutate(response = fct_relevel(response, "CC", "CO")) %>% 
  mutate(condition = fct_relevel(condition, c("Magical", "Ordinary"))) %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  geom_errorbar(data = filter(dat_summarized_conditions, response == "CO"),
              aes(ymax = ci_high,
                  ymin = ci_low,
                  width = 0.3)) +
  geom_point(
      data = dplyr::filter(dat_summarized_trials, response == "CO"),
    aes(group = interaction(itemB, response),
        fill = response),
             alpha = 0.8, 
             size = 5,
             shape = 21,
             color = "black") +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_line(
    data = dplyr::filter(dat_summarized_trials, response == "CO"),
    aes(group = interaction(itemB, response)),
    alpha = 0.4, color = "black"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_cowplot() +
  labs(y = "Proportion", x = "Condition", fill = "Response") +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    legend.text = element_text(size = 25),
    panel.background = element_rect(fill='transparent', color=NA),
    plot.background = element_rect(fill='transparent', color=NA)
  )

fig_slope

fig_slope <- ggsave("figures/intervention_slope_black_and_white.png", width = 3.5, height = 6, plot = fig_slope, bg = "white")

```

## Item-level with distances

```{r, fig.width = 12, fig.height = 12}
d_distances <- read_csv(preceding_distances_path)

dat_labels <- dat_summarized_trials %>%
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  distinct(itemB, CC_item, CO_item) %>% 
  left_join(d_distances %>%
              rename(itemB = target_item),
            by = c("itemB", "CC_item", "CO_item")) %>%
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(freesort_minus_causal_pairs_distance_CO = 
           round(freesort_minus_causal_pairs_distance_CO, 2),
         freesort_minus_causal_pairs_distance_CC = 
           round(freesort_minus_causal_pairs_distance_CC, 2)) %>% 
  mutate(facet_label = paste0(
    itemB, "\n",
    "", CC_item, "\n", 
    "", CO_item   
  )) %>% 
  mutate(facet_label = paste0(itemB, "\n",
                              "CC: ", CC_item, "\n",
                              "cd,fd,f-c: (",
                              causal_pairs_distance_CC_item, ",",
                              freesort_distance_CC_item, ",",
                              freesort_minus_causal_pairs_distance_CC, ")", "\n",  
                              "CO: ", CO_item, "\n",
                              "cd,fd,f-c: (",
                              causal_pairs_distance_CO_item, ",",
                              freesort_distance_CO_item, ",",
                              freesort_minus_causal_pairs_distance_CO, ")", "\n"))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

dat_summarized_by_item_levels <- dat_summarized_trials %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>% 
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_intervention <-  dat_summarized_by_item_levels %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity") +
  geom_bar(stat = "identity", colour = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_errorbar(data = filter(dat_summarized_by_item_levels, response == "CC"), 
                aes(ymax = mean_proportion + se,
                    ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        # legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 25),
        strip.text = element_text(size = 15)) +
  labs(y = "Proportion (CC)",
       title = "Intervention") +
  facet_wrap(~facet_label, nrow = 3)

p_intervention

# ggsave(
#   filename = "figures/p_intervention_item-level_stacked.pdf",
#   plot = p_intervention,          
#   device = "pdf",           
#   width = 20,               
#   height = 15,             
#   units = "in")
# 
# ggsave(
#   filename = "figures/p_intervention_item-level_stacked.png",
#   plot = p_intervention,  
#   bg = "white",
#   width = 20,               
#   height = 15,             
#   units = "in")

```

# Confirmatory Analysis - Analysis

## Logistic regression

```{r}
d_model <- dat %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  mutate(condition = factor(condition, levels = c("Magical", "Ordinary")))

model_effect_of_intervention <- glmer(response ~ condition + 
                                        (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_effect_of_intervention)

std_parameters <- standardize_parameters(model_effect_of_intervention, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_effect_of_intervention)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Ordinary-only model

```{r}
d_ordinary <- d_model %>% 
  mutate(subject_id = factor(subject_id)) %>% 
  filter(condition == "Ordinary") %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) 

model_effect_of_ordinary <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_ordinary)

summary(model_effect_of_ordinary)
paste0("probability: ", plogis(fixef(model_effect_of_ordinary)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_ordinary)[1]))

```

## Magical-only model

```{r}
d_magical <- d_model %>% 
  mutate(subject_id = factor(subject_id)) %>% 
  filter(condition == "Magical") %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) 

model_effect_of_magical <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_magical)

summary(model_effect_of_magical)
paste0("probability: ", plogis(fixef(model_effect_of_magical)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_magical)[1]))

```

# Exploratory Analysis - Prep

The exploratory distance analysis asks whether we can use the quantitative distances to explain variation in effect sizes across trials.  

## Append distances

```{r}
distances <- read_csv(preceding_distances_path)
``` 

## Merge and save distances

```{r}
dat_distances_intervention <- dat %>% 
  left_join(distances %>%
              rename(itemB = target_item),
            by = c("itemB", "CC_item", "CO_item")) %>% 
  mutate(causal_pairs_distance_CC_item = round(causal_pairs_distance_CC_item, 2),
         freesort_distance_CC_item = round(freesort_distance_CC_item, 2),
         freesort_minus_causal_pairs_distance_CC = round(freesort_minus_causal_pairs_distance_CC, 2),
         causal_pairs_distance_CO_item = round(causal_pairs_distance_CO_item, 2),
         freesort_distance_CO_item = round(freesort_distance_CO_item, 2),
         freesort_minus_causal_pairs_distance_CO = round(freesort_minus_causal_pairs_distance_CO, 2))

rmarkdown::paged_table(dat_distances_intervention)

write_csv(dat_distances_intervention, "dat_intervention_distances.csv")

```

## Read back in distances

```{r}
analysis_path <- here("code", "analysis")

dat_distances_intervention <- read_csv(paste0(analysis_path,
                "/5_magical_v_ordinary_intervention/dat_intervention_distances.csv")) 

```

# Exploratory Analysis - Figures

## Ordinary condition

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

dat_distances_wrangled <- dat_distances_intervention %>% 
  unite("joined", c(itemB, CC_item, CO_item), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response, freesort_minus_causal_pairs_distance_CC,
           freesort_minus_causal_pairs_distance_CO) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_pairs_distance_CC - freesort_minus_causal_pairs_distance_CO) %>% 
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

dat_distances_ordinary <- dat_distances_wrangled %>% 
  filter(condition == "Ordinary") %>% 
  filter(response == "CC")  %>% 
  separate(joined, into = c("itemB", "CC_item", "CO_item"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "CC: ", CC_item, "\n", "CO: ", CO_item))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    CC_item   = recode(CC_item, !!!short_names),
    CO_item  = recode(CO_item, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "CC: ", 
                         CC_item, "\n", "CO: ",
                         CO_item))  

fig_ordinary_distance <- dat_distances_ordinary %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  # geom_text(aes(label = labels), size = 3, vjust = 1.3) + #uncomment to see labels
  theme_bw() +
  labs(
      title = "Ordinary Condition",
      x = "CC more causally relevant →\nCO item more CO-relevant →",
       y = "Proportion (CC)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25, hjust = .5),
        # plot.title = element_text(hjust = .5, size = 25),
        plot.title = element_blank(),
        legend.position = "none") 

fig_ordinary_distance 

fig_ordinary_distance <- ggsave("figures/ordinary_distances.png", width = 6, height = 4.5, 
                        plot = fig_ordinary_distance, bg = "white")

```

## Magical condition

```{r}
dat_distances_magical <- dat_distances_wrangled %>% 
  filter(condition == "Magical") %>% 
  filter(response == "CC")  %>% 
  separate(joined, into = c("itemB", "CC_item", "CO_item"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "CC: ", CC_item, "\n", "CO: ", CO_item))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    CC_item   = recode(CC_item, !!!short_names),
    CO_item  = recode(CO_item, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "CC: ", CC_item, "\n", "CO: ",
                         CO_item))  

fig_magical_distance <- dat_distances_magical %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_bw() +
  labs(
      title = "Magical Condition",
      x = "CC more causally relevant →\nCO item more CO-relevant →",
      y = "Proportion (CC)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25, hjust = .5),
        # plot.title = element_text(hjust = .5, size = 25),
        plot.title = element_blank(),
        legend.position = "none")
 
fig_magical_distance

fig_magical_distance <- ggsave("figures/magical_distances.png", width = 6, height = 4.5, 
                        plot = fig_magical_distance, bg = "white")

```

# Exploratory Analysis - Analysis

## Prepare for modelling

```{r}
dat_distances_intervention_model <- dat_distances_intervention %>% 
  mutate(joint_distance_difference = freesort_minus_causal_pairs_distance_CC -
           freesort_minus_causal_pairs_distance_CO) %>% 
  mutate(response = factor(response, levels = c("CO", "CC"))) %>% 
  mutate(condition = factor(condition, levels = c("Ordinary", "Magical"))) %>% 
  mutate(subject_id = as.factor(subject_id)) 

```

## Ordinary condition

```{r}
model_ordinary_distances <- glmer(response ~ joint_distance_difference + 
                                  (1 | subject_id), 
    data = dat_distances_intervention_model %>% 
      filter(condition == "Ordinary") %>% 
      mutate(response = fct_relevel(response, c("CO", "CC"))),
    family = binomial(link = 'logit'))

summary(model_ordinary_distances)

std_parameters <- standardize_parameters(model_ordinary_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Magical condition

```{r}
model_magical_distances <- glmer(response ~ joint_distance_difference + (1 | subject_id), 
    data = dat_distances_intervention_model %>% 
      filter(condition == "Magical") %>% 
      mutate(response = fct_relevel(response, c("CO", "CC"))),
    family = binomial(link = 'logit'))

summary(model_magical_distances)

std_parameters <- standardize_parameters(model_magical_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

# THE END

```{r}

```







