---
title: "Explanation"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-19"
author: ""

---

# ReadMe

This is the analysis script for the Explanations study.  
N = 105 (before exclusions).  
The independent variable is whether the explanation provided for a target event is a Direct or Intrinsic item (within-subjects).  
The dependent variable is how satisfactory the explanation is, ranging from not at all (0) to extremely satisfying (100). 

# Setup

## Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               gt,
               webshot2,
               knitr,
               performance,
               effectsize,
               simr,
               conflicted,
               tidyverse)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code", "main")
freesort_and_causal_distances_df_path <- paste0(base_path,
                                                "/analysis/measure-main-and-pilot/snapshots_study1_main_analysis/freesort_minus_causals.csv")

short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

```


# Prepare data

## Read data

```{r}
data_path_ex <- paste0(base_path, "/data/explanation/JO-mbc-main-explanation-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_ex, pattern = "^2025-", full.names = TRUE)

d_ex <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## Wrangle data

```{r}
subjects_to_exclude_ex <- d_ex %>%
  filter(grepl("attention_check", condition)) %>% 
  filter(attn_correct == "no") %>% 
  pull(subject_id) %>% 
  unique()

paste("subjects excluded: ", length(subjects_to_exclude_ex))
paste(subjects_to_exclude_ex, collapse = ", ")

dat_ex <- d_ex %>% 
  filter(condition %in% c("causal", "similar")) %>%
  filter(!subject_id %in% subjects_to_exclude_ex) %>% #exclude 1 subject who failed attn check
  mutate(response = as.numeric(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  select(-condition) %>% 
  select(subject_id, itemB, causal_itemA, similar_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(item_type = case_when(
        !is.na(causal_itemA) ~ "causal_itemA",
        !is.na(similar_itemA) ~ "similar_itemA"),
        item = coalesce(as.character(causal_itemA), as.character(similar_itemA))) %>% 
  select(-causal_itemA, -similar_itemA) %>% 
  pivot_wider(names_from = item_type,
              values_from = c(item, response)) %>% 
  rename("causal_itemA" = item_causal_itemA,
         "similar_itemA" = item_similar_itemA, 
         "causal_itemA_explanation" = response_causal_itemA,
         "similar_itemA_explanation" = response_similar_itemA) 

rmarkdown::paged_table(dat_ex)

```

## Demographics

```{r}
df_demographics <- d_ex %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("subject_id", "trial_id","feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

```{r}
dat_ex_trials_summarized <- dat_ex_plot %>%
  group_by(itemB, causal_itemA, similar_itemA, explanation_type) %>%
  summarise(
    mean_satisfactory = mean(satisfactory, na.rm = TRUE),
    se_satisfactory = sd(satisfactory, na.rm = TRUE) / sqrt(n_distinct(subject_id)),
    .groups = "drop") %>% 
  mutate(explanation = case_when(
    explanation_type == "Direct" ~ causal_itemA,
    explanation_type == "Intrinsic" ~ similar_itemA)) %>% 
  select(itemB, explanation, explanation_type, mean_satisfactory, se_satisfactory)

rmarkdown::paged_table(dat_ex_trials_summarized)
```

## Summary stats

```{r}
# Raw Long form data
dat_ex_plot <- dat_ex %>% 
  rename("Direct" = causal_itemA_explanation,
         "Intrinsic" = similar_itemA_explanation) %>% 
  pivot_longer(cols = c(Direct, Intrinsic), 
               names_to = "explanation_type",
               values_to = "satisfactory") %>% 
  mutate(explanation_type = factor(explanation_type, levels = c("Direct", "Intrinsic"))) %>% 
  mutate(explanation = case_when(
    explanation_type == "Direct" ~ causal_itemA,
    explanation_type == "Intrinsic" ~ similar_itemA)) %>% 
  select(subject_id, itemB, explanation, explanation_type, satisfactory) %>% 
  arrange(subject_id, itemB)

rmarkdown::paged_table(dat_ex_plot)

# Trial-level summary
dat_ex_trials_summarized <- dat_ex_plot %>%
  group_by(itemB, causal_itemA, similar_itemA, explanation_type) %>%
  summarise(
    mean_satisfactory = mean(satisfactory, na.rm = TRUE),
    se_satisfactory = sd(satisfactory, na.rm = TRUE) / sqrt(n_distinct(subject_id)),
    .groups = "drop") %>% 
  mutate(explanation = case_when(
    explanation_type == "Direct" ~ causal_itemA,
    explanation_type == "Intrinsic" ~ similar_itemA)) %>% 
  select(itemB, explanation, explanation_type, mean_satisfactory, se_satisfactory)

rmarkdown::paged_table(dat_ex_trials_summarized)

# Condition-level
dat_ex_condition_level <- dat_ex %>% 
  rename("Direct" = causal_itemA_explanation,
         "Intrinsic" = similar_itemA_explanation) %>% 
  pivot_longer(cols = c(Direct, Intrinsic), 
               names_to = "explanation_type",
               values_to = "satisfactory") %>% 
  group_by(explanation_type) %>% 
  summarize(mean = mean(satisfactory, na.rm = TRUE),
            sd = sd(satisfactory, na.rm = TRUE))

rmarkdown::paged_table(dat_ex_condition_level)

```


```{r}
dat_items <- dat_ex_trials_summarized %>% 
  distinct(itemB, causal_itemA, similar_itemA) %>% 
  rename("Direct" = causal_itemA,
         "Intrinsic" = similar_itemA) %>% 
  pivot_longer(cols = c(Direct, Intrinsic),
               names_to = "item_type",
               values_to = "item")

dat_numbers <- dat_ex_trials_summarized %>% 
  select(mean_satisfactory, se_satisfactory)

dat_trials_summarized <- cbind(dat_items, dat_numbers)


#==



```


# Figures

## Figure with slope

```{r}
dat_ex_plot_long <- dat_ex_plot %>%
      mutate(causal_itemA = recode(causal_itemA, !!!short_names),
             similar_itemA = recode(similar_itemA, !!!short_names)) %>%
  pivot_longer(cols = c("causal_itemA", "similar_itemA"),
               names_to = "item_type",
               values_to = "item") %>%
  group_by(subject_id, itemB) %>%
  slice(-c(2, 3)) 

label_ex_data <- dat_ex_plot_long %>%
  ungroup() %>% 
  distinct(itemB, explanation_type, item)

dat_ex_trials_summarized %>% 
  ungroup() %>% 
  distinct(itemB, explanation_type, item, mean_satisfactory)

fig_slope <- dat_ex_plot %>% 
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .2) +
  geom_point(data = dat_ex_trials_summarized, 
             aes(x = explanation_type, y = mean_satisfactory), 
             alpha = 0.4, size = 5) +
  # geom_text(aes(label = itemB), data = label_ex_data) +
  geom_text(data = label_ex_data, aes(label = item), 
            y = 
            y = 95, vjust = 1, size = 6) +
  geom_line(data = dat_ex_trials_summarized
            , aes(x = explanation_type, 
                  y = mean_satisfactory, 
                  group = interaction(itemB, causal_itemA, similar_itemA)), 
            alpha = 0.2, color = "black") +
  labs(y = "How Satisfactory?", 
       x = "Explanation Type",
       fill = "Explanation Type") +
  theme_cowplot() +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        # aspect.ratio = 1.5,  #this or fig.width = 3, fig.height = 5 on top of code chunk or specify size in ggsave()
        legend.spacing.x = unit(1, "cm")
        ) +
  ylim(0, 100)

fig_slope

# fig_slope <- ggsave("figures/explanation_slope.png", plot = fig_slope, bg = "white") #no need to specify size because using aspect.ratio in theme()

# fig_slope <- ggsave("figures/explanation_slope_tall.png", width = 3, height = 6, plot = fig_slope, bg = "white")

fig_slope <- ggsave("figures/explanation_slope_tall.png", width = 3, height = 6, plot = fig_slope, bg = "white")


```

## for mbc pbs talk 4/17/26

```{r, fig.height = 12, fig.width = 8}
dat_ex_plot %>% 
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .2) +
  geom_point(data = dat_ex_trials_summarized, 
             aes(x = explanation_type, y = mean_satisfactory), 
             alpha = 0.4, size = 5) +
geom_text(
  data = dat_ex_trials_summarized,
  aes(
    x = explanation_type,
    y = mean_satisfactory,
    label = itemB
  )
) +
  # geom_text(aes(label = itemB), data = item_labels) +
  geom_line(data = dat_ex_trials_summarized
            , aes(x = explanation_type, 
                  y = mean_satisfactory, 
                  group = interaction(itemB, causal_itemA, similar_itemA)), 
            alpha = 0.2, color = "black") +
  labs(y = "How Satisfactory?", 
       x = "Explanation Type",
       fill = "Explanation Type") +
  theme_cowplot() +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        # aspect.ratio = 1.5,  #this or fig.width = 3, fig.height = 5 on top of code chunk or specify size in ggsave()
        legend.spacing.x = unit(1, "cm")
        ) +
  ylim(0, 100)

```

## Figure facet by trial

```{r, fig.width = 12, fig.height = 12}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

# short_names <- factor(short_names, levels = desired_order)

# Wide version fig - short names
dat_ex_plot_long <- dat_ex_plot %>%
      mutate(causal_itemA = recode(causal_itemA, !!!short_names),
             similar_itemA = recode(similar_itemA, !!!short_names)) %>%
  pivot_longer(cols = c("causal_itemA", "similar_itemA"),
               names_to = "item_type",
               values_to = "item") %>%
  group_by(subject_id, itemB) %>%
  slice(-c(2, 3)) 

rmarkdown::paged_table(dat_ex_plot_long)

label_ex_data <- dat_ex_plot_long %>%
  ungroup() %>% 
  distinct(itemB, explanation_type, item)

dat_subject <- dat_ex_plot_long %>%
  group_by(subject_id, itemB, explanation_type) %>%
  summarize(satisfactory = mean(satisfactory, na.rm = TRUE),
            .groups = "drop")

dat_ex_plot_long_wide <- dat_ex_plot_long %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(data = dat_subject, aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = label_ex_data, aes(label = item), 
            y = 95, vjust = 1, size = 6) +
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
  # facet_wrap(~itemB) 
    facet_wrap(~itemB, nrow = 3, ncol = 5)

dat_ex_plot_long_wide

# Wide version fig - compact names
compact_names <- c(
  "see something" = "see\nsomething",
  "hear something" = "hear\nsomething",
  "choose what to do" = "choose",
  "remember something" = "remember\nsomething",
  "think about something" = "think\nabout\nsomething",
  
  "take a walk" = "take\na walk", 
  "jump up and down" = "jump up\nand down",
  "reach for something" = "reach for\nsomething",
  "sit down" = "sit down",
  "kick something" = "kick\nsomething",
  
  "get sick" = "get sick",
  "feel scared" = "feel\nscared",
  "become hungry" = "become\nhungry",
  "experience pain" = "experience\npain",
  "get tired" = "get tired")

dat_ex_plot_long <- dat_ex_plot %>%
      mutate(causal_itemA = recode(causal_itemA, !!!compact_names),
             similar_itemA = recode(similar_itemA, !!!compact_names)) %>% 
      # mutate(causal_itemA = recode(causal_itemA, !!!short_names),
      #        similar_itemA = recode(similar_itemA, !!!short_names)) %>% 
  pivot_longer(cols = c("causal_itemA", "similar_itemA"),
               names_to = "item_type",
               values_to = "item") %>%
  group_by(subject_id, itemB) %>%
  slice(-c(2, 3)) 

label_ex_data <- dat_ex_plot_long %>%
  ungroup() %>% 
  distinct(itemB, explanation_type, item)

dat_subject <- dat_ex_plot_long %>%
  group_by(subject_id, itemB, explanation_type) %>%
  summarize(
    satisfactory = mean(satisfactory, na.rm = TRUE),
    .groups = "drop")

dat_ex_plot_long_wide_compact <- dat_ex_plot_long %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(data = dat_subject, aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = label_ex_data, aes(label = item), 
            y = 95, vjust = 1, size = 6) +
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
  facet_wrap(~itemB) 

dat_ex_plot_long_wide_compact

# Long version fig
dat_ex_plot_long <- dat_ex_plot %>%
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
      mutate(itemB = recode(itemB, !!!short_names), #added this 
             causal_itemA = recode(causal_itemA, !!!short_names),
             similar_itemA = recode(similar_itemA, !!!short_names)) %>% 
  pivot_longer(cols = c("causal_itemA", "similar_itemA"),
               names_to = "item_type",
               values_to = "item") %>%
  group_by(subject_id, itemB) %>%
  slice(-c(2, 3))

label_ex_data <- dat_ex_plot_long %>%
  ungroup() %>% 
  distinct(itemB, explanation_type, item)

dat_subject <- dat_ex_plot_long %>% #collapse into subject_level
  group_by(subject_id, itemB, explanation_type) %>%
  summarize(
    satisfactory = mean(satisfactory, na.rm = TRUE),
    .groups = "drop")

dat_ex_plot_long_long <- dat_ex_plot_long %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_point(data = dat_subject, alpha = 0.1) +
  geom_line(data = dat_subject, aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = label_ex_data, aes(label = item), 
            y = 95, vjust = 1, size = 5) +
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17),
    legend.position = "none",
    strip.text = element_text(size = 16),
    strip.background = element_rect(fill = NA, color = "black"),
    # aspect.ratio = 1.5
    ) +
  facet_wrap(~itemB) 
  
dat_ex_plot_long_long

dat_ex_plot_long_long <- ggsave("figures/explanation_slope_facet_by_trial.png", 
                                width = 10,
                                height = 8,
                    plot = dat_ex_plot_long_long, 
                    bg = "white") 


# fig_slope <- ggsave("figures/counterfactuals_slope.png", 
#                     width = 3, height = 5, plot = fig_slope, bg = "white")
```

## Figure single subject

```{r, fig.width = 12, fig.height = 12}
dat_ex_plot_long %>% 
  filter(subject_id == "subj_01") %>% 
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  geom_col(color = "black") +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_text(aes(label = item), y = 95, vjust = 1, size = 5) +
  scale_fill_manual(values = c("grey80", "white")) +
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_bw() +
  theme(
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        strip.text = element_text(size = 16),
        strip.background = element_rect(fill = NA, color = "black"),
        legend.position = "none") +
  facet_wrap(~itemB)

```

# Distances

## Read distances 

```{r}
distances <- read_csv(freesort_and_causal_distances_df_path)

```

## Append distances 

```{r}
dat_ex_plot_distances <- dat_ex_plot %>% 
  left_join(distances %>% 
              select(itemA, itemB, mean_causal_distance, 
                     mean_freesort_distance, freesort_minus_causal) %>% 
              rename("causal_itemA" = itemA,
                     "causal_itemA_causal_distance" = mean_causal_distance,
                     "causal_itemA_freesort_distance" = mean_freesort_distance,
                     "causal_itemA_freesort_minus_causal" = freesort_minus_causal),
            by = c("itemB", "causal_itemA")) %>% 
  left_join(distances %>% 
              select(itemA, itemB, mean_causal_distance, 
                     mean_freesort_distance, freesort_minus_causal) %>% 
              rename("similar_itemA" = itemA,
                     "similar_itemA_causal_distance" = mean_causal_distance,
                     "similar_itemA_freesort_distance" = mean_freesort_distance,
                     "similar_itemA_freesort_minus_causal" = freesort_minus_causal),
            by = c("itemB", "similar_itemA")) %>% 
  mutate(causal_itemA_causal_distance = round(causal_itemA_causal_distance, 2),
         causal_itemA_freesort_distance = round(causal_itemA_freesort_distance, 2),
         causal_itemA_freesort_minus_causal = round(causal_itemA_freesort_minus_causal, 2),
         similar_itemA_causal_distance = round(similar_itemA_causal_distance, 2),
         similar_itemA_freesort_distance = round(similar_itemA_freesort_distance, 2),
         similar_itemA_freesort_minus_causal = round(similar_itemA_freesort_minus_causal, 2))

rmarkdown::paged_table(dat_ex_plot_distances)

```

## Save joined distances

```{r}
# save 
write_csv(dat_ex_plot_distances, "dat_explanation_distances.csv")

```

## Read back distances

```{r}
analysis_path <- here("code", "main", "analysis")

dat_ex_plot_distances <- read_csv(paste0(analysis_path,
                "/explanation/dat_explanation_distances.csv"))

```

## Summarize data

```{r}
# Trial-level summary
explanation_distances_summarized <- dat_ex_plot_distances %>% 
  group_by(itemB, causal_itemA, similar_itemA, explanation_type) %>% 
  mutate(mean_satisfactory = mean(satisfactory)) %>% 
  mutate(mean_likelihood = round(mean_satisfactory, 2)) %>% 
  distinct(itemB, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(-c(subject_id, satisfactory)) %>% 
  relocate(mean_satisfactory, .after = explanation_type) %>% 
  relocate(causal_itemA_freesort_minus_causal, .after = mean_satisfactory) %>% 
  pivot_wider(names_from = explanation_type,
              values_from = mean_satisfactory) %>% 
  mutate(mean_difference = Direct - Intrinsic) %>% #not using, but just in case
  mutate(joint_distance_difference = causal_itemA_freesort_minus_causal -
           similar_itemA_freesort_minus_causal) #also not using, but doing just in case

rmarkdown::paged_table(explanation_distances_summarized)

```

# Distances - Figure 

## Long form data

```{r}
explanation_distances_summarized_long <- explanation_distances_summarized %>% 
    pivot_longer(cols = c(causal_itemA_freesort_minus_causal,
                          similar_itemA_freesort_minus_causal),
               names_to = "joint_distance_names",
               values_to = "joint_distance_values") %>%
  mutate(satisfactory_values = ifelse(joint_distance_names == "causal_itemA_freesort_minus_causal", Direct, Intrinsic)) %>% 
  mutate(satisfactory_names = ifelse(joint_distance_names == "causal_itemA_freesort_minus_causal", "Direct", "Intrinsic")) 

```

## Figure with joint distances

```{r}
distances_fig <- explanation_distances_summarized_long %>% 
  ggplot(aes(y = satisfactory_values, x = joint_distance_values, color = satisfactory_names)) +
  geom_point(alpha = 0.4, size = 5) +
  geom_smooth(method = "lm") + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 30),
        axis.text.y = element_text(size = 30),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Explanation",
    color = "Choice Item",
    fill = "Choice Item",
    x = "More intrinsically relevant, More directly relevant",
    y = "Satisfactory ratings"
  ) 

distances_fig

distances_fig <- ggsave("figures/explanation_distances.png", width = 5, height = 5, 
                        plot = distances_fig, bg = "white")

```

## Figure with different colors

```{r}

distances_fig_color <- explanation_distances_summarized_long %>% 
  ggplot(aes(y = satisfactory_values, 
             x = joint_distance_values, group = satisfactory_names)) +
  geom_point(aes(fill = satisfactory_names), 
             alpha = 0.4, size = 5, shape = 21, color = "black", stroke = 1.5) +
  geom_smooth(aes(color = satisfactory_names), method = "lm") + 
  scale_color_manual(values = c("gray40", "white")) +
  scale_fill_manual(values = c("gray40", "white")) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 30),
        axis.text.y = element_text(size = 30),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Explanation",
    color = "Choice Item",
    fill = "Choice Item",
    x = "More intrinsically relevant, More directly relevant",
    y = "Satisfactory ratings"
  ) 

distances_fig_color

distances_fig_color <- ggsave("figures/explanation_distances_color.png", width = 5, height = 5, 
                        plot = distances_fig_color, bg = "white")

```


## Figure with trial labels

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired"
)

distances_labels_fig <- explanation_distances_summarized_long %>% 
  mutate(
  itemB         = recode(itemB, !!!short_names),
  causal_itemA   = recode(causal_itemA, !!!short_names),
  similar_itemA  = recode(similar_itemA, !!!short_names)
) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ", similar_itemA)) %>% 
  ggplot(aes(y = satisfactory_values, x = joint_distance_values, color = satisfactory_names)) +
  geom_point(alpha = 0.4) +
  geom_text(aes(label = labels), vjust = -0.5, size = 2) +
  geom_smooth(method = "lm") + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Explanation",
    color = "Choice Item",
    fill = "Choice Item",
    x = "More intrinsically relevant, More directly relevant",
    y = "Satisfactory ratings"
  ) 

distances_labels_fig

distances_labels_fig <- ggsave("figures/explanation_distances_labels.png", width = 5, height = 5, plot = distances_labels_fig, bg = "white")

```

Alt figures to consider: fit a single line instead of 2, plot mean difference on y axis, plot joint distance difference on x axis, plot normalize y axis

# Distances - Analysis

## Wrangle

```{r}
dat_ex_plot_distances_renamed <- dat_ex_plot_distances %>% 
  rename("joint_direct" = causal_itemA_freesort_minus_causal,
         "joint_intrinsic" = similar_itemA_freesort_minus_causal) %>% 
  mutate(subject_id = as_factor(subject_id),
         causal_itemA = as_factor(causal_itemA),
         similar_itemA = as_factor(similar_itemA)) 

rmarkdown::paged_table(dat_ex_plot_distances_renamed)
```

## Run model

```{r}
model_distance <- lmerTest::lmer(satisfactory ~ joint_direct + joint_intrinsic +
                                              (1|subject_id), 
                                 data = dat_ex_plot_distances_renamed)
summary(model_distance)
standardize_parameters(model_distance)

```

# Modelling

```{r}
dat_model <- dat_ex_plot %>% 
  mutate(explanation_type = factor(explanation_type, levels = c("Direct", "Intrinsic")), 
         subject_id = as_factor(subject_id),
         causal_itemA = as_factor(causal_itemA),
         similar_itemA = as_factor(similar_itemA)) 

#model
model_effect_of_explanation_type <- lmerTest::lmer(satisfactory ~ explanation_type +
                                              (1|subject_id), data = dat_model)
summary(model_effect_of_explanation_type)
standardize_parameters(model_effect_of_explanation_type)

confint(model_effect_of_explanation_type)

plot(allEffects(model_effect_of_explanation_type))

#probabilities
effects_data <- allEffects(model_effect_of_explanation_type)
effects_df <- as.data.frame(effects_data$explanation)
effects_df

confint(model_effect_of_explanation_type)
```

## Check model

```{r}
performance::check_model(model_effect_of_explanation_type)
```

```{r}
summary(model_effect_of_explanation_type)
fixef(model_effect_of_explanation_type)  # Check the actual parameter names
or <- exp(fixef(model_effect_of_explanation_type)[1])
or

```

# THE END

```{r}

```


