---
title: "prediction"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-19"
author: ""
---

# ReadMe

This is the analysis script for the explanations study.  
N = 105 (before exclusions).  
One between-subjects condition. Independent variable is whether explanations
The question: 

# Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               gt,
               webshot2,
               knitr,
               performance,
               simr,
               conflicted,
               tidyverse)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()

```

# Global variables

```{r}
base_path <- here("code", "main")
freesort_and_causal_distances_df_path <- paste0(base_path,
                                                "/analysis/study1-measure-main-and-pilot/snapshots_study1_main_analysis/freesort_minus_causals.csv")

freesort_and_causal_distances_constrained_df_path <- paste0(base_path,
                                                "/analysis/study1-measure-main-and-pilot/snapshots_study1_main_analysis/short_list_domain_constraints.csv")

```


# Study 4 - Explanations

## read data

```{r}
data_path_pr <- paste0(base_path, "/data/prediction/JO-mbc-main-study5-v2-prediction-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_pr, pattern = "^2025-", full.names = TRUE)

d_pr <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")


```


## wrangle data

```{r}
subjects_to_exclude <- d_pr %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>%
  filter(attn_correct == FALSE) %>% 
  pull(subject_id) %>% 
  unique()

dat_pr <- d_pr %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% 
  filter(condition %in% c("event_prediction", "trait_inference")) %>%
  mutate(response = as.factor(response)) %>% 
  mutate(condition = ifelse(condition == "event_prediction", "prediction", "inference")) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "causal",
    grepl(similar_itemA, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  ungroup() %>% 
  select(subject_id, condition, itemB, causal_itemA, similar_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", #labels for first item of pair
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "bio", 
                                 itemB == "become hungry" ~ "bio",
                                 itemB == "feel scared"~ "bio",
                                 itemB == "experience pain"~ "bio",
                                 itemB == "get sick"~ "bio"),
         domain_causalitemA = case_when(causal_itemA == "hear something" ~ "mind", 
                                 causal_itemA == "choose what to do" ~ "mind",
                                 causal_itemA == "remember something" ~ "mind",
                                 causal_itemA == "think about something" ~ "mind",
                                 causal_itemA == "see something" ~ "mind",
                                 causal_itemA == "reach for something" ~ "action",
                                 causal_itemA == "sit down" ~ "action", 
                                 causal_itemA == "jump up and down" ~ "action",
                                 causal_itemA == "kick something" ~ "action",
                                 causal_itemA == "take a walk" ~ "action",
                                 causal_itemA == "get tired" ~ "bio", 
                                 causal_itemA == "become hungry" ~ "bio",
                                 causal_itemA == "feel scared"~ "bio",
                                 causal_itemA == "experience pain"~ "bio",
                                 causal_itemA == "get sick"~ "bio"),
          domain_similaritemA = case_when(similar_itemA == "hear something" ~ "mind", 
                                 similar_itemA == "choose what to do" ~ "mind",
                                 similar_itemA == "remember something" ~ "mind",
                                 similar_itemA == "think about something" ~ "mind",
                                 similar_itemA == "see something" ~ "mind",
                                 similar_itemA == "reach for something" ~ "action",
                                 similar_itemA == "sit down" ~ "action", 
                                 similar_itemA == "jump up and down" ~ "action",
                                 similar_itemA == "kick something" ~ "action",
                                 similar_itemA == "take a walk" ~ "action",
                                 similar_itemA == "get tired" ~ "bio", 
                                 similar_itemA == "become hungry" ~ "bio",
                                 similar_itemA == "feel scared"~ "bio",
                                 similar_itemA == "experience pain"~ "bio",
                                 similar_itemA == "get sick"~ "bio")) 

```

## demographics

```{r}
# demographics
df_demographics <- d_pr %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

paste0("pre-exclusion N: ", d_pr %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat_pr %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
summary(df_demographics$filename)
summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

# Plot

## Condition difference

```{r, fig.width = 6, fig.height = 5}
dat_summarized <- dat_pr %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(condition = ifelse(condition == "prediction", "Prediction", "Inference")) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

main_fig <- dat_summarized %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000"),
                        labels = c("Latent", "Direct")) + 
    geom_errorbar(data = filter(dat_summarized, response == "causal"), aes(ymax = mean_proportion + se,
                                                                           ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
    theme_cowplot() +
  labs(y = "Proportion",
       x = "Condition",
       fill = "Response") +
  ylim(0, 1) +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),

        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent', color = NA),
        legend.box.background = element_rect(fill='transparent', color = NA),
        
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm")
        ) 

main_fig

# main_fig <- ggsave("figures/prediction.png", width = 5, height = 5, plot = main_fig, bg = "transparent")

main_fig <- ggsave("figures/prediction.png", width = 6, height = 5, plot = main_fig, bg = "white")


```

## Condition difference - spp 2026

```{r, fig.width = 4, fig.height = 5}
spp_26 <- dat_summarized %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000")) + 
    geom_errorbar(data = filter(dat_summarized, response == "causal"), 
                  aes(ymax = mean_proportion + se,
                      ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
    theme_cowplot() +
  labs(y = "Proportion",
       x = "Condition",
       fill = "Response") +
  scale_x_discrete(labels = c("Inference" = "Infe-\nrence", "Prediction" = "Pred-\niction")) +
  ylim(0, 1) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 25),
        legend.position = "none",
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)#,
        ) 

spp_26

ggsave(paste0(base_path, "/analysis/study5-prediction/figures/spp_26.pdf"), 
       plot = spp_26,
       # device = svglite::svglite,
       width = 4,
       height = 5,
       units = "in",
       bg = "white")

```

# figure with slope

```{r}
dat_trial_summarized <- dat_pr %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(condition = ifelse(condition == "prediction", "Prediction", "Inference")) %>% 
  mutate(condition = factor(condition, levels = c("Prediction", "Inference"))) %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop") %>% 
  mutate(
    ci_low = pmax(0, mean_proportion - 1.96 * se),
    ci_high = pmin(1, mean_proportion + 1.96 * se)
  ) 

# dat_bar <- dat_trial_summarized %>%
#   group_by(condition, response) %>%
#   summarize(
#     mean_proportion = mean(mean_proportion),
#     se = sd(mean_proportion) / sqrt(n()),
#     .groups = "drop"
#   ) 

dat_bar <- dat_pr %>%
  mutate(
    response = fct_relevel(response, c("similar", "causal")),
    condition = ifelse(condition == "prediction", "Prediction", "Inference"),
    condition = factor(condition, levels = c("Prediction", "Inference"))
  ) %>%
  count(condition, response) %>%
  group_by(condition) %>%
  mutate(mean_proportion = n / sum(n)) %>%
  ungroup() %>%
  mutate(se = 0)


dat_bar %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) +
  geom_errorbar(
    data = dplyr::filter(dat_bar, response == "causal"),
    aes(ymin = mean_proportion - se, ymax = mean_proportion + se),
    width = 0.3
  ) +
  geom_point(
    data = dplyr::filter(dat_trial_summarized, response == "causal"),
    aes(group = joined),
    alpha = 0.9, color = "darkgray"#,
    # position = position_jitter(width = 0.05, height = 0)
  ) +
  geom_line(
    data = dplyr::filter(dat_trial_summarized, response == "causal"),
    aes(group = joined),
    alpha = 0.6, color = "darkgray"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_cowplot() +
  labs(y = "Proportion", x = "Condition", fill = "Response") +
  scale_x_discrete(labels = c("Inference" = "Infe-\nrence", "Prediction" = "Pred-\niction")) +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    legend.text = element_text(size = 25),
    panel.background = element_rect(fill='transparent', color=NA),
    plot.background = element_rect(fill='transparent', color=NA)
  )


```
v2

```{r}

```



## Item-level breakdown

### Append distances

```{r}
#appending distances
d_distances <- read_csv(freesort_and_causal_distances_constrained_df_path)

rmarkdown::paged_table(d_distances)
```

### Then plotting

```{r, fig.height = 12, fig.width = 12}
dat_summarized_itemlevel <- dat_pr %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  group_by(condition, itemB) %>%
  mutate(total = n()) %>% 
  group_by(condition, itemB, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

mean_diff <- dat_summarized_itemlevel %>%
  filter(response == "causal") %>%
  mutate(condition = tolower(condition)) %>%
  select(itemB, condition, mean_proportion) %>%
  tidyr::pivot_wider(names_from = condition, values_from = mean_proportion) %>%
  mutate(meanPred_minus_meanInf = round(prediction - inference, 2)) %>%
  select(itemB, meanPred_minus_meanInf)

dat_labels <- dat_pr %>% 
  left_join(d_distances %>% #join distances
              mutate("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  distinct(itemB, causal_itemA, similar_itemA, 
           causal_distance_causal_choice,
           freesort_distance_causal_choice,
           causal_distance_similar_choice,
           freesort_distance_similar_choice,
           freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         cds_minus_cdc = causal_distance_similar_choice - causal_distance_causal_choice,
         fdc_minus_fds = freesort_distance_causal_choice - freesort_distance_similar_choice,
         fdmcdc_minus_fdmcds = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>% 
  left_join(mean_diff, by = "itemB") %>%
  mutate(facet_label = paste0(itemB, 
                              "\n",
                              "causal: ", causal_itemA, 
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice,
                              ",",
                              freesort_distance_causal_choice,
                              ",",
                              freesort_minus_causal_distance_causal,
                              ")",
                              "\n",  # black square
                              "similar: ", similar_itemA, # white square (or use light gray block)
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice,
                              ",",
                              freesort_distance_similar_choice,
                              ",",
                              freesort_minus_causal_distance_similar,
                              ")",
                              "\n",
                              "cdS - cdC: ",
                              cds_minus_cdc,
                              "\n",
                              "fdC - fdS: ",
                              fdc_minus_fds,
                              "\n",
                              "(f-cC) - (f-cS): ",
                              fdmcdc_minus_fdmcds,
                              "\n",
                              "meanPred(C) - meanInf(C): ",
                              meanPred_minus_meanInf
                              ))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

# join labels + ordering AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion",
       title = "main") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

ggsave(
  filename = "figures/p_prediction_item-level.pdf",
  plot = p_itemlvl,          
  device = "pdf",           
  width = 22,               
  height = 15,             
  units = "in")

```

# Distances analysis

interpretation: for prediction, you choose whichever item is really causal. So you choose the causal item more if its causal and if the similar item is not causal; and you choose the similar item more if the similar item is more causal and the causal item is less causal.

## join and save

```{r}
d_distances
dat_pr_distances <- dat_pr %>% 
  left_join(d_distances %>% 
              select(causal_choice, similar_choice, target_item, 
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar) %>%
              rename("causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice,
                     "itemB" = target_item),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

write_csv(dat_pr_distances, "dat_prediction_distances.csv")

#View(dat_pr_distances)
```

## Read back in data frame

```{r}
analysis_path <- here("code", "main", "analysis")

dat_pr_distances <- read_csv(paste0(analysis_path,
                "/study5-prediction/dat_prediction_distances.csv"))

#prepare for modelling
dat_model <- dat_pr_distances %>% 
  mutate(subject_id = as.factor(subject_id),
         response = ifelse(response == "causal", 1, 0)) 

```

## Summarize data 

Not currently using this data frame but summarized just for checking purposes

```{r}
dat_model_summarized <- dat_model %>% 
  # mutate(response = fct_relevel(response, c("similar", "causal"))) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

rmarkdown::paged_table(dat_model_summarized)
```

## Prediction distances - clear way

Uses predict(). This is what I'm going with

```{r}
model_prediction <- glmer(response ~ freesort_minus_causal_distance_causal +
                        freesort_minus_causal_distance_similar + 
                        (1 | subject_id), 
    data = dat_model %>% filter(condition == "prediction"),
    family = binomial(link = 'logit'))

summary(model_prediction)

dat_prediction <- dat_model %>%
  distinct(condition, response, itemB, causal_itemA, similar_itemA,
           freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  # mutate(trial_id = paste("T:", itemB, "\n", "C:", 
  #                         causal_itemA, "\n", "S:", similar_itemA)) %>% 
  filter(condition == "prediction")

dat_prediction_newdata <- dat_prediction %>% 
  mutate(p_hat = predict(model_prediction, 
                         newdata = ., 
                         type = "response", 
                         re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, freesort_minus_causal_distance_causal, 
         freesort_minus_causal_distance_similar, p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
        "similar_item" = freesort_minus_causal_distance_similar) %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") 

# View(d_test)

plot_prediction_distances <- dat_prediction_newdata %>% 
  ggplot(aes(x = joint_distance, y = p_hat, color = item_type)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Prediction Condition",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_prediction_distances

```

### prediction, single x axis

```{r}
dat_prediction_newdata <- dat_prediction %>% 
  mutate(p_hat = predict(model_prediction, 
                         newdata = ., 
                         type = "response", 
                         re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, freesort_minus_causal_distance_causal, 
         freesort_minus_causal_distance_similar, p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
        "similar_item" = freesort_minus_causal_distance_similar) %>% 
  mutate(joint_distance_diff = causal_item - similar_item)

plot_prediction_distances <- dat_prediction_newdata %>% 
  ggplot(aes(x = joint_distance_diff, y = p_hat)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Prediction Condition",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint causal - Joint similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_prediction_distances

distances_diff_fig <- ggsave("figures/prediction_diffs_joint.png", 
                   width = 6, height = 5, plot = plot_prediction_distances, 
                   bg = "white")

```


## Magical distances - clear way

```{r}
model_inference <- glmer(response ~ freesort_minus_causal_distance_causal +
                        freesort_minus_causal_distance_similar + 
                        (1 | subject_id), 
    data = dat_model %>% filter(condition == "inference"),
    family = binomial(link = 'logit'))

summary(model_inference)

dat_inference_newdata <- dat_model %>%
  distinct(condition, response, itemB, causal_itemA, similar_itemA,
           causal_distance_causal_choice,
           freesort_distance_causal_choice,
           freesort_minus_causal_distance_causal,
           
           causal_distance_similar_choice,
           freesort_distance_similar_choice,
           freesort_minus_causal_distance_similar) %>%
  mutate(trial_id = paste("T:", itemB, "\n", "C:", 
                          causal_itemA, "\n", "S:", similar_itemA)) %>% 
  filter(condition == "inference")

dat_inference_newdata_plot <- dat_inference_newdata %>% 
  mutate(p_hat = predict(model_inference, 
                         newdata = ., 
                         type = "response", re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, 
         freesort_distance_causal_choice,
         causal_distance_causal_choice,
         freesort_minus_causal_distance_causal,
         
         freesort_distance_similar_choice,
         causal_distance_similar_choice,
         freesort_minus_causal_distance_similar, 
         p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
         "similar_item" = freesort_minus_causal_distance_similar,
         "cd_c" = causal_distance_causal_choice,
         "fd_c" = freesort_distance_causal_choice,
         "cd_s" = causal_distance_similar_choice,
         "fd_s" = freesort_distance_similar_choice,
         "target" = itemB) %>% 
  mutate(diff = causal_item + similar_item) 

# View(dat_inference_newdata_plot %>% 
#        arrange(p_hat) %>% 
#        distinct(target, .keep_all = TRUE))

plot_inference_distances <- dat_inference_newdata_plot %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") %>% 
  ggplot(aes(x = joint_distance, y = p_hat, color = item_type)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Inference Condition",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_inference_distances
#ordinary prediction = borne out in data
#the more the causal item is causal they choose causal item
# the more the causal item is similar they choose the similar item (the opposite item)

#magical prediction
#the more the similar item is similar they choose the similar item
#the more the similar item is causal, they choose the causal item (the opposite item)

```

### prediction, single x axis

```{r}
dat_inference_newdata_plot <- dat_inference_newdata %>% 
  mutate(p_hat = predict(model_inference, 
                         newdata = ., 
                         type = "response", re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, 
         freesort_distance_causal_choice,
         causal_distance_causal_choice,
         freesort_minus_causal_distance_causal,
         
         freesort_distance_similar_choice,
         causal_distance_similar_choice,
         freesort_minus_causal_distance_similar, 
         p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
         "similar_item" = freesort_minus_causal_distance_similar,
         "target" = itemB) %>% 
    mutate(joint_distance_diff = causal_item - similar_item)

plot_inference_distances <- dat_inference_newdata_plot %>% 
  ggplot(aes(x = joint_distance_diff, y = p_hat)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Inference Condition",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint causal - Joint similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_inference_distances

distances_diff_fig <- ggsave("figures/inference_diffs_joint.png", 
                   width = 6, height = 5, plot = plot_inference_distances, 
                   bg = "white")

```

# Primary Analysis

## Logistic regression

```{r}
d_model <- dat_pr %>%
  mutate(response = fct_relevel(response, c("causal", "similar"))) %>%
  mutate(subject_id = factor(subject_id))

model_prediction_vs_inference <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_prediction_vs_inference)

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_prediction_vs_inference)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Prediction condition only

```{r}
d_model_prediction <- d_model %>% 
  filter(condition == "prediction") %>% 
  mutate(condition = factor(condition))

model_prediction <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_prediction)

summary(model_prediction)

## Convert log odds to probabilities (I think)
plogis(fixef(model_prediction)[1])

```

## Inference condition only

```{r}
d_model_inference <- d_model %>% 
  filter(condition == "inference") %>% 
  mutate(condition = factor(condition))

model_inference <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_inference)

summary(model_inference)

## Convert log odds to probabilities (I think)
plogis(fixef(model_inference)[1])

```



```{r}

```


