---
title: "Causal Chain"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-11-22"
author: Joseph Outa
---

# ReadMe

- Study name: Causal chain
- Research question: Do subjects use direct causes for causal chain, and latent causes for common causes
- Design: Between-subjects, causal chain condition vs common cause condition
- Independent variable: choice of middle item in causal chain vs common cause
- Dependent variable: proportion choosing similar vs causal item
- Date study ran: 11/22/25 (105N pilot)
- Some descriptive stats: N of study 105, N per condition (causal_chain = 46, common_cause = 59), Mean age (42y)
- Location of relevant accessory files: codebook (/code/codebooks), pre-registration (/preregistration)

# Setup

## Load packages

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
theme_set(theme_bw())
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code", "pilot")
base_path_distances <- here("code", "main")
data_path <- paste0(base_path, "/data/data-study5-causal-chains/JO-mbc-pilot-cc-v3_105N")
# data_path <- paste0(base_path, "/data/data-study5-causal-chains/JO-mbc-pilot-cc-v2_105N")

snapshots_input_path_distances <- paste0(base_path_distances,
                                         "/analysis/1_measure-main-and-pilot/snapshots_study1_main_analysis")

distances_path <- paste0(snapshots_input_path_distances,
                                   "/freesort_minus_causals.csv")

desired_order <- c("see something", "choose what to do", "remember something", 
                   "sit down", "jump up and down", "take a walk", 
                   "get tired", "become hungry", "get sick")

```

## Read data

```{r, warnings = FALSE}
file_paths <- list.files(path = data_path, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

# Wrangle Data

## Wrangle

initial: 30 trials * 48 subjects = 1440 rows.
dat: (30 trials / 2 trials per row) * 48 subjects = 720 rows.
TODO: rename itemB to target item.

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>% 
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()

dat <- d %>% 
  filter(condition %in% c("causal_chain", "common_cause")) %>% 
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(middle_causal, selected_choice) ~ "causal",
    grepl(middle_similar, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  select(subject_id, condition, first_item, middle_causal, 
         middle_similar, third_item, response) %>% 
  # mutate(first_item = factor(first_item, levels = desired_order),
  #        middle_causal = factor(middle_causal, levels = desired_order),
  #        middle_similar = factor(middle_similar, levels = desired_order),
  #        third_item = factor(third_item, levels = desired_order)) %>% 
  mutate(domain_first_item = case_when(first_item == "hear something" ~ "mind", 
                                 first_item == "choose what to do" ~ "mind",
                                 first_item == "remember something" ~ "mind",
                                 first_item == "think about something" ~ "mind",
                                 first_item == "see something" ~ "mind",
                                 first_item == "reach for something" ~ "action",
                                 first_item == "sit down" ~ "action", 
                                 first_item == "jump up and down" ~ "action",
                                 first_item == "kick something" ~ "action",
                                 first_item == "take a walk" ~ "action",
                                 first_item == "get tired" ~ "bio", 
                                 first_item == "become hungry" ~ "bio",
                                 first_item == "feel scared"~ "bio",
                                 first_item == "experience pain"~ "bio",
                                 first_item == "get sick"~ "bio"),
         domain_third_item = case_when(third_item == "hear something" ~ "mind", 
                                 third_item == "choose what to do" ~ "mind",
                                 third_item == "remember something" ~ "mind",
                                 third_item == "think about something" ~ "mind",
                                 third_item == "see something" ~ "mind",
                                 third_item == "reach for something" ~ "action",
                                 third_item == "sit down" ~ "action", 
                                 third_item == "jump up and down" ~ "action",
                                 third_item == "kick something" ~ "action",
                                 third_item == "take a walk" ~ "action",
                                 third_item == "get tired" ~ "bio", 
                                 third_item == "become hungry" ~ "bio",
                                 third_item == "feel scared"~ "bio",
                                 third_item == "experience pain"~ "bio",
                                 third_item == "get sick"~ "bio"),
         domain_middle_causal = case_when(middle_causal == "hear something" ~ "mind", 
                                 middle_causal == "choose what to do" ~ "mind",
                                 middle_causal == "remember something" ~ "mind",
                                 middle_causal == "think about something" ~ "mind",
                                 middle_causal == "see something" ~ "mind",
                                 middle_causal == "reach for something" ~ "action",
                                 middle_causal == "sit down" ~ "action", 
                                 middle_causal == "jump up and down" ~ "action",
                                 middle_causal == "kick something" ~ "action",
                                 middle_causal == "take a walk" ~ "action",
                                 middle_causal == "get tired" ~ "bio", 
                                 middle_causal == "become hungry" ~ "bio",
                                 middle_causal == "feel scared"~ "bio",
                                 middle_causal == "experience pain"~ "bio",
                                 middle_causal == "get sick"~ "bio"),
          domain_middle_similar = case_when(middle_similar == "hear something" ~ "mind", 
                                 middle_similar == "choose what to do" ~ "mind",
                                 middle_similar == "remember something" ~ "mind",
                                 middle_similar == "think about something" ~ "mind",
                                 middle_similar == "see something" ~ "mind",
                                 middle_similar == "reach for something" ~ "action",
                                 middle_similar == "sit down" ~ "action", 
                                 middle_similar == "jump up and down" ~ "action",
                                 middle_similar == "kick something" ~ "action",
                                 middle_similar == "take a walk" ~ "action",
                                 middle_similar == "get tired" ~ "bio", 
                                 middle_similar == "become hungry" ~ "bio",
                                 middle_similar == "feel scared"~ "bio",
                                 middle_similar == "experience pain"~ "bio",
                                 middle_similar == "get sick"~ "bio")) %>% 
  ungroup()
  
```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 
cat("\n") 

paste0("pre-exclusion N: ", d %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
cat("\n") 

paste0(
  "Post-exclusion condition count: ",
  dat %>% 
    distinct(subject_id, .keep_all = TRUE) %>% 
    count(condition) %>% 
    mutate(label = paste0(condition, " = ", n)) %>% 
    pull(label) %>% 
    paste(collapse = ", ")
)
cat("\n") 

paste0("Age summary: ")
summary(df_demographics$age)
cat("\n") 

c("Gender: " =  "Count", table(df_demographics$gender))
cat("\n")
c("Ethnicity: " =  "Count", table(df_demographics$ethnicity))
cat("\n")
c("Race: " =  "Count", table(df_demographics$race))

```

# Plot

## Condition difference

```{r}
dat_summarized <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

main_fig <- dat_summarized %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000")) + 
    geom_errorbar(data = filter(dat_summarized, response == "causal"), aes(ymax = mean_proportion + se,
                                                                           ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
    theme_cowplot() +
  labs(y = "Proportion",
       x = "Condition",
       fill = "Response") +
  ylim(0, 1) +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),

        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent', color = NA),
        legend.box.background = element_rect(fill='transparent', color = NA),
        
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm")
        ) 

main_fig

# main_fig <- ggsave("figures/prediction.png", width = 5, height = 5, plot = main_fig, bg = "transparent")

main_fig <- ggsave("figures/causal_chain-v2.png", width = 6, height = 5, plot = main_fig, bg = "white")

```

## Item-level


```{r, fig.height = 12, fig.width = 12}
preceding_distances_path <- distances_path

d_distances <- read_csv(distances_path) %>%
  mutate(mean_causal_distance = round(mean_causal_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2))

dat_summarized_itemlevel <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  group_by(condition, first_third) %>%
  mutate(total = n()) %>% 
  group_by(condition, first_third, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

dat_labels <- dat %>% 
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  distinct(first_third, middle_causal, middle_similar) %>% 
  separate(first_third, c("first_item", "third_item"),
           sep = "_", remove = FALSE) %>%
  left_join(d_distances %>% #join causal distances
              rename("third_item" = itemB,
                     "middle_causal" = itemA,
                     "causal_distance_causal_third" = mean_causal_distance,
                     "freesort_distance_causal_third" = mean_freesort_distance,
                     "freesort_minus_causal_causal_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_causal,
                     causal_distance_causal_third,
                     freesort_distance_causal_third,
                     freesort_minus_causal_causal_third), 
            by = c("third_item", "middle_causal")) %>% 
  left_join(d_distances %>% #join similar distances
              rename("third_item" = itemB,
                     "middle_similar" = itemA,
                     "causal_distance_similar_third" = mean_causal_distance,
                     "freesort_distance_similar_third" = mean_freesort_distance,
                     "freesort_minus_causal_similar_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_similar,
                     causal_distance_similar_third,
                     freesort_distance_similar_third,
                     freesort_minus_causal_similar_third), 
            by = c("third_item", "middle_similar")) %>% 
  
  left_join(d_distances %>% 
              rename("first_item" = itemA,
                     "middle_causal" = itemB,
                     "causal_distance_causal_first" = mean_causal_distance,
                     "freesort_distance_causal_first" = mean_freesort_distance,
                     "freesort_minus_causal_causal_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_causal,
                     causal_distance_causal_first,
                     freesort_distance_causal_first,
                     freesort_minus_causal_causal_first), 
            by = c("first_item", "middle_causal")) %>% 
  left_join(d_distances %>% 
              rename("first_item" = itemA,
                     "middle_similar" = itemB,
                     "causal_distance_similar_first" = mean_causal_distance,
                     "freesort_distance_similar_first" = mean_freesort_distance,
                     "freesort_minus_causal_similar_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_similar,
                     causal_distance_similar_first,
                     freesort_distance_similar_first,
                     freesort_minus_causal_similar_first), 
            by = c("first_item", "middle_similar")) %>% 

  mutate(facet_label = paste0("first item: ", first_item,
                              "\n",
                              "third item: ", third_item,
                              "\n",
                              "causal: ", middle_causal, 
                              "\n",  
                              "similar: ", middle_similar
                              )) 

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  mutate(first_item = factor(first_item, levels = desired_order)) %>% 
  arrange(first_item) %>% 
  pull(facet_label)

#join labels + order AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(first_third, facet_label), by = "first_third") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion",
       title = "Causal Chain - pilot, N = 105") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

ggsave(
  filename = "figures/p_causal_chain_item-level-v2.pdf",
  plot = p_itemlvl,          
  device = "pdf",           
  width = 22,    
  bg = "white",
  height = 15,             
  units = "in")

```


## Item-level with distances

```{r, fig.height = 12, fig.width = 12}
preceding_distances_path <- distances_path
# d_distances <- read_csv(preceding_distances_path) %>%
d_preceding_distances <- read_csv(preceding_distances_path) %>%
# d_distances <- read_csv(distances_path) %>%
  mutate(mean_causal_distance = round(mean_causal_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2))

# d_following_distances <- read_csv(following_distances_path) %>% 
#   mutate(mean_causal_distance = round(mean_causal_distance, 2),
#          mean_freesort_distance = round(mean_freesort_distance, 2),
#          freesort_minus_causal = round(freesort_minus_causal, 2))


dat_summarized_itemlevel <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  group_by(condition, first_third) %>%
  mutate(total = n()) %>% 
  group_by(condition, first_third, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

dat_labels <- dat %>% 
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  distinct(first_third, middle_causal, middle_similar) %>% 
  separate(first_third, c("first_item", "third_item"),
           sep = "_", remove = FALSE) %>%
  left_join(d_preceding_distances %>% #join causal distances
              rename("third_item" = itemB,
                     "middle_causal" = itemA,
                     "causal_distance_causal_third" = mean_causal_distance,
                     "freesort_distance_causal_third" = mean_freesort_distance,
                     "freesort_minus_causal_causal_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_causal,
                     causal_distance_causal_third,
                     freesort_distance_causal_third,
                     freesort_minus_causal_causal_third), 
            by = c("third_item", "middle_causal")) %>% 
  left_join(d_preceding_distances %>% #join similar distances
              rename("third_item" = itemB,
                     "middle_similar" = itemA,
                     "causal_distance_similar_third" = mean_causal_distance,
                     "freesort_distance_similar_third" = mean_freesort_distance,
                     "freesort_minus_causal_similar_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_similar,
                     causal_distance_similar_third,
                     freesort_distance_similar_third,
                     freesort_minus_causal_similar_third), 
            by = c("third_item", "middle_similar")) %>% 
  
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_causal" = itemB,
                     "causal_distance_causal_first" = mean_causal_distance,
                     "freesort_distance_causal_first" = mean_freesort_distance,
                     "freesort_minus_causal_causal_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_causal,
                     causal_distance_causal_first,
                     freesort_distance_causal_first,
                     freesort_minus_causal_causal_first), 
            by = c("first_item", "middle_causal")) %>% 
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_similar" = itemB,
                     "causal_distance_similar_first" = mean_causal_distance,
                     "freesort_distance_similar_first" = mean_freesort_distance,
                     "freesort_minus_causal_similar_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_similar,
                     causal_distance_similar_first,
                     freesort_distance_similar_first,
                     freesort_minus_causal_similar_first), 
            by = c("first_item", "middle_similar")) %>% 

  mutate(facet_label = paste0("first item: ", first_item,
                              "\n",
                              "third item: ", third_item,
                              "\n",
                              "causal: ", middle_causal, 
                              "\n",  
                              "similar: ", middle_similar,
                              "\n",
                              "\n",
                              "1st item-cdS,fdS,cdC,fdC: ", "(", 
                              causal_distance_similar_first, ",",
                              freesort_distance_similar_first, ",",
                              causal_distance_causal_first, ",",
                              freesort_distance_causal_first, ")", "\n", 
                              "3rd item-cdS, fdS, cdC, fdC: ", "(", 
                              causal_distance_similar_third, ",",
                              freesort_distance_similar_third, ",",
                              causal_distance_causal_third, ",",
                              freesort_distance_causal_third, ")"
                              )) 

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  mutate(first_item = factor(first_item, levels = desired_order)) %>% 
  arrange(first_item) %>% 
  pull(facet_label)

#join labels + order AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(first_third, facet_label), by = "first_third") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion",
       title = "Causal Chain - pilot, N = 105") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

ggsave(
  filename = "figures/p_causal_chain_item-level-distances.pdf",
  plot = p_itemlvl,          
  device = "pdf",           
  width = 22,    
  bg = "white",
  height = 15,             
  units = "in")

```

## Item-level with distances

```{r}
d_distances <- read_csv(distances_path) %>% 
  mutate(mean_causal_distance = round(mean_causal_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2))

dat_summarized_itemlevel <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  group_by(condition, first_third) %>%
  mutate(total = n()) %>% 
  group_by(condition, first_third, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

dat_labels <- dat %>% 
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  distinct(first_third, middle_causal, middle_similar) %>% 
  separate(first_third, c("first_item", "third_item"),
           sep = "_", remove = FALSE) %>%
  left_join(d_distances %>% #join causal distances
              rename("third_item" = itemB,
                     "middle_causal" = itemA,
                     "causal_distance_causal_third" = mean_causal_distance,
                     "freesort_distance_causal_third" = mean_freesort_distance,
                     "freesort_minus_causal_causal_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_causal,
                     causal_distance_causal_third,
                     freesort_distance_causal_third,
                     freesort_minus_causal_causal_third), 
            by = c("third_item", "middle_causal")) %>% 
  left_join(d_distances %>% #join similar distances
              rename("third_item" = itemB,
                     "middle_similar" = itemA,
                     "causal_distance_similar_third" = mean_causal_distance,
                     "freesort_distance_similar_third" = mean_freesort_distance,
                     "freesort_minus_causal_similar_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_similar,
                     causal_distance_similar_third,
                     freesort_distance_similar_third,
                     freesort_minus_causal_similar_third), 
            by = c("third_item", "middle_similar")) %>% 
  
  left_join(d_distances %>% 
              rename("first_item" = itemA,
                     "middle_causal" = itemB,
                     "causal_distance_causal_first" = mean_causal_distance,
                     "freesort_distance_causal_first" = mean_freesort_distance,
                     "freesort_minus_causal_causal_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_causal,
                     causal_distance_causal_first,
                     freesort_distance_causal_first,
                     freesort_minus_causal_causal_first), 
            by = c("first_item", "middle_causal")) %>% 
  left_join(d_distances %>% 
              rename("first_item" = itemA,
                     "middle_similar" = itemB,
                     "causal_distance_similar_first" = mean_causal_distance,
                     "freesort_distance_similar_first" = mean_freesort_distance,
                     "freesort_minus_causal_similar_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_similar,
                     causal_distance_similar_first,
                     freesort_distance_similar_first,
                     freesort_minus_causal_similar_first), 
            by = c("first_item", "middle_similar")) %>% 

  mutate(facet_label = paste0("first item: ", first_item,
                              "\n",
                              "third item: ", third_item,
                              "\n",
                              "Causal: ", middle_causal, 
                              "\n",  
                              "Similar: ", middle_similar,
                              "\n",
                              "\n",
                              "1st item (cdS,fdS,cdC,fdC): ", "(", 
                              causal_distance_similar_first, ",",
                              freesort_distance_similar_first, ",",
                              causal_distance_causal_first, ",",
                              freesort_distance_causal_first, ")", "\n", 
                              "3rd item (cdS, fdS, cdC, fdC): ", "(", 
                              causal_distance_similar_third, ",",
                              freesort_distance_similar_third, ",",
                              causal_distance_causal_third, ",",
                              freesort_distance_causal_third, ")"
                              )) 

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  mutate(first_item = factor(first_item, levels = desired_order)) %>% 
  arrange(first_item) %>% 
  pull(facet_label)

#join labels + order AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(first_third, facet_label), by = "first_third") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion",
       title = "Causal Chain - pilot, N = 105") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

ggsave(
  filename = "figures/p_causal_chain_item-level-distances.pdf",
  plot = p_itemlvl,          
  device = "pdf",           
  width = 22,    
  bg = "white",
  height = 15,             
  units = "in")

```

# Primary Analysis

## Logistic regression

```{r}
##factor outcome variables
d_model <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(subject_id = factor(subject_id))

##run the model
model_chain_vs_common <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_chain_vs_common)

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_chain_vs_common)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

# Power analysis with simr 

NB: This only applies to the pilot

### Both conditions

```{r}
# This will test for power required to detect the condition difference

#Suppose we want a study with 150 participants..
model_sim <- extend(model_chain_vs_common, along = "subject_id", n = 150)
length(unique(simr::getData(model_sim)$subject_id)) #confirm that N is now 150

#run simulations
curve_chain_vs_common <- powerCurve(model_sim, fixed("conditioncommon_cause",
                                               "z"),
                    along = "subject_id", breaks = c(1, 5, 10, 20, 30, 40, 50,
                                                     60, 70, 80, 90, 100,
                                                     110, 120, 130, 140, 150), nsim = 100)

## Plot power curve
plot(curve_chain_vs_common)
print(curve_chain_vs_common)

```

### Causal Chain Only

```{r}
## Make sure to re-factor your outcome variable after filtering!
d_model_causal_chain <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "causal_chain") %>% 
  mutate(condition = factor(condition))

model_causal_chain <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_causal_chain)

summary(model_causal_chain)

## Convert log odds to probabilities (I think)
plogis(fixef(model_causal_chain)[1])

# Power Analysis
model_sim <- extend(model_causal_chain, along = "subject_id", n = 150)
length(unique(simr::getData(model_sim)$subject_id)) 

curve_causal_chain <- powerCurve(model_sim, fixed("(Intercept)",
                                               "z"),
                    along = "subject_id", breaks = c(1, 5, 10, 20, 30, 40, 50,
                                                     60, 70, 80, 90, 100,
                                                     110, 120, 130, 140, 150), nsim = 100)

plot(curve_causal_chain)
print(curve_causal_chain)

```

### Common Cause Only

```{r}
## Make sure to re-factor your outcome variable after filtering!
d_model_common_cause <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "common_cause") %>% 
  mutate(condition = factor(condition))

model_common_cause <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_common_cause)

summary(model_common_cause)

## Convert log odds to probabilities (I think)
plogis(fixef(model_common_cause)[1])

# Power Analysis
model_sim <- extend(model_common_cause, along = "subject_id", n = 150)
length(unique(simr::getData(model_sim)$subject_id)) 

curve_common_cause <- powerCurve(model_sim, fixed("(Intercept)",
                                               "z"),
                    along = "subject_id", breaks = c(1, 5, 10, 20, 30, 40, 50,
                                                     60, 70, 80, 90, 100,
                                                     110, 120, 130, 140, 150), nsim = 100)

plot(curve_common_cause)
print(curve_common_cause)

```

THE END


```{r}

```




