---
title: "Item selection"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-07-16"
author: Joseph Outa
---

This is the item selection for the Prediction Task. Each target item has a preceeding causal item, a proceeding causal item, and a similar item. 

# Setup

## load packages

```{r, setup, include = FALSE}
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

# paths
## script inputs
base_path <- here("code", "main", "analysis", "study1-measure-main-and-pilot")
snapshots_input_path <- paste0(base_path, "/snapshots_study1_main_analysis") 
data_input_path <- paste0(snapshots_input_path, "/combined_data_processed_step2.csv")
freesort_minus_causal_distances_output_path <- paste0(snapshots_input_path, "/freesort_minus_causals.csv")
snapshots_output_path <- paste0(base_path, "/figures/item-selection/") #for saving item selection csvs

```

## Read data

```{r}
df_combined <- read_csv(data_input_path)

#how many subjects
df_combined %>% 
  slice(length(df_combined$subject_id)) %>% 
  pull(subject_id)

```

# Long list

## "Freesort - causal" calculation

```{r}
#get mean distances by item pairs
df_pair_means <- df_combined %>% 
  select(subject_id, itemA, itemB, freesort_distance, causal_distance) %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>%
  summarize(mean_causal_distance = mean(causal_distance, na.rm = TRUE),
         mean_freesort_distance = mean(freesort_distance, na.rm = TRUE)) %>% 
  ungroup() %>% 
  separate(item_pairs, c("itemA", "itemB"), sep = "_")

#add domain labels
df_item_pair_means_domain <- df_pair_means %>%
  left_join(df_combined %>% 
              select(itemA, itemB, domain_itemA, domain_itemB) %>% 
              distinct(),
              by = c("itemA", "itemB")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order))


df_item_pair_means_domain_long <- df_item_pair_means_domain %>% 
  pivot_longer(
    cols = c("mean_causal_distance", "mean_freesort_distance"),
    names_to = "mean_type",
    values_to = "values"
  ) 

df_item_pair_means_freesort_minus_causal <- df_item_pair_means_domain_long %>% 
  pivot_wider(names_from = "mean_type",
              values_from = "values") %>% 
  mutate(freesort_minus_causal = mean_freesort_distance - mean_causal_distance)

# write.csv(df_item_pair_means_freesort_minus_causal, 
#           freesort_minus_causal_distances_output_path, row.names = F)
```


# Preceding Causal Items and Similar Items

## Plot long list

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemB) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemB)

#Generate a unique color for each itemB
unique_items <- unique(long_list_items$itemB)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemB,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/preceding_long-list-Prediction-task.png")

```

## Short list - no domain constraints

### Select short list

```{r}
#similar item (item with lowest freesort_minus_causal)
similar_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemB) %>% 
  slice_min(freesort_minus_causal)
 
#causal item (item with highest freesort_minus_causal)
causal_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemB) %>% 
  slice_max(freesort_minus_causal)

#join
short_list_selected_items <- causal_items %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemA,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemA, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemB") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemB", .before = "causal_choice") %>% 
  rename(target_item = itemB) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2))

#view items
paged_table(short_list_selected_items)

```


### Plot short list

```{r}
short_list_table <- short_list_selected_items %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #f7bf2a; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #69ad44; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #f36b2d; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  # Keep the domain column


df_table <- short_list_table %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("Causal Choice<br>(Causal Distance, Freesort Distance)"),
    similar_choice = md("Similar Choice<br>(Causal Distance, Freesort Distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#f7bf2a", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#69ad44", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#f36b2d", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table

gtsave(df_table, "figures/item-selection/preceding_short-list-Prediction-task.png")

```

## Short list - domain constraints

### Select short list 


```{r}
similar_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemB) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

causal_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemB) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
  
#join
short_list_selected_items_domain_constraints <- causal_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemA,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items_same_domain %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemA, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemB") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemB", .before = "causal_choice") %>% 
  rename(target_item = itemB) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

#view items
paged_table(short_list_selected_items_domain_constraints)

#save as csv
write_csv(file = "snapshots_study1_main_analysis/preceding_short_list_domain_constraints.csv",
          short_list_selected_items_domain_constraints)

```

### Plot short list constrained

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #f7bf2a; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #69ad44; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #f36b2d; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  # Keep the domain column


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("Causal Choice<br>(Causal Distance, Freesort Distance)"),
    similar_choice = md("Similar Choice<br>(Causal Distance, Freesort Distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#f7bf2a", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#69ad44", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#f36b2d", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/preceding_short-list-Prediction-task-constrained.png")
```

# Following Causal Items and Similar Items

## Plot long list

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemA) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemA)

#Generate a unique color for each itemB
unique_items <- unique(long_list_items$itemB)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemA,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/following_long-list-Prediction-task.png")

```

## Short list - no domain constraints

### Select short list

```{r}
#similar item (item with lowest freesort_minus_causal)
similar_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemA) %>% 
  slice_min(freesort_minus_causal)
 
#causal item (item with highest freesort_minus_causal)
causal_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemA) %>% 
  slice_max(freesort_minus_causal)

#join
short_list_selected_items <- causal_items %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemB,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemB, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemA") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemA", .before = "causal_choice") %>% 
  rename(target_item = itemA) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2))

#view items
paged_table(short_list_selected_items)


```


### Plot short list

```{r}
short_list_table <- short_list_selected_items %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #f7bf2a; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #69ad44; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #f36b2d; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  # Keep the domain column


df_table <- short_list_table %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("Causal Choice<br>(Causal Distance, Freesort Distance)"),
    similar_choice = md("Similar Choice<br>(Causal Distance, Freesort Distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#f7bf2a", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#69ad44", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#f36b2d", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table

gtsave(df_table, "figures/item-selection/following_short-list-Prediction-task.png")

```

## Short list - domain constraints

### Select short list 


```{r}
similar_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemA) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

causal_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemA) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
  
#join
short_list_selected_items_domain_constraints <- causal_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemB,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items_same_domain %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemB, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemA") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemA", .before = "causal_choice") %>% 
  rename(target_item = itemA) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

write_csv(file = "snapshots_study1_main_analysis/following_short_list_domain_constraints.csv",
          short_list_selected_items_domain_constraints)

#view items
paged_table(short_list_selected_items_domain_constraints)


```

### Plot short list constrained

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #f7bf2a; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #69ad44; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #f36b2d; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  # Keep the domain column


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("Causal Choice<br>(Causal Distance, Freesort Distance)"),
    similar_choice = md("Similar Choice<br>(Causal Distance, Freesort Distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#f7bf2a", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#69ad44", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#f36b2d", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/following_short-list-Prediction-task-constrained.png")
```




# END

```{r}
#placeholder
```

