---
title: "study 6"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2024-10-28"
author: ""

---

# ReadMe

This is the analysis for the ordinary vs magical intervention study of the MBC project. 

# Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               gt,
               webshot2,
               knitr,
               performance,
               tidyverse,
               simr,
               conflicted)
sessionInfo()

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)

```

# Global variables

```{r}
base_path <- here("code", "pilot")
main_path <- here("code", "main") #for grabbing updated items

# freesort_and_causal_distances_df_path <- paste0(base_path, "/data/data-study4-explanations/freesort_minus_causals.csv")

snapshots_input_path_main <- paste0(main_path,
                               "/analysis/study1-measure-main-and-pilot/snapshots_study1_main_analysis")
preceding_distances_path <- paste0(snapshots_input_path_main,
                                                "/preceding_short_list_domain_constraints.csv")
following_distances_path <- paste0(snapshots_input_path_main,
                                                "/following_short_list_domain_constraints.csv")

```


# Study 6 - Magical and ordinary intervention

## Prepare data

### read data

```{r, warnings = FALSE}
data_path_cf <- paste0(base_path, "/data/data-study7-follow-up-pilots/inference/JO-mbc-main-study7-inf-50N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_cf, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

### wrangle data

initial: 30 trials per subject * 48 subjects = 1440 rows.
dat: (30 trials / 2 trials per row) * 48 subjects = 720 rows.

(after filtering to only relevant trials)
initial: 15 trials per subject * 2 subjects = 30 rows

TODO: rename itemB to target item.

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>% 
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()


dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% #exclude 1 subject who failed attn check
  filter(condition %in% c("preceding", "following")) %>%
  mutate("causal_itemA" = preceding_causal_itemA,
         "similar_itemA" = preceding_similar_itemA) %>% 
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  mutate(selected_choice = stringr::str_match(selected_choice, "<strong>(.*?)</strong>")[,2]) %>%
  mutate(selected_choice = stringr::str_squish(selected_choice)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "causal",
    grepl(similar_itemA, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  # filter(response == "other") %>%
  # select(condition, causal_itemA, similar_itemA, selected_choice)
  # count(response)
  ungroup() %>% 
  select(subject_id, condition, itemB, causal_itemA, similar_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", #labels for first item of pair
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "bio", 
                                 itemB == "become hungry" ~ "bio",
                                 itemB == "feel scared"~ "bio",
                                 itemB == "experience pain"~ "bio",
                                 itemB == "get sick"~ "bio"),
         domain_causalitemA = case_when(causal_itemA == "hear something" ~ "mind", 
                                 causal_itemA == "choose what to do" ~ "mind",
                                 causal_itemA == "remember something" ~ "mind",
                                 causal_itemA == "think about something" ~ "mind",
                                 causal_itemA == "see something" ~ "mind",
                                 causal_itemA == "reach for something" ~ "action",
                                 causal_itemA == "sit down" ~ "action", 
                                 causal_itemA == "jump up and down" ~ "action",
                                 causal_itemA == "kick something" ~ "action",
                                 causal_itemA == "take a walk" ~ "action",
                                 causal_itemA == "get tired" ~ "bio", 
                                 causal_itemA == "become hungry" ~ "bio",
                                 causal_itemA == "feel scared"~ "bio",
                                 causal_itemA == "experience pain"~ "bio",
                                 causal_itemA == "get sick"~ "bio"),
          domain_similarityitemA = case_when(similar_itemA == "hear something" ~ "mind", 
                                 similar_itemA == "choose what to do" ~ "mind",
                                 similar_itemA == "remember something" ~ "mind",
                                 similar_itemA == "think about something" ~ "mind",
                                 similar_itemA == "see something" ~ "mind",
                                 similar_itemA == "reach for something" ~ "action",
                                 similar_itemA == "sit down" ~ "action", 
                                 similar_itemA == "jump up and down" ~ "action",
                                 similar_itemA == "kick something" ~ "action",
                                 similar_itemA == "take a walk" ~ "action",
                                 similar_itemA == "get tired" ~ "bio", 
                                 similar_itemA == "become hungry" ~ "bio",
                                 similar_itemA == "feel scared"~ "bio",
                                 similar_itemA == "experience pain"~ "bio",
                                 similar_itemA == "get sick"~ "bio")) 

```

### demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$filename)
summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

  
```

## main figure or plot

```{r}
dat_summarized <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  # mutate(condition = ifelse(condition == "preceding", "Making Someone do Something", "Giving Creature Ability")) %>%
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

main_fig <- dat_summarized %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000")) + #or whatever you'd like!
  scale_x_discrete(labels = c("Giving Creature Ability" = "granting", 
                              "Making Someone do Something" = "causing")) +
    geom_errorbar(data = filter(dat_summarized, response == "causal"), aes(ymax = mean_proportion + se,
                                                                           ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
    theme_cowplot() +
  labs(y = "Proportion",
       x = "Causal Event Type",
       fill = "Response",
       title = "Inference") +
  ylim(0, 1) +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),

        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent', color = NA),
        legend.box.background = element_rect(fill='transparent', color = NA),
        
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm"),
        
        plot.title = element_text(hjust = 0.5, size = 25)
        ) 

main_fig

# main_fig <- ggsave("spp_study6.png", width = 5, height = 5, plot = main_fig, bg = "transparent")
main_fig <- ggsave("figures/inference.png", width = 6, height = 5, plot = main_fig, bg = "white")

```

## item-level plot, includes distances in plot

## plot-preceding

```{r, fig.width = 12, fig.height = 12}
d_distances <- read_csv(preceding_distances_path)

dat_pre <- dat %>% 
  mutate(condition = as.character(condition),
         itemB = as.character(itemB),
         causal_itemA = as.character(causal_itemA),
         similar_itemA = as.character(similar_itemA)) %>% 
  filter(condition == "preceding")

dat_summarized_by_item <- dat_pre %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  tidyr::complete(response, nesting(condition, itemB, 
                                    causal_itemA, similar_itemA,
                                    domain_causalitemA, domain_similarityitemA,
                                    domain_itemB), fill = list(count = 0)) %>% #fill empty responses
  group_by(condition, itemB) %>%
  mutate(total = n()) %>%  #get total responses per condition
  ungroup() %>% 
  group_by(condition, itemB, response) %>%
  mutate(
    count = n(),  #count responses for each response type
    total = first(total),  #total responses for the condition
    mean_proportion = count / total,  #prop response within condition
    se = sqrt(mean_proportion * (1 - mean_proportion) / total)) %>%
  distinct(condition, itemB, .keep_all = TRUE) %>%
  select(-subject_id) %>%
  ungroup()

dat_labels <- dat_summarized_by_item %>% 
  distinct(itemB, causal_itemA, similar_itemA) %>% 
  left_join(d_distances %>% #join distances
              rename("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice) %>% 
              select(itemB, causal_itemA, similar_itemA,
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar), 
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2)) %>% 
  mutate(facet_label = paste0(
    itemB, "\n",
    "", causal_itemA, "\n", 
    "", similar_itemA   
  )) %>% 
  mutate(facet_label = paste0(itemB, "\n",
                              "causal: ", causal_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice, ",",
                              freesort_distance_causal_choice, ",",
                              freesort_minus_causal_distance_causal, ")", "\n",  
                              "similar: ", similar_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice, ",",
                              freesort_distance_similar_choice, ",",
                              freesort_minus_causal_distance_similar, ")", "\n"))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

dat_summarized_by_item_levels <- dat_summarized_by_item %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>% 
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_inference_pre <-  dat_summarized_by_item_levels %>% 
  ggplot(aes(x =condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity") +
  geom_bar(stat = "identity", colour = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_errorbar(data = filter(dat_summarized_by_item_levels, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  scale_fill_manual(values = c("grey80", "#000000")) +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 25),
        strip.text = element_text(size = 15)) +
  labs(y = "proportion",
       title = "Inference - Preceding") +
  facet_wrap(~facet_label, nrow = 3) 

p_inference_pre

ggsave(
  filename = "figures/p_inference_preceding_item-level_stacked.pdf",
  plot = p_inference_pre,
  device = "pdf",
  width = 20,
  height = 15,
  units = "in")
# 
ggsave(
  filename = "figures/p_inference_preceding_item-level_stacked.png",
  plot = p_inference_pre,
  bg = "white",
  width = 20,
  height = 15,
  units = "in")

```


### item-level - following

```{r, fig.width = 12, fig.height = 12}
d_distances <- read_csv(following_distances_path)

dat_fol <- dat %>% 
  mutate(condition = as.character(condition),
         itemB = as.character(itemB),
         causal_itemA = as.character(causal_itemA),
         similar_itemA = as.character(similar_itemA)) %>% 
  filter(condition == "following")

dat_summarized_by_item <- dat_fol %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  tidyr::complete(response, nesting(condition, itemB, 
                                    causal_itemA, similar_itemA,
                                    domain_causalitemA, domain_similarityitemA,
                                    domain_itemB), fill = list(count = 0)) %>% #fill empty responses
  group_by(condition, itemB) %>%
  mutate(total = n()) %>%  #get total responses per condition
  ungroup() %>% 
  group_by(condition, itemB, response) %>%
  mutate(
    count = n(),  #count responses for each response type
    total = first(total),  #total responses for the condition
    mean_proportion = count / total,  #prop response within condition
    se = sqrt(mean_proportion * (1 - mean_proportion) / total)) %>%
  distinct(condition, itemB, .keep_all = TRUE) %>%
  select(-subject_id) %>%
  ungroup()

dat_labels <- dat_summarized_by_item %>% 
  distinct(itemB, causal_itemA, similar_itemA) %>% 
  left_join(d_distances %>% #join distances
              rename("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice) %>% 
              select(itemB, causal_itemA, similar_itemA,
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar), 
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2)) %>% 
  mutate(facet_label = paste0(
    itemB, "\n",
    "", causal_itemA, "\n", 
    "", similar_itemA   
  )) %>% 
  mutate(facet_label = paste0(itemB, "\n",
                              "causal: ", causal_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice, ",",
                              freesort_distance_causal_choice, ",",
                              freesort_minus_causal_distance_causal, ")", "\n",  
                              "similar: ", similar_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice, ",",
                              freesort_distance_similar_choice, ",",
                              freesort_minus_causal_distance_similar, ")", "\n"))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

dat_summarized_by_item_levels <- dat_summarized_by_item %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>% 
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_inference_foll <-  dat_summarized_by_item_levels %>% 
  ggplot(aes(x =condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity") +
  geom_bar(stat = "identity", colour = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_errorbar(data = filter(dat_summarized_by_item_levels, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  scale_fill_manual(values = c("grey80", "#000000")) +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 25),
        strip.text = element_text(size = 15)) +
  labs(y = "proportion",
       title = "Inference - Following") +
  facet_wrap(~facet_label, nrow = 3) 

p_inference_foll

ggsave(
  filename = "figures/p_inference_following_item-level_stacked.pdf",
  plot = p_inference_foll,
  device = "pdf",
  width = 20,
  height = 15,
  units = "in")
#
ggsave(
  filename = "figures/p_inference_following_item-level_stacked.png",
  plot = p_inference_foll,
  bg = "white",
  width = 20,
  height = 15,
  units = "in")

```


# Primary Analysis

## Logistic regression

```{r}
d_model <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(subject_id = factor(subject_id))

model_effect_of_order <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_effect_of_order)

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_effect_of_order)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```


## Power analysis with simr

### Analysis

Detecting condition difference

```{r}
#suppose we want a study with 150 participants..
model_sim <- extend(model_effect_of_order, along = "subject_id", n = 150)
length(unique(simr::getData(model_sim)$subject_id)) #confirm that N is now 150

# #2
curve_preceding_vs_following <- powerCurve(model_sim, fixed("conditionpreceding",
                                               "z"),
                    along = "subject_id", breaks = c(1, 5, 10, 20, 30, 40, 50,
                                                     60, 70, 80, 90, 100,
                                                     110, 120, 130, 140, 150), nsim = 100)


```

### Plotting power curve

```{r}
plot(curve_preceding_vs_following)
print(curve_preceding_vs_following)

```

### Following-only

```{r}
d_model_following <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "following") %>% 
  mutate(condition = factor(condition))

# write_csv(d_model_following, file = "following.csv")

model_following <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_following)

summary(model_following)

plogis(fixef(model_following)[1])

# Power Analysis
model_sim <- extend(model_following, along = "subject_id", n = 150)
length(unique(simr::getData(model_sim)$subject_id)) #confirm that N is now 100

# #2
curve_following <- powerCurve(model_sim, fixed("(Intercept)",
                                               "z"),
                    along = "subject_id", breaks = c(1, 5, 10, 20, 30, 40, 50,
                                                     60, 70, 80, 90, 100,
                                                     110, 120, 130, 140, 150), nsim = 100)

plot(curve_following)
print(curve_following)

```

```{r}

```




