---
title: "experiment1 preprocessing"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      number_sections: true
date: "2024-7-7"
author: anonymous
---

This script does the following:  
1. Combines raw data from the pilot and main studies `pilot_data_raw.csv` and `data_raw.csv`. The codebooks for the raw datasets are available at `data/experiment1_data_raw_codebook` and XXX (generate codebook for the other one!)  
2. Parses it into a combined (i.e. freesort + causation) data frame and saves into csv `combined_data_processed_step1.csv`. The codebook for this data frame is available at `/snapshots_experiment1_preprocessing_analysis/data_processed_step1_codebook`.  

Study description:    
- Pilot was ran on 12/13/24 on Connect CloudResearch, N = 50 participants.
- Main study was ran 6/30/25 on Connect CloudResearch, N = 102 participants.
- Subject selection criteria: 95% approval rate, minimum 10 previous submissions, and fluent in English. 
- NB: Total N should be reported as 152, not 155 as is in preregistrations, since we lost N = 3 in main round to technical issues with datapipe.

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse, here, corrplot, jsonlite)

sessionInfo()

```

# Read data

```{r}
base_path <- here("code")

data_path_1 <- paste0(base_path, "/data/1_measure/data_raw.csv")
data_path_2 <- paste0(base_path, "/data/1_measure/pilot_data_raw.csv")

d1 <- read_csv(data_path_1, col_types = cols(
  .default = col_guess(),
  final_locations = col_character(),
  init_locations = col_character(),
  moves = col_character()
))

d2 <- read_csv(data_path_2, col_types = cols(
  .default = col_guess(),
  final_locations = col_character(),
  init_locations = col_character(),
  moves = col_character()
)) %>% 
  mutate(subject_id = sprintf("subj_%03d", dense_rank(subject_id) + 102)) 

d_combined <- bind_rows(d1, d2)

d <- d_combined

```

# Set variables

```{r}
items <- c("choose what to do", "reach for something", "feel scared",  #items in exact order of img1.png to img15.png used in sort task
           "experience pain", "get sick", "get tired", "become hungry", 
           "see something", "think about something", "hear something", 
           "remember something", "jump up and down", "kick something", 
           "take a walk", "sit down")

# desired_order <- c("see something", "hear something", "choose what to do", #ordering by domain
#                    "remember something", "think about something", "reach for something", 
#                    "sit down", "jump up and down", "kick something", "take a walk", 
#                    "get tired", "become hungry", "feel scared", "experience pain", "get sick")

desired_order <- c("see something", "hear something", "choose what to do", 
                  "remember something", "think about something", "reach for something", 
                  "kick something", "sit down", "jump up and down", "take a walk", 
                  "feel scared","experience pain", "get tired", "become hungry","get sick")

#paths: data outputs
analysis_path <- paste0(base_path, "/analysis/1.5_item_selection")
combined_output_csv <- "combined_data_processed_step1"
snapshots_path <- paste0(analysis_path, "/snapshots_experiment1_preprocessing_analysis")
combined_output_path <- paste0(snapshots_path, "/", combined_output_csv, ".csv") 

```


# Parse data frames

## Parse Sorting Task data

```{r}
data_freesort <- d %>%
  filter(trial_type == "freesort") %>% 
  select(subject_id, trial_index, final_locations) %>% 
  mutate(parsed_location = map(final_locations, ~ fromJSON(.))) %>% #parse JSON
  unnest(parsed_location) %>% #unnest the list column
  mutate(
    img_number = as.numeric(str_extract(src, "\\d+")), #etract image numbers from `src`
    item = items[img_number] #map image numbers to item labels
  ) %>%
  select(-c("final_locations", "src", "img_number")) %>% 
  mutate(trial_type = "freesort") %>% 
  relocate(trial_type, .after = subject_id) %>% 
  rename(original_trial_index = trial_index)

#write.csv(data_freesort, file = freesort_output_path, row.names = F)
```

## Parse Causal Pairs Task data

```{r}
response_data <- d %>%
  filter(trial_type == "survey-slider") %>% 
  select(subject_id, trial_index, response) %>%
  mutate(response = map(response, ~ tryCatch(
    fromJSON(.) %>%
      enframe(name = "question_id", value = "response"),
    error = function(e) tibble(question_id = character(), response = character())
  ))) %>%
  unnest(response) %>% 
  mutate(
    response = unlist(response), 
    response = as.numeric(response), 
    question_index = str_remove(question_id, "Q") 
  ) %>%
  select(subject_id, trial_index, question_index, response)

metadata_data <- d %>%
  select(subject_id, trial_index, `0`:`14`, `15`) %>% 
  pivot_longer(
    cols = -c(subject_id, trial_index),  
    names_to = "question_index",      
    values_to = "metadata"            
  ) %>% 
  mutate(
    parsed_metadata = map(metadata, ~ {
      if (is.na(.x)) {
        tibble() # Handle NA metadata
      } else {
        fromJSON(.x, simplifyVector = FALSE) %>%
          map(~ if (is.null(.)) NA else .) %>%  #replace NULL with NA
          as_tibble()
      }
    })
  ) %>% 
  unnest(parsed_metadata) %>%    
  select(-metadata)           

#merge the response_data and metadata_data into data_causal_pairs
data_causal_pairs <- response_data %>%
  inner_join(metadata_data, by = c("subject_id", "trial_index", "question_index")) %>% 
  mutate(trial_type = "causal_pairs") %>% 
  relocate(trial_type, .after = subject_id) %>%
  rename(original_trial_index = trial_index, 
         original_question_index = question_index) %>% 
  group_by(subject_id, trial_type) %>%
  mutate(trial_index = dense_rank(original_trial_index),
         question_index = row_number()) %>%
  ungroup() %>% 
  relocate(c("trial_index", "question_index"), .after = "trial_type") %>% 
  relocate(c("original_trial_index", "original_question_index"), .after = "correct_response")

```

## Exclusions

- In Causal Pairs Task we have 4 attention checks at pages 4, 8, 10 and 13. No attention checks in Sorting Task 
- We are excluding subjects who fail at least 2 attention checks (Other possible criteria: time taken to complete study)

```{r}
data_causal_pairs <- data_causal_pairs %>%
  mutate(attention_check_id = case_when(
    attention_check == TRUE & trial_index == 4  ~ 1, 
    attention_check == TRUE & trial_index == 8  ~ 2, 
    attention_check == TRUE & trial_index == 10 ~ 3, 
    attention_check == TRUE & trial_index == 13 ~ 4, 
    TRUE ~ NA_integer_ #non-attention check rows
  )) %>%
  mutate(correct_response = case_when(
    attention_check == TRUE & trial_index == 4  ~ 0, #"Move slider all the way to left"
    attention_check == TRUE & trial_index == 8  ~ 75,  #"Move slider to 'Maybe yes'"
    attention_check == TRUE & trial_index == 10 ~ 100, #"Move slider all the way to right"
    attention_check == TRUE & trial_index == 13 ~ 0,   #"Move slider to 'Definitely not'"
    TRUE ~ correct_response # Retain existing values for non-attention check rows
  )) %>%
  mutate(correct = case_when(
    attention_check == TRUE & trial_index == 4  & response >= 0 & response <= 5   ~ TRUE, 
    attention_check == TRUE & trial_index == 8  & response >= 70 & response <= 80 ~ TRUE, 
    attention_check == TRUE & trial_index == 10 & response >= 0 & response <= 5 ~ TRUE, #3 and 4 are switched for some reason
    attention_check == TRUE & trial_index == 13 & response >= 95 & response <= 100   ~ TRUE,
    attention_check == TRUE ~ FALSE, #outside acceptable range
    TRUE ~ NA #non-attn check rows
  ))

excluded_participants <- data_causal_pairs %>%
  filter(attention_check == TRUE) %>% 
  group_by(subject_id) %>% 
  summarize(
    num_incorrect = sum(correct == FALSE, na.rm = TRUE), 
    .groups = "drop"
  ) %>%
  filter(num_incorrect >= 2) %>% #identify participants with x or more incorrect
  pull(subject_id) 

data_causal_pairs <- data_causal_pairs %>%
  filter(!subject_id %in% excluded_participants)

data_freesort <- data_freesort %>%
  filter(!subject_id %in% excluded_participants)

#excluded 1 subject: subj_14

```

## Add trial order column

```{r}
#Combine trial types to compare their starting original_trial_index
trial_order_info <- bind_rows(
  data_causal_pairs %>% distinct(subject_id, trial_type, original_trial_index),
  data_freesort %>% distinct(subject_id, trial_type, original_trial_index)
) %>%
  group_by(subject_id) %>%
  summarize(
    trial_type_order = case_when(
      min(original_trial_index[trial_type == "causal_pairs"]) < min(original_trial_index[trial_type == "freesort"]) ~ 
        list(c(causal_pairs = "first", freesort = "second")),
      TRUE ~ list(c(causal_pairs = "second", freesort = "first"))
    )
  ) %>%
  unnest_wider(trial_type_order)

#Add trial_type_order to data_causal_pairs
data_causal_pairs <- data_causal_pairs %>%
  left_join(
    trial_order_info %>% select(subject_id, causal_pairs),
    by = "subject_id"
  ) %>%
  rename(trial_type_order = causal_pairs) %>%
  relocate(trial_type_order, .after = trial_type)

# Add trial_type_order to data_freesort
data_freesort <- data_freesort %>%
  left_join(
    trial_order_info %>% select(subject_id, freesort),
    by = "subject_id"
  ) %>%
  rename(trial_type_order = freesort) %>%
  relocate(trial_type_order, .after = trial_type)

```

## Create combined data frame 

```{r}
data_combined <- bind_rows(
  data_causal_pairs,
  data_freesort
)

assign(combined_output_csv, data_combined)

write.csv(data_combined, combined_output_path, row.names = F)

```

THE END

```{r}

```


