---
title: "Item selection"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-07-16"
author: Joseph Outa
---

# Setup

## Load packages

```{r, setup, include = FALSE}
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

# paths
## script inputs
base_path <- here("code", "analysis", "1.5_item_selection")
snapshots_input_path <- paste0(base_path, "/snapshots_experiment1_combined_analysis") 
data_input_path <- paste0(snapshots_input_path, "/combined_data_processed_step2.csv")
freesort_minus_causal_pairs_distances_output_path <- paste0(snapshots_input_path, "/freesort_minus_causals.csv")
snapshots_output_path <- paste0(base_path, "/figures/item-selection/") #for saving item selection csvs

```

## Read data

```{r}
df_combined <- read_csv(data_input_path)

#how many subjects
df_combined %>% 
  slice(length(df_combined$subject_id)) %>% 
  pull(subject_id)

rmarkdown::paged_table(df_combined)

```

# Experiment 2 (Explanation), 3 (Counterfactual), and 5 (Intervention) - Preceding causes

### Select long list 

```{r}
#get mean distances by item pairs
df_pair_means <- df_combined %>% 
  select(subject_id, itemA, itemB, freesort_distance, causal_pairs_distance) %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>%
  summarize(mean_causal_pairs_distance = mean(causal_pairs_distance, na.rm = TRUE),
         mean_freesort_distance = mean(freesort_distance, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # mutate(mean_causal_pairs_distance = (mean_causal_pairs_distance - min(mean_causal_pairs_distance)) / (max(mean_causal_pairs_distance) - min(mean_causal_pairs_distance)), 
  # mean_freesort_distance = (mean_freesort_distance - min(mean_freesort_distance)) / (max(mean_freesort_distance) - min(mean_freesort_distance))) %>% #re-normalizess
  separate(item_pairs, c("itemA", "itemB"), sep = "_")

#add domain labels
df_item_pair_means_domain <- df_pair_means %>%
  left_join(df_combined %>% 
              select(itemA, itemB, domain_itemA, domain_itemB) %>% 
              distinct(),
              by = c("itemA", "itemB")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order))

df_item_pair_means_domain_long <- df_item_pair_means_domain %>% 
  pivot_longer(
    cols = c("mean_causal_pairs_distance", "mean_freesort_distance"),
    names_to = "mean_type",
    values_to = "values") 

df_item_pair_means_freesort_minus_causal <- df_item_pair_means_domain_long %>% 
  pivot_wider(names_from = "mean_type",
              values_from = "values") %>% 
  mutate(freesort_minus_causal = mean_freesort_distance - mean_causal_pairs_distance)

df_item_pair_means_freesort_minus_causal

#save as csv
write.csv(df_item_pair_means_freesort_minus_causal,
          freesort_minus_causal_pairs_distances_output_path, row.names = F)

```

### Plot long list table

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemB) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemB) %>% 
  rename("cd" = mean_causal_pairs_distance,
         "fd" = mean_freesort_distance,
         "fd_minus_cd" = freesort_minus_causal) %>% 
  mutate(cd = round(cd, 2),
         fd = round(fd, 2),
         fd_minus_cd = round(fd_minus_cd, 2)) %>% 
  relocate(fd, .before = cd)

#Generate a unique color for each itemB
unique_items <- unique(long_list_items$itemB)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemB,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/preceding_long-list.png")


```

### Select short list 


```{r}
CO_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemB) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

CC_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemB) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
#join
short_list_selected_items_domain_constraints <- CC_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_pairs_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(CC_item = itemA,
         causal_pairs_distance_CC_item = mean_causal_pairs_distance,
         freesort_distance_CC_item = mean_freesort_distance,
         freesort_minus_causal_pairs_distance_CC = freesort_minus_causal) %>% 
  left_join(CO_items_same_domain %>% 
              select(itemA, itemB, mean_causal_pairs_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(CO_item = itemA, 
                     causal_pairs_distance_CO_item = mean_causal_pairs_distance,
                     freesort_distance_CO_item = mean_freesort_distance,
                     freesort_minus_causal_pairs_distance_CO = freesort_minus_causal),
            by = "itemB") %>% 
  relocate("CO_item", .after = "CC_item") %>% 
  relocate("itemB", .before = "CC_item") %>% 
  rename(target_item = itemB) %>% 
  mutate(causal_pairs_distance_CC_item = round(causal_pairs_distance_CC_item, 2),
         freesort_distance_CC_item = round(freesort_distance_CC_item, 2),
         causal_pairs_distance_CO_item = round(causal_pairs_distance_CO_item, 2),
         freesort_distance_CO_item = round(freesort_distance_CO_item, 2),
         freesort_minus_causal_pairs_distance_CC = round(freesort_minus_causal_pairs_distance_CC, 2),
         freesort_minus_causal_pairs_distance_CO = round(freesort_minus_causal_pairs_distance_CO, 2))

#view items
paged_table(short_list_selected_items_domain_constraints)

#save as csv
write_csv(file = "snapshots_experiment1_combined_analysis/preceding_short_list.csv",
          short_list_selected_items_domain_constraints)

```

### Plot short list table

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"),
    CC_item = paste0(CC_item, " (", causal_pairs_distance_CC_item, ", ", freesort_distance_CC_item, ", ", freesort_minus_causal_pairs_distance_CC, ")"),
    CO_item = paste0(CO_item, " (", causal_pairs_distance_CO_item, ", ", freesort_distance_CO_item, ", ", freesort_minus_causal_pairs_distance_CO, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #db9728; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #d0495a; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #00788a; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item)) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, CC_item, CO_item)  


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and CC/CO Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    CC_item = md("CC item<br>(CP distance, Freesort distance, joint distance)"),
    CO_item = md("CO item<br>(CP distance, Freesort distance, joint distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  
  fmt_markdown(columns = c(CC_item, CO_item)) %>%
  
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#db9728", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "mind")) %>%
  tab_style(
    style = list(
      cell_text(color = "#d0495a", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "action")) %>%
  tab_style(
    style = list(
      cell_text(color = "#00788a", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "body")) %>%
  tab_options(
    table.font.names = "Arial")

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/preceding_short-list.png")
```

# Experiment 5 (Prediction) - Following causes

## Plot long list table

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemA) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemA)

#Generate a unique color for each itemA
unique_items <- unique(long_list_items$itemA)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemA,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/following_long-list.png")

```

## Select short list 

```{r}
CO_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemA) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

CC_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemA) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
#join
short_list_selected_items_domain_constraints <- CC_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_pairs_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(CC_item = itemB,
         causal_pairs_distance_CC_item = mean_causal_pairs_distance,
         freesort_distance_CC_item = mean_freesort_distance,
         freesort_minus_causal_pairs_distance_CC = freesort_minus_causal) %>% 
  left_join(CO_items_same_domain %>% 
              select(itemA, itemB, mean_causal_pairs_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(CO_item = itemB, 
                     causal_pairs_distance_CO_item = mean_causal_pairs_distance,
                     freesort_distance_CO_item = mean_freesort_distance,
                     freesort_minus_causal_pairs_distance_CO = freesort_minus_causal),
            by = "itemA") %>% 
  relocate("CO_item", .after = "CC_item") %>% 
  relocate("itemA", .before = "CC_item") %>% 
  rename(target_item = itemA) %>% 
  mutate(causal_pairs_distance_CC_item = round(causal_pairs_distance_CC_item, 2),
         freesort_distance_CC_item = round(freesort_distance_CC_item, 2),
         causal_pairs_distance_CO_item = round(causal_pairs_distance_CO_item, 2),
         freesort_distance_CO_item = round(freesort_distance_CO_item, 2),
         freesort_minus_causal_pairs_distance_CC = round(freesort_minus_causal_pairs_distance_CC, 2),
         freesort_minus_causal_pairs_distance_CO = round(freesort_minus_causal_pairs_distance_CO, 2))

write_csv(file = "snapshots_experiment1_combined_analysis/following_short_list.csv",
          short_list_selected_items_domain_constraints)

#view items
paged_table(short_list_selected_items_domain_constraints)


```

## Plot short list table

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    CC_item = paste0(CC_item, " (", causal_pairs_distance_CC_item, ", ", freesort_distance_CC_item, ", ", freesort_minus_causal_pairs_distance_CC, ")"),
    CO_item = paste0(CO_item, " (", causal_pairs_distance_CO_item, ", ", freesort_distance_CO_item, ", ", freesort_minus_causal_pairs_distance_CO, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #db9728; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #d0495a; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #00788a; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, CC_item, CO_item)  # Keep the domain column


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and CC/CO Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    CC_item = md("CC item<br>(CP distance, Freesort distance, joint distance)"),
    CO_item = md("CO item<br>(CP distance, Freesort distance, joint distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(CC_item, CO_item)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#db9728", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#d0495a", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#00788a", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/following_short-list.png")
```

# Experiment 6 (Biological Reasoning v Causal Triads) - Middle items

## First extract distances (renormalized)

```{r}
#get mean distances by item pairs
df_pair_means <- df_combined %>% 
  select(subject_id, itemA, itemB, freesort_distance, causal_pairs_distance) %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>%
  summarize(mean_causal_pairs_distance = mean(causal_pairs_distance, na.rm = TRUE),
         mean_freesort_distance = mean(freesort_distance, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(mean_causal_pairs_distance = (mean_causal_pairs_distance - min(mean_causal_pairs_distance)) / (max(mean_causal_pairs_distance) - min(mean_causal_pairs_distance)),
  mean_freesort_distance = (mean_freesort_distance - min(mean_freesort_distance)) / (max(mean_freesort_distance) - min(mean_freesort_distance))) %>% #re-normalizess
  separate(item_pairs, c("itemA", "itemB"), sep = "_")

#add domain labels
df_item_pair_means_domain <- df_pair_means %>%
  left_join(df_combined %>% 
              select(itemA, itemB, domain_itemA, domain_itemB) %>% 
              distinct(),
              by = c("itemA", "itemB")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order))

df_item_pair_means_domain_long <- df_item_pair_means_domain %>% 
  pivot_longer(
    cols = c("mean_causal_pairs_distance", "mean_freesort_distance"),
    names_to = "mean_type",
    values_to = "values") 

df_item_pair_means_freesort_minus_causal <- df_item_pair_means_domain_long %>% 
  pivot_wider(names_from = "mean_type",
              values_from = "values") %>% 
  mutate(freesort_minus_causal = mean_freesort_distance - mean_causal_pairs_distance)

df_item_pair_means_freesort_minus_causal

```

## Create long list of items

For the Causal Chain vs Common Cause experiment, we did the following:   
- first we visually identified incomplete (i.e. cause rating < 0.5) causal paths between two pairs of items. 
- we identified 9 such pairs. These became the 9 pairs of target items that formed our 9 trials. Each trial has 2 target items, a first event, and a second event (which we sometimes call third, because there are 3 events with a missing middle), and subjects will be tasked with selecting the middle item. 
- We then selected the causal item as such: for each of the two target items, we computed their mean causal pairs distance with all other possible 13 items, e.g. mean(target 1 - x1, target 2 - x1), mean(target 1 - x2, target 2, x2)...and so on until x13. The middle item x[n] with the lowest mean causal pairs distance became the CC item. 
- We then selected the similar item as such: we rank ordered the mean freesort distance between the two targets and all other items e.g. mean(target 1 - x1, target 2 - x1)...mean(target 1 - x2, target 2 - x2)...and so on until x13. The x[n] with the lowest mean distance became the CO item. (or as it were, the Latent Item)

```{r}
distances <- df_item_pair_means_freesort_minus_causal

best_middle <- function(distances, first, third,
                        metric = freesort_minus_causal,
                        pick = c("min","max")) {
  pick <- match.arg(pick)

  triad_means <- distances %>%
    select(-c(domain_itemA, domain_itemB)) %>%
    mutate(itemA = as.character(itemA),
           itemB = as.character(itemB)) %>%
    filter((itemA == first & itemB != third) |
           (itemB == third & itemA != first)) %>%
    mutate(other_item = ifelse(itemA == first, itemB, itemA)) %>%
    group_by(other_item) %>%
    summarise(mean_joint = mean({{ metric }}), .groups = "drop") %>%
    arrange(if (pick == "max") mean_joint else desc(mean_joint))

  list(
    best = triad_means %>% slice(1) %>% pull(other_item),
    ranking = triad_means)
}

targets <- tibble::tribble(
  ~first,               ~third,
  "see something",      "hear something",
  "choose what to do",  "hear something",
  "remember something", "hear something",
  "sit down",           "jump up and down",
  "jump up and down",   "sit down",
  "take a walk",        "reach for something",
  "get tired",          "feel scared",
  "become hungry",      "feel scared",
  "get sick",           "become hungry"
)

all_rankings <- targets %>%
  mutate(middle_items = map2(first, third, ~best_middle(distances, .x, .y, pick = "min")$ranking)) %>%
  unnest(middle_items) %>%
  group_by(first, third) %>%
  mutate(rank = row_number()) %>%
  ungroup() 

distances_causal_chain_common_causes <- all_rankings %>% 
  rename("first_item" = first,
         "third_item" = third,
         "middle_item" = other_item,
         "freesort_minus_causal_pairs_distance" = mean_joint)

paged_table(distances_causal_chain_common_causes)

write.csv(distances_causal_chain_common_causes, "snapshots_item_selection/mean_joint_distances_experiment_6.csv") #will be used as input to experiment 6 exploratory distance analyses

```

## Select extreme items

```{r}
#for causal chain item
causal_chain_items <- all_rankings %>%
  group_by(first, third) %>%
  slice(1) %>%
  ungroup()

causal_chain_items

#for causal origin item item
causal_origin_items <- all_rankings %>%
  group_by(first, third) %>%
  slice(n()) %>%
  ungroup()

causal_origin_items

#NB: To avoid repeats, we manually re-selected some of these items e.g. for "remember" (first) to "hear" (third), we used "scared" instead of "walk" because "walk" was repeated in the last 2 items. 

item_table <- tribble(
  ~domain, ~first_target, ~second_target, ~cc_item, ~cc_distance, ~co_item, ~co_distance,
  "mind", "see something", "hear something", "take a walk", 0.581, "remember something", 0.052,
  "mind", "choose what to do", "hear something", "take a walk", 0.492, "see something", -0.126,
  "mind", "remember something", "hear something", "feel scared", 0.458, "think about something", -0.086,
  "action", "sit down", "jump up and down", "experience pain", 0.401, "take a walk", -0.568,
  "action", "jump up and down", "sit down", "get tired", 0.664, "take a walk", -0.398,
  "action", "take a walk", "reach for something", "see something", 0.545, "jump up and down", -0.330,
  "body", "get tired", "feel scared", "choose what to do", 0.532, "become hungry", -0.118,
  "body", "become hungry", "feel scared", "think about something", 0.699, "get tired", -0.058,
  "body", "get sick", "become hungry", "remember something", 0.518, "experience pain", -0.052
) %>%
  group_by(domain) %>%
  mutate(domain_display = ifelse(row_number() == 1, domain, "")) %>%
  ungroup() %>%
  select(domain_display, first_target, second_target, cc_item, cc_distance, co_item, co_distance)

#Final list of items
paged_table(item_table)

```

## Save items in table

```{r}
color_item <- function(item) {
  case_when(
    item %in% c("see something", "hear something", "remember something",
                "think about something", "choose what to do") ~
      paste0("<span style='color:#db9728;font-weight:bold;'>", item, "</span>"),

    item %in% c("reach for something", "sit down", "jump up and down",
                "kick something", "take a walk") ~
      paste0("<span style='color:#d0495a;font-weight:bold;'>", item, "</span>"),

    item %in% c("get tired", "become hungry", "feel scared",
                "experience pain", "get sick") ~
      paste0("<span style='color:#00788a;font-weight:bold;'>", item, "</span>"),

    TRUE ~ item
  )
}

item_table <- item_table %>%
  mutate(
    first_target = color_item(first_target),
    second_target = color_item(second_target)
  )

item_table_gt <- item_table %>%
  gt() %>%
  cols_label(
    domain_display = "domain",
    first_target = "First target",
    second_target = "Second target",
    cc_item = "CC item",
    cc_distance = md("Mean<br>joint<br>distance"),
    co_item = "CO item",
    co_distance = md("Mean<br>joint<br>distance")
  ) %>%
  tab_spanner(
    label = "Target items",
    columns = c(first_target, second_target)
  ) %>%
  tab_spanner(
    label = "Middle item in forced-choice response",
    columns = c(cc_item, cc_distance, co_item, co_distance)
  ) %>%
  fmt_markdown(
    columns = c(first_target, second_target)
  ) %>% 
  fmt_number(
    columns = c(cc_distance, co_distance),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_text(color = "#db9728", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "mind")
  ) %>%
  tab_style(
    style = cell_text(color = "#d0495a", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "action")
  ) %>%
  tab_style(
    style = cell_text(color = "#00788a", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "body")
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", align = "center"),
    locations = cells_column_spanners()
  ) %>%
  tab_options(
    table.font.names = "Arial",
    # table.font.size = px(22),
    table.border.top.width = px(2),
    table.border.bottom.width = px(2),
    column_labels.border.top.width = px(2),
    column_labels.border.bottom.width = px(2),
    data_row.padding = px(10)
  ) #%>%
#  opt_table_lines(extent = "all")

item_table_gt

gtsave(
  item_table_gt,
  "figures/item-selection/experiment_6.png"
)
```

# All Experiments - Demographics table

```{r}

experiment_table <- tribble(
  ~measure, ~experiment_1, ~experiment_2, ~experiment_3, ~experiment_4, ~experiment_5, ~experiment_6,
  "N after exclusions", "101", "104", "102", "102", "105", "104",
  "N excluded (reason)", "1 (failed attention check)", "1 (failed attention check)", "3 (failed attention check)", "5 (failed attention check)", "0", "0",
  "Mean age (min, max)", "38.06 (19, 73)", "40.10 (20, 80)", "41.07 (21, 70)", "42.73 (19, 79)", "41.5 (19, 79)", "42.61 (18, 75)",
  "Female", "41", "41", "53", "63", "59", "56",
  "Male", "60", "63", "52", "38", "45", "45",
  "Non-binary", "1", "3", "1", "NA", "NA", "1",
  "White", "73", "74", "82", "79", "85", "80",
  "Black/African American", "17", "9", "8", "8", "6", "8",
  "Asian", "8", "15", "12", "13", "12", "10",
  "Latino/Hispanic", "2", "1", "1", "NA", "NA", "NA",
  "Other", "7", "NA", "1", "5", "2", "6")

experiment_table_gt <- experiment_table %>%
  gt() %>%
  cols_label(
    measure = "",
    experiment_1 = md("Experiment 1<br>(Measure)"),
    experiment_2 = md("Experiment 2<br>(Explanation)"),
    experiment_3 = md("Experiment 3<br>(Counterfactuals)"),
    experiment_4 = md("Experiment 4<br>(Inference v Prediction)"),
    experiment_5 = md("Experiment 5<br>(Magical v Ordinary Intervention)"),
    experiment_6 = md("Experiment 6<br>(Biological Reasoning v Causal Triads)")
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = measure)
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

experiment_table_gt

gtsave(
  experiment_table_gt,
  "figures/item-selection/all_experiments_demographics.png"
)

```

# THE END

```{r}
#placeholder
```

