---
title: "Causal Chain"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-12-18"
author: Joseph Outa
---

# ReadMe

- This is the analysis script for the Causal Chain vs Intrinsic Cause study.  
- Date run: 12/18/25
- N = 105 before exclusions
- 2 between-subjects conditions
- DV: Someone x, which made them _, which made them y. Fill the blank (Causal Chain), a gene makes a creature x, _, and z. Fill the blank (Intrinsic Cause), IV: Binary choice between direct vs intrinsic item.   
- Hypothesis: subjects choose direct item when completing causal chain and intrinsic item when reasoning about behavioral effects of biological causes

# Setup

## Load packages

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               effectsize,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
theme_set(theme_bw())
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code", "main")

study_path <- paste0(base_path, "/analysis/causal-chain")

data_path <- paste0(base_path, "/data/causal-chain/JO-mbc-main-cc-v2-105N")

snapshots_input_path_distances <- paste0(base_path,
                                         "/analysis/measure-main-and-pilot/snapshots_study1_main_analysis")

distances_path <- paste0(snapshots_input_path_distances,
                                   "/freesort_minus_causals.csv")

desired_order <- c("see something", "choose what to do", "remember something", 
                   "sit down", "jump up and down", "take a walk", 
                   "get tired", "become hungry", "get sick")


```

# Confirmatory Analysis - Prep

## Read data

```{r, warnings = FALSE}
file_paths <- list.files(path = data_path, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## Wrangle data

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>% 
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()

dat <- d %>%
  filter(condition %in% c("causal_chain", "common_cause")) %>% 
    mutate(condition = ifelse(condition == "causal_chain", "Causal Chain",
                            "Intrinsic Cause")) %>%
  mutate(condition = as.factor(condition)) %>% 
  mutate(response = ifelse(response == "similar", "Intrinsic", "Direct")) %>% 
  mutate(subject_id = factor(subject_id)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(middle_causal, selected_choice) ~ "Direct",
    grepl(middle_similar, selected_choice) ~ "Intrinsic",
    TRUE ~ "other"
  )) %>% 
  mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))) %>% 
  select(subject_id, condition, first_item, middle_causal, 
         middle_similar, third_item, response) %>% 
  mutate(domain_first_item = case_when(first_item == "hear something" ~ "mind", 
                                 first_item == "choose what to do" ~ "mind",
                                 first_item == "remember something" ~ "mind",
                                 first_item == "think about something" ~ "mind",
                                 first_item == "see something" ~ "mind",
                                 first_item == "reach for something" ~ "action",
                                 first_item == "sit down" ~ "action", 
                                 first_item == "jump up and down" ~ "action",
                                 first_item == "kick something" ~ "action",
                                 first_item == "take a walk" ~ "action",
                                 first_item == "get tired" ~ "bio", 
                                 first_item == "become hungry" ~ "bio",
                                 first_item == "feel scared"~ "bio",
                                 first_item == "experience pain"~ "bio",
                                 first_item == "get sick"~ "bio"),
         domain_third_item = case_when(third_item == "hear something" ~ "mind", 
                                 third_item == "choose what to do" ~ "mind",
                                 third_item == "remember something" ~ "mind",
                                 third_item == "think about something" ~ "mind",
                                 third_item == "see something" ~ "mind",
                                 third_item == "reach for something" ~ "action",
                                 third_item == "sit down" ~ "action", 
                                 third_item == "jump up and down" ~ "action",
                                 third_item == "kick something" ~ "action",
                                 third_item == "take a walk" ~ "action",
                                 third_item == "get tired" ~ "bio", 
                                 third_item == "become hungry" ~ "bio",
                                 third_item == "feel scared"~ "bio",
                                 third_item == "experience pain"~ "bio",
                                 third_item == "get sick"~ "bio"),
         domain_middle_causal = case_when(middle_causal == "hear something" ~ "mind", 
                                 middle_causal == "choose what to do" ~ "mind",
                                 middle_causal == "remember something" ~ "mind",
                                 middle_causal == "think about something" ~ "mind",
                                 middle_causal == "see something" ~ "mind",
                                 middle_causal == "reach for something" ~ "action",
                                 middle_causal == "sit down" ~ "action", 
                                 middle_causal == "jump up and down" ~ "action",
                                 middle_causal == "kick something" ~ "action",
                                 middle_causal == "take a walk" ~ "action",
                                 middle_causal == "get tired" ~ "bio", 
                                 middle_causal == "become hungry" ~ "bio",
                                 middle_causal == "feel scared"~ "bio",
                                 middle_causal == "experience pain"~ "bio",
                                 middle_causal == "get sick" ~ "bio"),
          domain_middle_similar = case_when(middle_similar == "hear something" ~ "mind", 
                                 middle_similar == "choose what to do" ~ "mind",
                                 middle_similar == "remember something" ~ "mind",
                                 middle_similar == "think about something" ~ "mind",
                                 middle_similar == "see something" ~ "mind",
                                 middle_similar == "reach for something" ~ "action",
                                 middle_similar == "sit down" ~ "action", 
                                 middle_similar == "jump up and down" ~ "action",
                                 middle_similar == "kick something" ~ "action",
                                 middle_similar == "take a walk" ~ "action",
                                 middle_similar == "get tired" ~ "bio", 
                                 middle_similar == "become hungry" ~ "bio",
                                 middle_similar == "feel scared"~ "bio",
                                 middle_similar == "experience pain"~ "bio",
                                 middle_similar == "get sick"~ "bio")) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response)) 

rmarkdown::paged_table(dat)

```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 
cat("\n") 

paste0("pre-exclusion N: ", d %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
cat("\n") 

paste0(
  "Post-exclusion condition count: ",
  dat %>% 
    distinct(subject_id, .keep_all = TRUE) %>% 
    count(condition) %>% 
    mutate(label = paste0(condition, " = ", n)) %>% 
    pull(label) %>% 
    paste(collapse = ", ")
)
cat("\n") 

paste0("Age summary: ")
summary(df_demographics$age)
cat("\n") 

c("Gender: " =  "Count", table(df_demographics$gender))
cat("\n")
c("Ethnicity: " =  "Count", table(df_demographics$ethnicity))
cat("\n")
c("Race: " =  "Count", table(df_demographics$race))

```

## Summarize data 

```{r}
# Condition-level, with cis
dat_summarized_conditions <- dat %>%
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = count / total, 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
            .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  select(-c(count, total))

rmarkdown::paged_table(dat_summarized_conditions)

# Trial-level summary
dat_summarized_trials <- dat %>% #not using but good for proofing
  unite("joined", c(first_item, middle_causal, 
                    middle_similar, third_item), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = count / total, 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
            .groups = "drop") %>% 
  complete(condition, joined, response,
           fill = list(count = 0, mean_proportion = 0, se = 0)) %>%
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) 

rmarkdown::paged_table(dat_summarized_trials)

```

# Confirmatory Analysis - Figures

## Figure with slope

```{r, fig.width = 3, fig.height = 5}
fig_slope <- dat_summarized_conditions %>%
  mutate(response = fct_relevel(response, "Direct", "Intrinsic")) %>% 
  mutate(condition = fct_relevel(condition, "Intrinsic Cause", "Causal Chain")) %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  geom_errorbar(data = filter(dat_summarized_conditions, response == "Intrinsic"), 
                  aes(ymax = ci_high,
                      ymin = ci_low,
                      width = 0.3)) +
  geom_point(
    data = dplyr::filter(dat_summarized_trials, response == "Intrinsic"),
    aes(group = joined),
    alpha = 0.4, color = "black", size = 5
  ) +
  geom_line(
    data = dplyr::filter(dat_summarized_trials, response == "Intrinsic"),
    aes(group = joined),
    alpha = 0.4, color = "black"
  ) +
  #   geom_text(
  #   data = dplyr::filter(dat_summarized_trials, response == "Intrinsic"),
  #   aes(label = joined),
  #   size = 2,
  #   vjust = -0.5
  # ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_x_discrete(labels = c("Causal Chain" = "Causal\nChain", 
                              "Intrinsic Cause" = "Intrinsic\nCause")) +
  theme_cowplot() +
  labs(y = "Proportion (Direct)", 
       x = "Condition", 
       fill = "Response") +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    legend.text = element_text(size = 25),
    panel.background = element_rect(fill='transparent', color=NA),
    plot.background = element_rect(fill='transparent', color=NA))

fig_slope

fig_slope <- ggsave("figures/causal_chain_slope.png", width = 3.5, height = 6, plot = fig_slope, bg = "white")

```

## Item-level with distances

```{r, fig.height = 12, fig.width = 12}
preceding_distances_path <- distances_path

d_preceding_distances <- read_csv(preceding_distances_path) %>%
  mutate(mean_causal_distance = round(mean_causal_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2))

dat_summarized_itemlevel <- dat %>%
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  group_by(condition, first_third) %>%
  mutate(total = n()) %>% 
  group_by(condition, first_third, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

dat_labels <- dat %>% 
  rename("middle_direct" = middle_causal,
         "middle_intrinsic" = middle_similar) %>% 
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  distinct(first_third, middle_direct, middle_intrinsic) %>% 
  separate(first_third, c("first_item", "third_item"),
           sep = "_", remove = FALSE) %>%
  left_join(d_preceding_distances %>% #join causal distances
              rename("third_item" = itemB,
                     "middle_direct" = itemA,
                     "causal_distance_causal_third" = mean_causal_distance,
                     "freesort_distance_causal_third" = mean_freesort_distance,
                     "freesort_minus_causal_causal_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_direct,
                     causal_distance_causal_third,
                     freesort_distance_causal_third,
                     freesort_minus_causal_causal_third), 
            by = c("third_item", "middle_direct")) %>% 
  left_join(d_preceding_distances %>% #join similar distances
              rename("third_item" = itemB,
                     "middle_intrinsic" = itemA,
                     "causal_distance_similar_third" = mean_causal_distance,
                     "freesort_distance_similar_third" = mean_freesort_distance,
                     "freesort_minus_causal_similar_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_intrinsic,
                     causal_distance_similar_third,
                     freesort_distance_similar_third,
                     freesort_minus_causal_similar_third), 
            by = c("third_item", "middle_intrinsic")) %>% 
  
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_direct" = itemB,
                     "causal_distance_causal_first" = mean_causal_distance,
                     "freesort_distance_causal_first" = mean_freesort_distance,
                     "freesort_minus_causal_causal_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_direct,
                     causal_distance_causal_first,
                     freesort_distance_causal_first,
                     freesort_minus_causal_causal_first), 
            by = c("first_item", "middle_direct")) %>% 
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_intrinsic" = itemB,
                     "causal_distance_similar_first" = mean_causal_distance,
                     "freesort_distance_similar_first" = mean_freesort_distance,
                     "freesort_minus_causal_similar_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_intrinsic,
                     causal_distance_similar_first,
                     freesort_distance_similar_first,
                     freesort_minus_causal_similar_first), 
            by = c("first_item", "middle_intrinsic")) %>% 

  mutate(facet_label = paste0("first item: ", first_item,
                              "\n",
                              "third item: ", third_item,
                              "\n",
                              "causal: ", middle_direct, 
                              "\n",  
                              "similar: ", middle_intrinsic,
                              "\n",
                              "\n",
                              "1st item-cdS,fdS,cdC,fdC: ", "(", 
                              causal_distance_similar_first, ",",
                              freesort_distance_similar_first, ",",
                              causal_distance_causal_first, ",",
                              freesort_distance_causal_first, ")", "\n", 
                              "3rd item-cdS, fdS, cdC, fdC: ", "(", 
                              causal_distance_similar_third, ",",
                              freesort_distance_similar_third, ",",
                              causal_distance_causal_third, ",",
                              freesort_distance_causal_third, ")"
                              )) 

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  mutate(first_item = factor(first_item, levels = desired_order)) %>% 
  arrange(first_item) %>% 
  pull(facet_label)

#join labels + order AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(first_third, facet_label), by = "first_third") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))) %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "white")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "Direct"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(size = 25, hjust = 0.5),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion (Direct)",
       title = "Causal Chain") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

ggsave(
  filename = paste0(study_path, "/figures/p_causal_chain_item-level-distances.pdf"),
  plot = p_itemlvl,
  device = "pdf",
  width = 22,
  bg = "white",
  height = 15,
  units = "in")

```

# Confirmatory Analysis - Analysis

## Logistic regression

```{r}
##factor outcome variables
d_model <- dat %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>% 
  mutate(condition = factor(condition, levels = c("Causal Chain", "Intrinsic Cause")))

##run the model
model_chain_vs_common <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_chain_vs_common)

std_parameters <- standardize_parameters(model_chain_vs_common, 
                                         ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_chain_vs_common)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Causal Chain only

```{r}
d_chain <- d_model %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "Causal Chain") 

model_effect_of_chain <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_chain)

summary(model_effect_of_chain)

paste0("probability: ", plogis(fixef(model_effect_of_chain)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_chain)[1]))

```

## Biological Reasoning only

```{r}
d_biological <- d_model %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "Intrinsic Cause") 

model_effect_of_biological <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_biological)
summary(model_effect_of_biological)

paste0("probability: ", plogis(fixef(model_effect_of_biological)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_biological)[1]))

```

# Distances - Prep

## Append distances

```{r}
distances <- read_csv("distances_causal_chain.csv") %>%
  select(-1) %>% 
  rename("middle_item" = middle_causal) 

```

## Merge and save distances

```{r}
d_cc_distances <- dat %>% 
  left_join(distances %>% 
              rename("middle_causal" = middle_item,
                     "rank_causal" = rank),
              by = c("first_item", "third_item", "middle_causal")) %>% 
  left_join(distances %>% 
              rename("middle_similar" = middle_item,
                    "freesort_minus_causal_distance_similar" = freesort_minus_causal_distance_causal,
                    "rank_similar" = rank), 
              by = c("first_item", "third_item", "middle_similar")) %>% 
  mutate(freesort_minus_causal_distance_causal = 
           round(freesort_minus_causal_distance_causal, 2),
         freesort_minus_causal_distance_similar = 
           round(freesort_minus_causal_distance_similar, 2) 
         ) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) 

rmarkdown::paged_table(d_cc_distances)

write_csv(d_cc_distances, "dat_causal_chain_distances.csv")

```

## Read back in distances

```{r}
analysis_path <- here("code", "main", "analysis")

d_cc_distances <- read_csv(paste0(analysis_path,
                "/causal-chain/dat_causal_chain_distances.csv"))

```

# Distances - Figures

## Causal Chain condition

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

#first summarize
d_cc_distances_summarized <- d_cc_distances %>% #rename all these to summarized
  unite("joined", c(first_item, middle_causal, middle_similar, third_item), sep = "_") %>%
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response, freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>% 
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_cc_distances_summarized_causal_chain <- d_cc_distances_summarized %>% 
  filter(condition == "Causal Chain") %>% 
  filter(response == "Direct")  %>% 
  separate(joined, into = c("first_item", "middle_causal", "middle_similar", "third_item"),
         sep = "_") %>%
  mutate(joined = paste0("first: ", first_item, "\n", "direct: ", middle_causal, "\n", "essential: ", middle_similar, "third: ", third_item, "\n"))  %>% 
  mutate(
    first_item         = recode(first_item, !!!short_names),
    third_item         = recode(third_item, !!!short_names),
    middle_causal   = recode(middle_causal, !!!short_names),
    middle_similar  = recode(middle_similar, !!!short_names)) %>%
  mutate(labels = paste0("first: ", first_item, "\n", "direct: ", middle_causal, "\n", "essential: ",
                         middle_similar, "\n", "third: ", third_item))

fig_cc_distances <- d_cc_distances_summarized_causal_chain %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  # geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Causal Chain Condition",
       x = "Joint distance difference",
       y = "Proportion (direct)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1.1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        # plot.title = element_blank(),
        legend.position = "none") 

fig_cc_distances 

fig_cc_distances <- ggsave("figures/causal_chain_distances_wide.png", width = 6, height = 4, 
                        plot = fig_cc_distances, bg = "white")

```

## Biological Reasoning condition

```{r}
d_cc_distances_summarized_intrinsic_cause <- d_cc_distances_summarized %>% 
  filter(condition == "Intrinsic Cause") %>% 
  filter(response == "Direct")  %>% 
  separate(joined, into = c("first_item", "middle_causal", "middle_similar", "third_item"),
         sep = "_") %>%
  mutate(joined = paste0("first: ", first_item, "\n", "direct: ", middle_causal, "\n", "essential: ", middle_similar, "third: ", third_item, "\n"))  %>% 
  mutate(
    first_item         = recode(first_item, !!!short_names),
    third_item         = recode(third_item, !!!short_names),
    middle_causal   = recode(middle_causal, !!!short_names),
    middle_similar  = recode(middle_similar, !!!short_names)) %>%
  mutate(labels = paste0("first: ", first_item, "\n", "direct: ", middle_causal, "\n", "essential: ",
                         middle_similar, "\n", "third: ", third_item))

fig_ic_distances <- d_cc_distances_summarized_intrinsic_cause %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  # geom_text(aes(label = labels), size = 3, vjust = -.2) +
  theme_bw() +
  labs(
      title = "Biological Reasoning Condition",
       x = "Joint distance difference",
       y = "Proportion (direct)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1.1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        # plot.title = element_blank(),
        legend.position = "none") 

fig_ic_distances

fig_ic_distances <- ggsave("figures/intrinsic_cause_distances_wide.png", width = 6, height = 4, 
                        plot = fig_ic_distances, bg = "white")

```

# Distances - Analysis

## Prepare for modelling

```{r}
d_cc_distances_model <- d_cc_distances %>%
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal -
           freesort_minus_causal_distance_similar) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))) %>% 
  mutate(condition = factor(condition, levels = c("Causal Chain", "Intrinsic Cause"))) 
```

## Causal Chain

```{r}
model_cc_distances <- glmer(response ~ joint_distance_difference + 
                              (1 | subject_id), 
    data = d_cc_distances_model %>% 
      filter(condition == "Causal Chain") %>% 
      mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))),
    family = binomial(link = 'logit'))

summary(model_cc_distances)

std_parameters <- standardize_parameters(model_cc_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Biological Reasoning

```{r}
model_ic_distances <- glmer(response ~ joint_distance_difference + 
                              (1 | subject_id), 
    data = d_cc_distances_model %>% 
      filter(condition == "Intrinsic Cause") %>% 
      mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))),
    family = binomial(link = 'logit'))

summary(model_ic_distances)

std_parameters <- standardize_parameters(model_ic_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

# THE END

```{r}

```




