---
title: "Prediction"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-19"
author: ""
---

# ReadMe

- This is the analysis script for the Prediction vs Inductive Inference study.  
- Date run: 11/7/25
- N = 105 before exclusions
- 2 between-subjects conditions: Prediction task vs Inductive Inference task.
- DV: If x happens, what will happen next? (Prediction), if creature can do x, what else can it do? (Inductive inference), IV: Binary choice between direct vs intrinsic event (Prediction), Binary choice between direct vs intrinsic item (Inference).  
- Hypothesis: subjects choose direct item for predicting next event, and intrinsic item for inferring what other capacity a creature will have.

# Setup

## Load packages

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               gt,
               webshot2,
               knitr,
               performance,
               effectsize,
               simr,
               conflicted,
               tidyverse)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code", "main")
freesort_and_causal_distances_df_path <- paste0(base_path,
                                                "/analysis/measure-main-and-pilot/snapshots_study1_main_analysis/freesort_minus_causals.csv")

freesort_and_causal_distances_constrained_df_path <- paste0(base_path,
                                                "/analysis/measure-main-and-pilot/snapshots_study1_main_analysis/short_list_domain_constraints.csv")

```

# Confirmatory Analysis - Prep

The main confirmatory analysis asks what proportion of subjects select the direct vs intrinsic item in each condition. 

## Read data

```{r}
data_path_pr <- paste0(base_path, "/data/prediction/JO-mbc-main-v2-prediction-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_pr, pattern = "^2025-", full.names = TRUE)

d_pr <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

rmarkdown::paged_table(d_pr)

```

## Wrangle data

```{r}
subjects_to_exclude <- d_pr %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>%
  filter(attn_correct == FALSE) %>% 
  pull(subject_id) %>% 
  unique()

dat_pr <- d_pr %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% 
  filter(condition %in% c("event_prediction", "trait_inference")) %>%
  mutate(response = ifelse(response == "causal", "Direct", "Intrinsic")) %>% 
  mutate(response = as.factor(response)) %>% 
  mutate(condition = ifelse(condition == "event_prediction", "Prediction", "Inference")) %>% 
  mutate(condition = as.factor(condition)) %>% 
  mutate(condition = fct_relevel(condition, c("Prediction", "Inference"))) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "Direct",
    grepl(similar_itemA, selected_choice) ~ "Intrinsic",
    TRUE ~ "other"
  )) %>% 
  ungroup() %>% 
  mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))) %>% 
  select(subject_id, condition, itemB, causal_itemA, similar_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", #labels for first item of pair
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "bio", 
                                 itemB == "become hungry" ~ "bio",
                                 itemB == "feel scared"~ "bio",
                                 itemB == "experience pain"~ "bio",
                                 itemB == "get sick"~ "bio"),
         domain_causalitemA = case_when(causal_itemA == "hear something" ~ "mind", 
                                 causal_itemA == "choose what to do" ~ "mind",
                                 causal_itemA == "remember something" ~ "mind",
                                 causal_itemA == "think about something" ~ "mind",
                                 causal_itemA == "see something" ~ "mind",
                                 causal_itemA == "reach for something" ~ "action",
                                 causal_itemA == "sit down" ~ "action", 
                                 causal_itemA == "jump up and down" ~ "action",
                                 causal_itemA == "kick something" ~ "action",
                                 causal_itemA == "take a walk" ~ "action",
                                 causal_itemA == "get tired" ~ "bio", 
                                 causal_itemA == "become hungry" ~ "bio",
                                 causal_itemA == "feel scared"~ "bio",
                                 causal_itemA == "experience pain"~ "bio",
                                 causal_itemA == "get sick"~ "bio"),
          domain_similaritemA = case_when(similar_itemA == "hear something" ~ "mind", 
                                 similar_itemA == "choose what to do" ~ "mind",
                                 similar_itemA == "remember something" ~ "mind",
                                 similar_itemA == "think about something" ~ "mind",
                                 similar_itemA == "see something" ~ "mind",
                                 similar_itemA == "reach for something" ~ "action",
                                 similar_itemA == "sit down" ~ "action", 
                                 similar_itemA == "jump up and down" ~ "action",
                                 similar_itemA == "kick something" ~ "action",
                                 similar_itemA == "take a walk" ~ "action",
                                 similar_itemA == "get tired" ~ "bio", 
                                 similar_itemA == "become hungry" ~ "bio",
                                 similar_itemA == "feel scared"~ "bio",
                                 similar_itemA == "experience pain"~ "bio",
                                 similar_itemA == "get sick"~ "bio")) 

rmarkdown::paged_table(dat_pr)
```

## Demographics

```{r}
# demographics
df_demographics <- d_pr %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

paste0("pre-exclusion N: ", d_pr %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat_pr %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
summary(df_demographics$filename)
summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Summarize data

```{r}
# Trial-level summary
dat_trial_summarized <- dat_pr %>%
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    .groups = "drop"
  ) %>% 
  tidyr::complete(condition, joined, response, fill = list(count = 0)) %>% 
  group_by(condition, joined) %>%
  fill(total, .direction = "downup") %>%
  mutate(
    mean_proportion = count / total,
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),
    ci_low = pmax(0, mean_proportion - 1.96 * se),
    ci_high = pmin(1, mean_proportion + 1.96 * se)
  ) %>%
  ungroup() 

rmarkdown::paged_table(dat_trial_summarized %>% 
                         separate(joined, 
                                  into = c("itemB", "causal_itemA", "similar_itemA"), 
                                  sep = "_"))

# Condition-level summary
dat_condition_summarized <- dat_pr %>%
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    .groups = "drop"
  ) %>% 
  tidyr::complete(
    condition,
    response = c("Intrinsic", "Direct"),
    fill = list(count = 0)
  ) %>%
  group_by(condition) %>%
  fill(total, .direction = "downup") %>%
  mutate(
    mean_proportion = count / total,
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),
    ci_low = pmax(0, mean_proportion - 1.96 * se),
    ci_high = pmin(1, mean_proportion + 1.96 * se)
  ) %>%
  ungroup()

rmarkdown::paged_table(dat_condition_summarized)

```

## Specific relations reported in paper

### Jumping -> tired vs walk

```{r}
#jumping is much more likely to make someone get tired than to make them take a walk
dat_jump <- dat_pr %>% 
  filter(condition == "Prediction",
         itemB == "jump up and down",
         causal_itemA == "get tired",
         similar_itemA == "take a walk") %>% 
  mutate(direct_binary = ifelse(response == "Direct", 1, 0))

#mean proportion choosing tired
model_jump_prop <- glm(direct_binary ~ 1,
                  family = binomial,
                  data = dat_jump)

summary(model_jump_prop)
plogis(coef(model_jump_prop[1]))
plogis(confint(model_jump_prop))

#CIs for beta
model_jump <- glmer(
  response ~ 1 + (1 | subject_id),
  data = dat_jump,
  family = binomial)

summary(model_jump)
standardize_parameters(model_jump)

```

### Hearing -> see vs scared

```{r}
#hearing is just as likely to make someone see something as to make them feel scared
dat_hear <- dat_pr %>% 
  filter(condition == "Prediction",
         itemB == "hear something",
         causal_itemA == "feel scared",
         similar_itemA == "see something") %>% 
  mutate(direct_binary = ifelse(response == "Direct", 1, 0))

#mean proportion choosing scared0
model_hear_prop <- glm(direct_binary ~ 1,
                  family = binomial,
                  data = dat_hear)

summary(model_hear_prop)
plogis(coef(model_hear_prop[1]))
plogis(confint(model_hear_prop))

#CIs for beta
model_hear <- glmer(
  response ~ 1 + (1 | subject_id),
  data = dat_hear,
  family = binomial)

summary(model_hear)

confint(model_hear)
standardize_parameters(model_hear)

```


# Confirmatory Analysis - Figures

## Figure with slope

```{r}
fig_slope <- dat_condition_summarized %>%
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>%
  mutate(condition = fct_relevel(condition, c("Inference", "Prediction"))) %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  geom_errorbar(data = filter(dat_condition_summarized, response == "Intrinsic"), 
              aes(ymax = ci_high,
                  ymin = ci_low,
                  width = 0.3)) +
  #   geom_text(
  #   data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
  #   aes(label = joined),
  #   size = 2,
  #   vjust = -0.5
  # ) +
  geom_point(
    data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
    aes(group = joined),
    alpha = 0.4, color = "black", size = 5) +
  geom_line(
    data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
    aes(group = joined),
    alpha = 0.4, color = "black"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_cowplot() +
  labs(y = "Proportion", x = "Condition", fill = "Response") +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    #aspect.ratio = 1.5,
    legend.text = element_text(size = 25)
  )

fig_slope

fig_slope <- ggsave("figures/prediction_slope.png", width = 3.5, height = 6, plot = fig_slope, bg = "white")

```

## Figure with slope - black and white

```{r}
fig_slope <- dat_condition_summarized %>%
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>%
  mutate(condition = fct_relevel(condition, c("Inference", "Prediction"))) %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  scale_fill_manual(values = c("#CCCCCC", "white")) +
  geom_errorbar(data = filter(dat_condition_summarized, response == "Intrinsic"), 
              aes(ymax = ci_high,
                  ymin = ci_low,
                  width = 0.3)) +
  #   geom_text(
  #   data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
  #   aes(label = joined),
  #   size = 2,
  #   vjust = -0.5
  # ) +
  # geom_point(
  #   data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
  #   aes(group = joined),
  #   alpha = 0.4, color = "black", size = 5) +
  
  geom_point(
      data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
    aes(group = joined,
        fill = response),
             alpha = 0.8, 
             size = 5,
             shape = 21,
             color = "black") +
  scale_fill_manual(values = c(
          "Direct" = "#CCCCCC",
          "Intrinsic" = "white")) +
  
  geom_line(
    data = dplyr::filter(dat_trial_summarized, response == "Intrinsic"),
    aes(group = joined),
    alpha = 0.4, color = "black"
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_cowplot() +
  labs(y = "Proportion", x = "Condition", fill = "Response") +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    #aspect.ratio = 1.5,
    legend.text = element_text(size = 25)
  )

fig_slope

fig_slope <- ggsave("figures/prediction_slope-black-and-white.png", width = 3.5, height = 6, plot = fig_slope, bg = "white")

```

## Item-level with distances

```{r, fig.height = 12, fig.width = 12}
#appending distances
d_distances <- read_csv(freesort_and_causal_distances_constrained_df_path)

rmarkdown::paged_table(d_distances)

### Then Plotting
dat_summarized_itemlevel <- dat_pr %>%
  group_by(condition, itemB) %>%
  mutate(total = n()) %>% 
  group_by(condition, itemB, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

mean_diff <- dat_summarized_itemlevel %>%
  filter(response == "Direct") %>%
  mutate(condition = tolower(condition)) %>%
  select(itemB, condition, mean_proportion) %>%
  tidyr::pivot_wider(names_from = condition, values_from = mean_proportion) %>%
  mutate(meanPred_minus_meanInf = round(prediction - inference, 2)) %>%
  select(itemB, meanPred_minus_meanInf)

dat_labels <- dat_pr %>% 
  left_join(d_distances %>% #join distances
              mutate("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  distinct(itemB, causal_itemA, similar_itemA, 
           causal_distance_causal_choice,
           freesort_distance_causal_choice,
           causal_distance_similar_choice,
           freesort_distance_similar_choice,
           freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         cds_minus_cdc = causal_distance_similar_choice - causal_distance_causal_choice,
         fdc_minus_fds = freesort_distance_causal_choice - freesort_distance_similar_choice,
         fdmcdc_minus_fdmcds = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>% 
  left_join(mean_diff, by = "itemB") %>%
  mutate(facet_label = paste0(itemB, 
                              "\n",
                              "causal: ", causal_itemA, 
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice,
                              ",",
                              freesort_distance_causal_choice,
                              ",",
                              freesort_minus_causal_distance_causal,
                              ")",
                              "\n",  
                              "similar: ", similar_itemA, 
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice,
                              ",",
                              freesort_distance_similar_choice,
                              ",",
                              freesort_minus_causal_distance_similar,
                              ")",
                              "\n",
                              "cdS - cdC: ",
                              cds_minus_cdc,
                              "\n",
                              "fdC - fdS: ",
                              fdc_minus_fds,
                              "\n",
                              "(f-cC) - (f-cS): ",
                              fdmcdc_minus_fdmcds,
                              "\n",
                              "meanPred(C) - meanInf(C): ",
                              meanPred_minus_meanInf
                              ))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#join labels + ordering AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("white", "grey80")) + 
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "Direct"), 
                aes(ymax = mean_proportion + se,
                    ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion",
       title = "main") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

# ggsave(
#   filename = "figures/p_prediction_item-level.pdf",
#   plot = p_itemlvl,          
#   device = "pdf",           
#   width = 22,               
#   height = 15,             
#   units = "in")

```

# Confirmatory Analysis - Analysis

## Logistic regression

```{r}
d_model <- dat_pr %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>% 
  mutate(condition = factor(condition, levels = c("Prediction", "Inference")))

model_prediction_vs_inference <- glmer(response ~ condition + 
                                         (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_prediction_vs_inference)

std_parameters <- standardize_parameters(model_prediction_vs_inference, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters
```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_prediction_vs_inference)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Prediction-only model

```{r}
d_model_pr <- dat_pr %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>%
  filter(condition == "Prediction")

model_prediction <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_pr)

summary(model_prediction)
paste0("probability: ", plogis(fixef(model_prediction)[1]))
paste0("odds ratio: ", exp(fixef(model_prediction)[1]))

```

## Inference-only model

```{r}
d_model_inf <- dat_pr %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))) %>%
  filter(condition == "Inference")

model_inference <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model_inf)

summary(model_inference)
paste0("probability: ", plogis(fixef(model_inference)[1]))
paste0("odds ratio: ", exp(fixef(model_inference)[1]))

```

# Distances - Prep

The exploratory distance analysis asks whether we can use the quantitative distances to explain variation in effect sizes across trials.  

## Append distances

```{r}
#appending distances
d_distances <- read_csv(freesort_and_causal_distances_constrained_df_path)

rmarkdown::paged_table(d_distances)
```

## Merge and save distances

```{r}
dat_pr_distances <- dat_pr %>% 
  left_join(d_distances %>% 
              select(causal_choice, similar_choice, target_item, 
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar) %>%
              rename("causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice,
                     "itemB" = target_item),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

rmarkdown::paged_table(dat_pr_distances)

write_csv(dat_pr_distances, "dat_prediction_distances.csv")

```

## Read back in distances

```{r}
analysis_path <- here("code", "main", "analysis")

dat_pr_distances <- read_csv(paste0(analysis_path,
                "/prediction/dat_prediction_distances.csv")) %>% 
  mutate(condition = factor(condition, levels = c("Prediction", "Inference"))) %>% 
  mutate(response = factor(response, levels = c("Direct", "Intrinsic")))

```

# Distances - Figures

## Prediction condition - y axis CC

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

dat_pr_distances_wrangled <- dat_pr_distances %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response, freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>%
  # mutate(joint_distance_difference = freesort_minus_causal_distance_similar - freesort_minus_causal_distance_causal) %>%
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_prop_and_distances_prediction <- dat_pr_distances_wrangled %>% 
  filter(condition == "Prediction") %>% 
  filter(response == "Direct")  %>% 
  separate(joined, into = c("itemB", "causal_itemA", "similar_itemA"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ", similar_itemA))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    causal_itemA   = recode(causal_itemA, !!!short_names),
    similar_itemA  = recode(similar_itemA, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ",
                         similar_itemA))  

#figure
fig_pred_distance <- d_prop_and_distances_prediction %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = .4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  #geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Prediction Condition",
       x = "Joint distance difference",
       y = "Proportion (Intrinsic)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        legend.position = "none") 

fig_pred_distance

fig_pred_distance <- ggsave("figures/prediction_distances_points-yCC.png", width = 6, height = 4.5,
                        plot = fig_pred_distance, bg = "white")

# fig_pred_distance <- ggsave("figures/prediction_distances_points_reversed_jd.png", width = 6, height = 4,
#                         plot = fig_pred_distance, bg = "white")

```

## Prediction condition - y axis CO

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

dat_pr_distances_wrangled <- dat_pr_distances %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response, freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>%
  # mutate(joint_distance_difference = freesort_minus_causal_distance_similar - freesort_minus_causal_distance_causal) %>%
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_prop_and_distances_prediction <- dat_pr_distances_wrangled %>% 
  filter(condition == "Prediction") %>% 
  filter(response == "Intrinsic")  %>% 
  separate(joined, into = c("itemB", "causal_itemA", "similar_itemA"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ", similar_itemA))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    causal_itemA   = recode(causal_itemA, !!!short_names),
    similar_itemA  = recode(similar_itemA, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ",
                         similar_itemA))  

#figure
fig_pred_distance <- d_prop_and_distances_prediction %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = .4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  #geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Prediction Condition",
       x = "Joint distance difference",
       y = "Proportion (Intrinsic)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        legend.position = "none") 

fig_pred_distance

fig_pred_distance <- ggsave("figures/prediction_distances_points-yCO.png", width = 6, height = 4,
                        plot = fig_pred_distance, bg = "white")

# fig_pred_distance <- ggsave("figures/prediction_distances_points_reversed_jd.png", width = 6, height = 4,
#                         plot = fig_pred_distance, bg = "white")

```

## Inference condition - y axis CC

```{r}
dat_pr_distances_wrangled <- dat_pr_distances %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  # group_by(condition, joined, response) %>%
  group_by(condition, joined, response, freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>%
   # mutate(joint_distance_difference = freesort_minus_causal_distance_similar - freesort_minus_causal_distance_causal) %>%
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_prop_and_distances_inference <- dat_pr_distances_wrangled %>% 
  filter(condition == "Inference") %>% 
  filter(response == "Direct")  %>% 
  separate(joined, into = c("itemB", "causal_itemA", "similar_itemA"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ", similar_itemA))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    causal_itemA   = recode(causal_itemA, !!!short_names),
    similar_itemA  = recode(similar_itemA, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ",
                         similar_itemA))  

fig_inf_distance <- d_prop_and_distances_inference %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = .4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  #geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Inference Condition",
       x = "Joint distance difference",
       y = "Proportion (Direct)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        legend.position = "none") 

fig_inf_distance

fig_inf_distance <- ggsave("figures/inference_distances_points-yCC.png", width = 6, height = 4.5,
                        plot = fig_inf_distance, bg = "white")

# fig_inf_distance <- ggsave("figures/inference_distances_points_reverse_jd.png", width = 6, height = 4,
#                         plot = fig_inf_distance, bg = "white")

```

## Inference condition - y axis CO

```{r}
dat_pr_distances_wrangled <- dat_pr_distances %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  # group_by(condition, joined, response) %>%
  group_by(condition, joined, response, freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>%
   # mutate(joint_distance_difference = freesort_minus_causal_distance_similar - freesort_minus_causal_distance_causal) %>%
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_prop_and_distances_inference <- dat_pr_distances_wrangled %>% 
  filter(condition == "Inference") %>% 
  filter(response == "Intrinsic")  %>% 
  separate(joined, into = c("itemB", "causal_itemA", "similar_itemA"),
         sep = "_") %>%
  mutate(joined = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ", similar_itemA))  %>% 
  mutate(
    itemB         = recode(itemB, !!!short_names),
    causal_itemA   = recode(causal_itemA, !!!short_names),
    similar_itemA  = recode(similar_itemA, !!!short_names)) %>% 
  mutate(labels = paste0("target: ", itemB, "\n", "direct: ", causal_itemA, "\n", "intrinsic: ",
                         similar_itemA))  

fig_inf_distance <- d_prop_and_distances_inference %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = .4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  #geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Inference Condition",
       x = "Joint distance difference",
       y = "Proportion (Intrinsic)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        legend.position = "none") 

fig_inf_distance

fig_inf_distance <- ggsave("figures/inference_distances_points-yCO.png", width = 6, height = 4,
                        plot = fig_inf_distance, bg = "white")

# fig_inf_distance <- ggsave("figures/inference_distances_points_reverse_jd.png", width = 6, height = 4,
#                         plot = fig_inf_distance, bg = "white")

```

# Distances - Analysis

## Prepare for modelling

```{r}
dat_pr_distances_model <- dat_pr_distances %>% 
  mutate(joint_distance_difference = freesort_minus_causal_distance_causal -
           freesort_minus_causal_distance_similar) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("Intrinsic", "Direct")))

```

## Prediction condition

```{r}
model_prediction_distances <- glmer(response ~ joint_distance_difference + (1 | subject_id), 
    data = dat_pr_distances_model %>% 
      filter(condition == "Prediction") %>% 
      mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))),
    family = binomial(link = 'logit'))

summary(model_prediction_distances)

std_parameters <- standardize_parameters(model_prediction_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Inference condition

```{r}
model_inference_distances <- glmer(response ~ joint_distance_difference + (1 | subject_id), 
    data = dat_pr_distances_model %>% filter(condition == "Inference") %>% 
            mutate(response = fct_relevel(response, c("Direct", "Intrinsic"))),
    family = binomial(link = 'logit'))

summary(model_inference_distances)

std_parameters <- standardize_parameters(model_inference_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters
```

## Inference condition, flipped coef

```{r}
model_inference_distances <- glmer(response ~ joint_distance_difference + (1 | subject_id), 
    data = dat_pr_distances_model %>% filter(condition == "Inference") %>% 
            mutate(response = fct_relevel(response, c("Intrinsic", "Direct"))),
    family = binomial(link = 'logit'))

summary(model_inference_distances)

std_parameters <- standardize_parameters(model_inference_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters
```

# THE END

```{r}

```
