---
title: "study 6"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-11"
author: ""

---

# ReadMe

This is the analysis for the ordinary vs magical intervention study of the MBC project. 

# Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects,  
               gt,
               webshot2,
               knitr,
               performance,
               tidyverse,
               simr,
               conflicted)
sessionInfo()

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)

```

# Global variables

```{r}
base_path <- here("code", "main")

snapshots_input_path_main <- paste0(base_path,
                                    "/analysis/study1-measure-main-and-pilot/snapshots_study1_main_analysis")
preceding_distances_path <- paste0(snapshots_input_path_main,
                                                "/preceding_short_list_domain_constraints.csv")
following_distances_path <- paste0(snapshots_input_path_main,
                                                "/following_short_list_domain_constraints.csv")

```

# Prepare data

## read data

```{r, warnings = FALSE}
data_path_cf <- paste0(base_path, "/data/intervention/JO-mbc-main-study3-v2_intervention-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_cf, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## wrangle data

initial: 30 trials per subject * 48 subjects = 1440 rows.
dat: (30 trials / 2 trials per row) * 48 subjects = 720 rows.

(after filtering to only relevant trials)
initial: 15 trials per subject * 2 subjects = 30 rows

TODO: rename itemB to target item.

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_choice) %>%
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()

dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% #exclude 1 subject who failed attn check
  filter(condition %in% c("ordinary", "magical")) %>%
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "causal",
    grepl(similar_itemA, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  ungroup() %>% 
  select(subject_id, condition, itemB, causal_itemA, similar_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", #labels for first item of pair
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "bio", 
                                 itemB == "become hungry" ~ "bio",
                                 itemB == "feel scared"~ "bio",
                                 itemB == "experience pain"~ "bio",
                                 itemB == "get sick"~ "bio"),
         domain_causalitemA = case_when(causal_itemA == "hear something" ~ "mind", 
                                 causal_itemA == "choose what to do" ~ "mind",
                                 causal_itemA == "remember something" ~ "mind",
                                 causal_itemA == "think about something" ~ "mind",
                                 causal_itemA == "see something" ~ "mind",
                                 causal_itemA == "reach for something" ~ "action",
                                 causal_itemA == "sit down" ~ "action", 
                                 causal_itemA == "jump up and down" ~ "action",
                                 causal_itemA == "kick something" ~ "action",
                                 causal_itemA == "take a walk" ~ "action",
                                 causal_itemA == "get tired" ~ "bio", 
                                 causal_itemA == "become hungry" ~ "bio",
                                 causal_itemA == "feel scared"~ "bio",
                                 causal_itemA == "experience pain"~ "bio",
                                 causal_itemA == "get sick"~ "bio"),
          domain_similaritemA = case_when(similar_itemA == "hear something" ~ "mind", 
                                 similar_itemA == "choose what to do" ~ "mind",
                                 similar_itemA == "remember something" ~ "mind",
                                 similar_itemA == "think about something" ~ "mind",
                                 similar_itemA == "see something" ~ "mind",
                                 similar_itemA == "reach for something" ~ "action",
                                 similar_itemA == "sit down" ~ "action", 
                                 similar_itemA == "jump up and down" ~ "action",
                                 similar_itemA == "kick something" ~ "action",
                                 similar_itemA == "take a walk" ~ "action",
                                 similar_itemA == "get tired" ~ "bio", 
                                 similar_itemA == "become hungry" ~ "bio",
                                 similar_itemA == "feel scared"~ "bio",
                                 similar_itemA == "experience pain"~ "bio",
                                 similar_itemA == "get sick"~ "bio")) 

```

## demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

paste0("pre-exclusion N: ", d %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
summary(df_demographics$filename)
summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

cond_labels <- d %>%
  filter(condition %in% c("ordinary", "magical")) %>%
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "causal",
    grepl(similar_itemA, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  distinct(subject_id, itemB, causal_itemA, similar_itemA, response, condition)

```

# Plot 

## Main figure

```{r, fig.width = 6, fig.height = 5}
dat_summarized <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(condition = ifelse(condition == "magical", "Magical", "Ordinary")) %>% 
  mutate(condition = factor(condition, levels = c("Ordinary", "Magical"))) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

main_fig <- dat_summarized %>%
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000"),
                      labels = c("Latent", "Direct")) + #or whatever you'd like!
  # scale_x_discrete(labels = c("Giving Creature Ability" = "granting", 
  #                             "Making Someone do Something" = "causing")) +
    geom_errorbar(data = filter(dat_summarized, response == "causal"), aes(ymax = mean_proportion + se,
                                                                           ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
    theme_cowplot() +
  labs(y = "Proportion",
       x = "Intervention Type",
       fill = "Response") +
  ylim(0, 1) +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),

        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent', color = NA),
        legend.box.background = element_rect(fill='transparent', color = NA),
        
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm")
        ) 

main_fig

# main_fig <- ggsave("figures/intervention.png", width = 5, height = 5, plot = main_fig, bg = "transparent")

main_fig <- ggsave("figures/intervention_white-111125.png", width = 6, height = 5, plot = main_fig, bg = "white")

```


## Figure for spp 2026

```{r, fig.width = 4, fig.height = 5}
spp_26 <- dat_summarized %>%
  mutate(condition = fct_relevel(condition, "Magical")) %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
    geom_bar(stat = "identity", colour = "black") +
    scale_fill_manual(values = c("grey80", "#000000")) + 
    geom_errorbar(data = filter(dat_summarized, response == "causal"), 
                  aes(ymax = mean_proportion + se,
                      ymin = mean_proportion - se),
                  stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  theme_cowplot() +
  labs(y = "Proportion",
       x = "Intervention Type",
       fill = "Response") +
  scale_x_discrete(labels = c("Ordinary" = "Ordinary ", "Magical" = "  Magical")) +
  ylim(0, 1) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 25),
        legend.position = "none",
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)#,
        ) 

spp_26

ggsave(paste0(base_path, "/analysis/study3-intervention/figures/spp_26.pdf"), 
       plot = spp_26,
       # device = svglite::svglite,
       width = 4,
       height = 5,
       units = "in",
       bg = "white")


```

## Item-level plot
Includes distances in plot

```{r, fig.width = 12, fig.height = 12}
d_distances <- read_csv(preceding_distances_path)

dat_summarized_by_item <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  tidyr::complete(response, nesting(condition, itemB, 
                                    causal_itemA, similar_itemA,
                                    domain_causalitemA, domain_similaritemA,
                                    domain_itemB), fill = list(count = 0)) %>% #fill empty responses
  group_by(condition, itemB) %>%
  mutate(total = n()) %>%  #get total responses per condition
  ungroup() %>% 
  group_by(condition, itemB, response) %>%
  mutate(
    count = n(),  #count responses for each response type
    total = first(total),  #total responses for the condition
    mean_proportion = count / total,  #prop response within condition
    se = sqrt(mean_proportion * (1 - mean_proportion) / total)) %>%
  distinct(condition, itemB, .keep_all = TRUE) %>%
  select(-subject_id) %>%
  ungroup()

dat_labels <- dat_summarized_by_item %>% 
  distinct(itemB, causal_itemA, similar_itemA) %>% 
  left_join(d_distances %>% #join distances
              rename("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice) %>% 
              select(itemB, causal_itemA, similar_itemA,
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar), 
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2)) %>% 
  mutate(facet_label = paste0(
    itemB, "\n",
    "", causal_itemA, "\n", 
    "", similar_itemA   
  )) %>% 
  mutate(facet_label = paste0(itemB, "\n",
                              "causal: ", causal_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice, ",",
                              freesort_distance_causal_choice, ",",
                              freesort_minus_causal_distance_causal, ")", "\n",  
                              "similar: ", similar_itemA, "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice, ",",
                              freesort_distance_similar_choice, ",",
                              freesort_minus_causal_distance_similar, ")", "\n"))

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

dat_summarized_by_item_levels <- dat_summarized_by_item %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>% 
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_intervention <-  dat_summarized_by_item_levels %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity") +
  geom_bar(stat = "identity", colour = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_errorbar(data = filter(dat_summarized_by_item_levels, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  scale_fill_manual(values = c("grey80", "#000000")) +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 25),
        strip.text = element_text(size = 15)) +
  labs(y = "proportion",
       title = "Intervention") +
  facet_wrap(~facet_label, nrow = 3)

p_intervention

ggsave(
  filename = "figures/p_intervention_item-level_stacked.pdf",
  plot = p_intervention,          
  device = "pdf",           
  width = 20,               
  height = 15,             
  units = "in")

ggsave(
  filename = "figures/p_intervention_item-level_stacked.png",
  plot = p_intervention,  
  bg = "white",
  width = 20,               
  height = 15,             
  units = "in")

```

# Primary Analysis

## Logistic regression

```{r}
d_model <- dat %>%
  mutate(response = fct_relevel(response, c("causal", "similar"))) %>%
  mutate(subject_id = factor(subject_id))

model_effect_of_intervention <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_effect_of_intervention)

```

## CIs - 2026

```{r}
d_cis <- dat %>%
  mutate(response = fct_relevel(response, c("causal", "similar"))) %>%
  mutate(subject_id = factor(subject_id)) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop") %>% 
  mutate(
    ci_low = pmax(0, mean_proportion - 1.96 * se),
    ci_high = pmin(1, mean_proportion + 1.96 * se)
  ) %>% 
  select(-c(count, total))

d_cis
```


## Get specific probabilities

```{r}
effects_data <- allEffects(model_effect_of_intervention)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Ordinary-only model
```{r}
d_ordinary <- d_model %>% 
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "ordinary") 

model_effect_of_ordinary <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_ordinary)

summary(model_effect_of_ordinary)

plogis(fixef(model_effect_of_ordinary)[1])

```

## Magical-only model

```{r}
d_magical <- d_model %>% 
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "magical") 

model_effect_of_magical <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_magical)
plogis(fixef(model_effect_of_magical)[1])
summary(model_effect_of_magical)
or <- exp(fixef(model_effect_of_magical)[1])
or

```

# Distances Analyses

## Join and save distances

```{r}
distances <- read_csv(preceding_distances_path)

dat_plot_distances_intervention <- dat %>% 
  left_join(distances %>% 
              select(causal_choice, similar_choice, target_item, 
                     causal_distance_causal_choice,
                     freesort_distance_causal_choice,
                     freesort_minus_causal_distance_causal,
                     causal_distance_similar_choice,
                     freesort_distance_similar_choice,
                     freesort_minus_causal_distance_similar) %>%
              rename("causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice,
                     "itemB" = target_item),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

# write_csv(dat_plot_distances_intervention, "dat_intervention_distances.csv")

```


## Read back in data frame

```{r}
analysis_path <- here("code", "main", "analysis")

dat_plot_distances_intervention <- read_csv(paste0(analysis_path,
                "/study3-intervention/dat_intervention_distances.csv"))

#prepare for modelling
dat_model <- dat_plot_distances_intervention %>% 
  mutate(subject_id = as.factor(subject_id),
         response = ifelse(response == "causal", 1, 0)) 

```

## Summarize data 

Not currently using this data frame but summarized just for checking purposes

```{r}
dat_model_summarized <- dat_model %>% 
  # mutate(response = fct_relevel(response, c("similar", "causal"))) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

```


## Ordinary distances - clear way

Uses predict(). This is what I'm going with.

```{r}
model_ordinary <- glmer(response ~ freesort_minus_causal_distance_causal +
                        freesort_minus_causal_distance_similar + 
                        (1 | subject_id), 
    data = dat_model %>% filter(condition == "ordinary"),
    family = binomial(link = 'logit'))

summary(model_ordinary)

dat_ordinary <- dat_model %>%
  distinct(condition, response, itemB, causal_itemA, similar_itemA,
           freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>%
  # mutate(trial_id = paste("T:", itemB, "\n", "C:", 
  #                         causal_itemA, "\n", "S:", similar_itemA)) %>% 
  filter(condition == "ordinary")

dat_ordinary_newdata <- dat_ordinary %>% 
  mutate(p_hat = predict(model_ordinary, 
                         newdata = ., 
                         type = "response", 
                         re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, freesort_minus_causal_distance_causal, 
         freesort_minus_causal_distance_similar, p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
        "similar_item" = freesort_minus_causal_distance_similar)

# View(d_test)

plot_ordinary_distances <- dat_ordinary_newdata %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") %>% 
  ggplot(aes(x = joint_distance, y = p_hat, color = item_type)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Ordinary Intervention",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_ordinary_distances

```

#### Ordinary condition, single x axis

```{r}

dat_ordinary_newdata <- dat_ordinary %>% 
  mutate(p_hat = predict(model_ordinary, 
                         newdata = ., 
                         type = "response", 
                         re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, freesort_minus_causal_distance_causal, 
         freesort_minus_causal_distance_similar, p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
        "similar_item" = freesort_minus_causal_distance_similar) %>% 
  mutate(joint_distance_diff = causal_item - similar_item)

plot_ordinary_distances <- dat_ordinary_newdata %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") %>% 
  ggplot(aes(x = joint_distance_diff, y = p_hat)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Ordinary Intervention",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint causal - Joint similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_ordinary_distances

distances_diff_fig <- ggsave("figures/ordinary_diffs_joint.png", 
                   width = 6, height = 5, plot = plot_ordinary_distances, 
                   bg = "white")

```

## Magical distances - clear way

```{r}
model_magical <- glmer(response ~ freesort_minus_causal_distance_causal +
                        freesort_minus_causal_distance_similar + 
                        (1 | subject_id), 
    data = dat_model %>% filter(condition == "magical"),
    family = binomial(link = 'logit'))

summary(model_magical)

dat_magical_newdata <- dat_model %>%
  distinct(condition, response, itemB, causal_itemA, similar_itemA,
           causal_distance_causal_choice,
           freesort_distance_causal_choice,
           freesort_minus_causal_distance_causal,
           
           causal_distance_similar_choice,
           freesort_distance_similar_choice,
           freesort_minus_causal_distance_similar) %>%
  mutate(trial_id = paste("T:", itemB, "\n", "C:", 
                          causal_itemA, "\n", "S:", similar_itemA)) %>% 
  filter(condition == "magical")

dat_magical_newdata_plot <- dat_magical_newdata %>% 
  mutate(p_hat = predict(model_magical, 
                         newdata = ., 
                         type = "response", re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, 
         freesort_distance_causal_choice,
         causal_distance_causal_choice,
         freesort_minus_causal_distance_causal,
         
         freesort_distance_similar_choice,
         causal_distance_similar_choice,
         freesort_minus_causal_distance_similar, 
         p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
         "similar_item" = freesort_minus_causal_distance_similar,
         "cd_c" = causal_distance_causal_choice,
         "fd_c" = freesort_distance_causal_choice,
         "cd_s" = causal_distance_similar_choice,
         "fd_s" = freesort_distance_similar_choice,
         "target" = itemB) %>% 
  mutate(diff = causal_item + similar_item) 

# View(dat_magical_newdata_plot %>% 
#        arrange(p_hat) %>% 
#        distinct(target, .keep_all = TRUE))

plot_magical_distances <- dat_magical_newdata_plot %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") %>% 
  ggplot(aes(x = joint_distance, y = p_hat, color = item_type)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Magical Intervention",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_magical_distances
#ordinary prediction = borne out in data
#the more the causal item is causal they choose causal item
# the more the causal item is similar they choose the similar item (the opposite item)

#magical prediction
#the more the similar item is similar they choose the similar item
#the more the similar item is causal, they choose the causal item (the opposite item)

```

#### Magical condition, single x axis

```{r}

dat_magical_newdata_plot <- dat_magical_newdata %>% 
  mutate(p_hat = predict(model_magical, 
                         newdata = ., 
                         type = "response", re.form = NA)) %>% 
  mutate(p_hat = round(p_hat, 2)) %>% 
  select(itemB, causal_itemA, similar_itemA, 
         freesort_distance_causal_choice,
         causal_distance_causal_choice,
         freesort_minus_causal_distance_causal,
         
         freesort_distance_similar_choice,
         causal_distance_similar_choice,
         freesort_minus_causal_distance_similar, 
         p_hat) %>% 
  rename("causal_item" = freesort_minus_causal_distance_causal,
         "similar_item" = freesort_minus_causal_distance_similar,
         "cd_c" = causal_distance_causal_choice,
         "fd_c" = freesort_distance_causal_choice,
         "cd_s" = causal_distance_similar_choice,
         "fd_s" = freesort_distance_similar_choice,
         "target" = itemB) %>% 
  mutate(diff = causal_item + similar_item) %>% 
  mutate(joint_distance_diff = causal_item - similar_item)

plot_magical_distances <- dat_magical_newdata_plot %>% 
  pivot_longer(c(causal_item, similar_item),
               names_to = "item_type",
               values_to = "joint_distance") %>% 
  ggplot(aes(x = joint_distance_diff, y = p_hat)) +
  geom_point() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(method = "lm") +
  theme_bw() +
  labs(
    title = "Magical Intervention",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint causal - Joint similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

plot_magical_distances

distances_diff_fig <- ggsave("figures/magical_diffs_joint.png", 
                   width = 6, height = 5, plot = plot_magical_distances, 
                   bg = "white")

```


## Figure for troubleshooting Magical condition

```{r, fig.height = 6}
#
dat_lab <- dat_magical_newdata_plot %>% 
  pivot_longer(
    c(causal_item, similar_item),
    names_to = "item_type",
    values_to = "joint_distance"
  ) %>% 
  mutate(
    label = case_when(
      item_type == "causal_item"  ~ causal_itemA,
      item_type == "similar_item" ~ similar_itemA
    )
  )

dat_magical_newdata_plot %>% 
  pivot_longer(
    c(causal_item, similar_item),
    names_to = "item_type",
    values_to = "joint_distance"
  ) %>% 
  ggplot(aes(y = p_hat)) +

  ## horizontal connectors (fd_c → cd_c)
  geom_segment(
    data = dat_magical_newdata_plot,
    aes(
      x = causal_item,
      xend = similar_item,
      y = p_hat,
      yend = p_hat
    ),
    inherit.aes = FALSE,
    color = "grey70"
  ) +
  geom_point(aes(x = joint_distance, color = item_type)) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_smooth(aes(x = joint_distance, color = item_type),
              method = "lm") +
  theme_bw()  + 
  geom_text(
    data = dat_lab,
    aes(x = joint_distance, y = p_hat, label = label, color = item_type),
    # hjust = 1.1,
    vjust = 1,
    size = 3,
    show.legend = FALSE
  ) +
  geom_text(
    data = dat_magical_newdata_plot,
    # aes(x = pmin(fd_c, cd_c) - 0.02, 
     aes(x = ((causal_item + similar_item) / 2), 
        y = p_hat, label = target),
    inherit.aes = FALSE,
    vjust = -0.6,
    size = 3,
    color = "black"
  ) +
  labs(
    title = "Magical Condition",
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  ) +
  theme(legend.position = "top")


```


## Simulation test

for simulating my plot data

```{r}
set.seed(1)
n <- 15
fmc_c <- round(runif(n, 0, 0.5), 2)
fmc_s <- round(runif(n, -0.8, 0.2), 2)
pr_r <- 0.6 + 0.8 * fmc_c - 0.7 * fmc_s + rnorm(n, 0, 0.1)
pr = round(pr_r, 2)
pr <- round(rbeta(n, 5, 2), 2)

d_t <- data.frame(pr, fmc_c, fmc_s)

m_dt <- lm(pr ~ fmc_s + fmc_c, data = d_t)
summary(m_dt)

new_d <- data.frame(
    fmc_s = c(-0.6, -0.2, 0.1),
    fmc_c = c(0.1, 0.3, 0.45)
  )

predict(m_dt, new_d)

```


## Ordinary distances - long way

```{r}
dat_model <- dat_plot_distances_intervention %>% 
  mutate(subject_id = as.factor(subject_id),
         response = ifelse(response == "causal", 1, 0)) 

# Ordinary Intervention Condition
model_ordinary <- glmer(response ~ freesort_minus_causal_distance_causal +
                        freesort_minus_causal_distance_similar + 
                        (1 | subject_id), 
    data = dat_model %>% filter(condition == "ordinary"),
    family = binomial(link = 'logit'))

# effects_data <- allEffects(model_ordinary)

#extract predictions for all unique joint distance data points in the data
effects_data <- allEffects(
  model_ordinary,
  xlevels = list(
    freesort_minus_causal_distance_causal  =
      sort(unique(dat_model$freesort_minus_causal_distance_causal)),
    freesort_minus_causal_distance_similar =
      sort(unique(dat_model$freesort_minus_causal_distance_similar))
  )
)

causal_effect <- as.data.frame(effects_data$`freesort_minus_causal_distance_causal`)
similar_effect <- as.data.frame(effects_data$`freesort_minus_causal_distance_similar`)

causal_effect$Predictor <- "Causal Item"
similar_effect$Predictor <- "Similar Item"

colnames(causal_effect)[1] <- "JointDistance"
colnames(similar_effect)[1] <- "JointDistance"

combined_effects <- rbind(causal_effect, similar_effect)

combined_effects %>% 
  ggplot(aes(x = JointDistance, y = fit, color = Predictor)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_bw() +
  labs(
    title = "Ordinary Intervention Condition",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  labs(
  x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  y = "Probability\nSimilar Item                                             Causal Item",
  )

```

# The End

```{r}

```







