---
title: "Counterfactuals"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-08-22"
author: ""
---

# ReadMe

This is the analysis for the Counterfactuals study.  
The study had N = 105 (before exclusions).  
The independent variable is whether the preceding item in a counterfactual scenario is a Direct or Intrinsic item (within-subjects).   
The dependent variable is the likelihood of the target event occuring in the counterfactual scenario where the preceding item is blocked/absent. 

# Setup

## Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(
               lme4, 
               lmerTest,
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               conflicted,
               gt,
               webshot2,
               knitr,
               performance,
               effectsize,
               tidyverse,
               simr)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code", "main")
freesort_and_causal_distances_df_path <- paste0(base_path,
                                                "/analysis/measure-main-and-pilot/snapshots_study1_main_analysis/freesort_minus_causals.csv")

short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

compact_names <- c(
  "see something" = "see\nsomething",
  "hear something" = "hear\nsomething",
  "choose what to do" = "choose",
  "remember something" = "remember\nsomething",
  "think about something" = "think\nabout\nsomething",
  
  "take a walk" = "take\na walk", 
  "jump up and down" = "jump up\nand down",
  "reach for something" = "reach for\nsomething",
  "sit down" = "sit down",
  "kick something" = "kick\nsomething",
  
  "get sick" = "get sick",
  "feel scared" = "feel\nscared",
  "become hungry" = "become\nhungry",
  "experience pain" = "experience\npain",
  "get tired" = "get tired")

```

# Confirmatory Analysis - Prep

## Read data

```{r, warnings = FALSE}
data_path_cf <- paste0(base_path, "/data/counterfactuals/JO-mbc-main-counterfactuals-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_cf, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

rmarkdown::paged_table(d)

```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Wrangle data

Initial data frame: 30 trials * 48 subjects = 1440 rows.
"dat" data frame: (30 trials / 2 trials per row) * 48 subjects = 720 rows.

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  filter(attn_correct == "no") %>% 
  pull(subject_id) %>% 
  unique()

print(subjects_to_exclude)

dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>%
  filter(condition %in% c("counterfactual", "similarity")) %>% 
  mutate(condition = ifelse(condition == "counterfactual", "direct", "intrinsic")) %>%
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  select(-condition) %>% 
  select(subject_id, itemB, causal_itemA, similar_itemA, response_value) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order), 
         similar_itemA = factor(similar_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(item_type = case_when(
        !is.na(causal_itemA) ~ "causal_itemA",
        !is.na(similar_itemA) ~ "similar_itemA"),
        item = coalesce(as.character(causal_itemA), as.character(similar_itemA))) %>% 
  select(-causal_itemA, -similar_itemA) %>% 
  pivot_wider(names_from = item_type,
              values_from = c(item, response_value)) %>% 
  rename("causal_itemA" = item_causal_itemA,
         "similar_itemA" = item_similar_itemA, 
         "causal_itemA_counterfactual" = response_value_causal_itemA,
         "similar_itemA_counterfactual" = response_value_similar_itemA,
         "target" = itemB) 

rmarkdown::paged_table(dat)

n_subjects <- dat %>%
  distinct(subject_id) %>% 
  summarize(n_subjects = n())

paste0("N subjects: ", n_subjects)

```

## Summary stats

```{r}
# Raw Long form data
dat_long <- dat %>% 
  rename("Direct" = causal_itemA_counterfactual,
         "Intrinsic" = similar_itemA_counterfactual) %>% 
  pivot_longer(cols = c("Direct", "Intrinsic"), 
               names_to = "counterfactual_type",
               values_to = "likelihood") %>% 
  mutate(counterfactual_type = factor(counterfactual_type, levels = c("Direct", "Intrinsic"))) %>% 
  mutate(counterfactual = case_when(
    counterfactual_type == "Direct" ~ causal_itemA,
    counterfactual_type == "Intrinsic" ~ similar_itemA)) %>% 
  select(subject_id, target, counterfactual, counterfactual_type, likelihood) %>% 
  arrange(subject_id, target)

rmarkdown::paged_table(dat_long)

# Trial-level summary
dat_trials_summarized <- dat_long %>%
  group_by(target, counterfactual, counterfactual_type) %>%
  summarise(mean_likelihood = mean(likelihood, na.rm = TRUE),
            se_likelihood = sd(likelihood, na.rm = TRUE) / sqrt(n_distinct(subject_id)),
            .groups = "drop") 

rmarkdown::paged_table(dat_trials_summarized)

# Condition-level summary
dat_condition_level <- dat_long %>% 
  group_by(counterfactual_type) %>% 
  summarize(mean = mean(likelihood, na.rm = TRUE),
            sd = sd(likelihood, na.rm = TRUE))

rmarkdown::paged_table(dat_condition_level)
```

# Confirmatory Analysis - Figures

## Figure with slope

```{r, fig.width = 3.5, fig.height = 6}
fig_slope <- dat_long %>% 
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .2) +
  geom_point(data = dat_trials_summarized, aes(x = counterfactual_type, y = mean_likelihood), 
             alpha = 0.2, size = 5) +
  # geom_text(data = dat_trials_summarized %>%
  #             mutate(counterfactual = recode(counterfactual, !!!short_names)),
  #           aes(label = counterfactual, y = mean_likelihood),
  #           vjust = 1, size = 6) +
  geom_line(data = dat_trials_summarized, 
            aes(x = counterfactual_type, 
                y = mean_likelihood, 
                group = target), 
            alpha = 0.2, color = "black") +
  labs(y = "Counterfactual Likelihood", 
       x = "Preceding Item Type",
       fill = "Type") +
  theme_cowplot() +
  scale_fill_manual(values = c("#CCCCCC", "white")) + 
  theme(
        axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.position = "top",
        legend.title = element_text(size = 25),
        legend.text = element_text(size = 25)
        ) +
  ylim(0, 100)

fig_slope

fig_slope <- ggsave("figures/counterfactuals_slope.png", 
                    width = 3, height = 6, plot = fig_slope, bg = "white")

```

## Figure facet by trial

```{r, fig.width = 12, fig.height = 12}
# Wide version fig - short names
dat_plot_long_wide <- dat_long %>%
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(counterfactual = recode(counterfactual, !!!short_names)),
            aes(label = counterfactual, y = 95),
            vjust = 1, size = 6) + 
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
    facet_wrap(~target, nrow = 3, ncol = 5)

dat_plot_long_wide

# Wide version fig - compact names
dat_plot_long_wide_compact <- dat_long %>%
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(counterfactual = recode(counterfactual, !!!compact_names)),
            aes(label = counterfactual, y = 95),
            vjust = 1, size = 6) + 
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
    facet_wrap(~target, nrow = 3, ncol = 5)

dat_plot_long_wide_compact

# Long version fig - short names
dat_plot_long_long <- dat_long %>%
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_point(alpha = 0.1) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(counterfactual = recode(counterfactual, !!!compact_names)),
            aes(label = counterfactual, y = 95),
            vjust = 1, size = 6) + 
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17),
    legend.position = "none",
    strip.text = element_text(size = 16),
    strip.background = element_rect(fill = NA, color = "black")
    ) +
  facet_wrap(~target) 
  
dat_plot_long_long

dat_plot_long_long <- ggsave("figures/counterfactuals_slope_facet_by_trial.png", 
                                width = 10,
                                height = 8,
                    plot = dat_plot_long_long, 
                    bg = "white") 

```

## Figure single subject

```{r, fig.width = 12, fig.height = 12}
dat_long %>% 
  filter(subject_id == "subj_01") %>% 
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  geom_col(color = "black") +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_text(aes(label = counterfactual), y = 95, vjust = 1, size = 5) +
  scale_fill_manual(values = c("grey80", "white")) +
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  theme_cowplot() +
  theme(
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        strip.text = element_text(size = 16),
        strip.background = element_rect(fill = NA, color = "black"),
        legend.position = "none") +
  facet_wrap(~target)

```

# Confirmatory Analysis - Analysis

## Prepare data

```{r}
dat_model <- dat_long %>% 
  mutate(counterfactual_type = factor(counterfactual_type, levels = c("Intrinsic", "Direct")), 
         subject_id = as_factor(subject_id)) 

rmarkdown::paged_table(dat_model)

```

## Run model

```{r}
#model
model_effect_of_counterfactual_type <- lmerTest::lmer(likelihood ~ counterfactual_type +
                                              (1|subject_id), data = dat_model)

#model outputs
summary(model_effect_of_counterfactual_type)
standardize_parameters(model_effect_of_counterfactual_type)
confint(model_effect_of_counterfactual_type)

#odds ratios
fixef(model_effect_of_counterfactual_type)  
or <- exp(fixef(model_effect_of_counterfactual_type)[1])
or

#probabilities
effects_data <- allEffects(model_effect_of_counterfactual_type)
effects_df <- as.data.frame(effects_data$counterfactual)
effects_df

#plot model
plot(allEffects(model_effect_of_counterfactual_type))

```

## Check model

```{r}
check_model(model_effect_of_counterfactual_type)
```

# Distances - Prep

## Read distances 

```{r}
distances <- read_csv(freesort_and_causal_distances_df_path)

```

## Append distances

```{r}
#join distances to Trial level data
dat_trials_summarized_distances_long <- dat_trials_summarized %>% 
  left_join(distances %>% 
              rename("target" = itemB,
                     "counterfactual" = itemA,
                     "domain_counterfactual" = domain_itemA,
                     "domain_target" = domain_itemB,
                     "joint_distance" = freesort_minus_causal) %>% 
              mutate(target = factor(target, levels = desired_order)) %>% 
              relocate(target, .before = "counterfactual"),
            by = c("target", "counterfactual")) %>% 
  select(target, counterfactual, counterfactual_type, domain_target, 
         domain_counterfactual, mean_likelihood, joint_distance)

rmarkdown::paged_table(dat_trials_summarized_distances_long)

```

## Save joined distances

```{r}
write_csv(dat_trials_summarized_distances_long, "dat_counterfactuals_distances.csv")

```

## Read back in data frame

```{r}
analysis_path <- here("code", "main", "analysis")

dat_trials_summarized_distances_long <- read_csv(paste0(analysis_path,
                "/counterfactuals/dat_counterfactuals_distances.csv"))

```



# Distances - Figures


```{r}
fig_distances <- dat_trials_summarized_distances_long %>% 
  mutate(target = recode(target, !!!short_names),
         counterfactual = recode(counterfactual,!!!short_names)) %>% 
  mutate(labels = paste0("target: ", target, "\n", counterfactual_type, ": ", counterfactual)) %>% 
  ggplot(aes(y = mean_likelihood, x = joint_distance, color = counterfactual_type)) +
  geom_point(alpha = 0.4, size = 5) +
  geom_smooth(method = "lm") + 
  # geom_text(aes(label = labels), vjust = -0.5, size = 2) + #uncomment this to include labels
  theme_bw() +
  theme(axis.text.x = element_text(size = 30),
        axis.text.y = element_text(size = 30),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Counterfactuals",
    color = "Choice Item",
    fill = "Choice Item",
    x = "More intrinsically relevant, More directly relevant",
    y = "Likelihood"
  ) 

fig_distances

fig_distances <- ggsave("figures/counterfactuals_distances.png", 
                        width = 6, height = 4, plot = fig_distances, bg = "white")

# fig_distances_labels <- ggsave("figures/counterfactual_distances_labels.png", 
#                                width = 5, height = 5, plot = fig_distances_labels, bg = "white")

```

# Distance - Analysis

## Append data

```{r}
#join distances to subject-level data
dat_long_distances <- dat_long %>% 
  left_join(distances %>% 
              rename("target" = itemB,
                     "counterfactual" = itemA,
                     "domain_counterfactual" = domain_itemA,
                     "domain_target" = domain_itemB,
                     "joint_distance" = freesort_minus_causal) %>% 
              mutate(target = factor(target, levels = desired_order)) %>% 
              relocate(target, .before = "counterfactual"),
            by = c("target", "counterfactual")) %>% 
  select(subject_id, target, counterfactual, counterfactual_type, likelihood,
         domain_target, domain_counterfactual, joint_distance)

rmarkdown::paged_table(dat_long_distances)

```

## Model - Distance 

```{r}
model_effect_of_distance <- lmerTest::lmer(likelihood ~ joint_distance + (1|subject_id), 
               data = dat_long_distances)

#model outputs
summary(model_effect_of_distance)
standardize_parameters(model_effect_of_distance)
confint(model_effect_of_distance)

#plot
plot(allEffects(model_effect_of_distance))

```

# THE END

```{r}

```


