---
title: "Item selection"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-07-16"
author: Joseph Outa
---

This is the item selection for the causal chain task 

Q: does this also include item selection for other tasks? It seems so. See if i can reduce the script to only focus on Causal

# Setup

## load packages

```{r, setup, include = FALSE}
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

# paths
## script inputs
base_path <- here("code", "main", "analysis", "study1-measure-main-and-pilot")
snapshots_input_path <- paste0(base_path, "/snapshots_study1_main_analysis") 
data_input_path <- paste0(snapshots_input_path, "/combined_data_processed_step2.csv")
freesort_minus_causal_distances_output_path <- paste0(snapshots_input_path, "/freesort_minus_causals.csv")
snapshots_output_path <- paste0(base_path, "/figures/item-selection/") #for saving item selection csvs

```

## Read data

```{r}
df_combined <- read_csv(data_input_path)

#how many subjects
paste0("subject count: ", length(unique(df_combined$subject_id)))

```

# Summarize distances

This is where we normalize! uncomment to see previous plots

```{r}
#get mean distances by item pairs
df_pair_means <- df_combined %>% 
  select(subject_id, itemA, itemB, freesort_distance, causal_distance) %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>%
  summarize(mean_causal_distance = mean(causal_distance, na.rm = TRUE),
         mean_freesort_distance = mean(freesort_distance, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(mean_causal_distance = (mean_causal_distance - min(mean_causal_distance)) / (max(mean_causal_distance) - min(mean_causal_distance)), #NORMALIZE distances! Uncomment to see former plots!
         mean_freesort_distance = (mean_freesort_distance - min(mean_freesort_distance)) / (max(mean_freesort_distance) - min(mean_freesort_distance))) %>%
  separate(item_pairs, c("itemA", "itemB"), sep = "_")

#add domain labels
df_item_pair_means_domain <- df_pair_means %>%
  left_join(df_combined %>% 
              select(itemA, itemB, domain_itemA, domain_itemB) %>% 
              distinct(),
              by = c("itemA", "itemB")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order))

df_item_pair_means_domain_long <- df_item_pair_means_domain %>% 
  pivot_longer(
    cols = c("mean_causal_distance", "mean_freesort_distance"),
    names_to = "mean_type",
    values_to = "values"
  ) 

df_item_pair_means_freesort_minus_causal <- df_item_pair_means_domain_long %>% 
  pivot_wider(names_from = "mean_type",
              values_from = "values") %>% #lol could have just directly mutated joint distances intsead of longifying the undoing it by widening
  mutate(freesort_minus_causal = mean_freesort_distance - mean_causal_distance) 

df_item_pair_means_freesort_minus_causal
# #save as csv
# write.csv(df_item_pair_means_freesort_minus_causal,
#           freesort_minus_causal_distances_output_path, row.names = F)

colnames(df_item_pair_means_freesort_minus_causal)
```

# Causal Chain items 

For the Causal Chain vs Common Cause experiment, we did the following:   
- first we visually identified incomplete (i.e. cause rating < 0.5) causal paths between two pairs of items. 
- we identified 9 such pairs. These became the 9 pairs of target items that formed our 9 trials. Each trial has 2 target items, a first event, and a third event, and subjects will be tasked with selecting the middle item. 
- We then selected the causal item as such: for each of the two target items, we computed their mean causal distance with all other possible 13 items, e.g. mean(target 1 - x1, target 2 - x1), mean(target 1 - x2, target 2, x2)...and so on until x13. The middle item x[n] with the lowest mean causal distance became the causal item. 
- We then selected the similar item as such: we rank ordered the mean freesort distance between the two targets and all other items e.g. mean(target 1 - x1, target 2 - x1)...mean(target 1 - x2, target 2 - x2)...and so on until x13. The x[n] with the lowest mean distance became the similar item. (or as it were, the Latent Item)

## Using joint distances - Compact version

Damn it! I ran with the joint causal distance for Causal Chain, but not the joint similar distance for Common Cause.
Update: It actually gives all ranked middle items, so i can choose for myself which is similar and which is causal

```{r}
distances <- df_item_pair_means_freesort_minus_causal

best_middle <- function(distances, first, third,
                        metric = freesort_minus_causal,
                        pick = c("min","max")) {
  pick <- match.arg(pick)

  triad_means <- distances %>%
    select(-c(domain_itemA, domain_itemB)) %>%
    mutate(itemA = as.character(itemA),
           itemB = as.character(itemB)) %>%
    filter((itemA == first & itemB != third) |
           (itemB == third & itemA != first)) %>%
    mutate(other_item = ifelse(itemA == first, itemB, itemA)) %>%
    group_by(other_item) %>%
    summarise(mean_joint = mean({{ metric }}), .groups = "drop") %>%
    arrange(if (pick == "max") mean_joint else desc(mean_joint))

  list(
    best = triad_means %>% slice(1) %>% pull(other_item),
    ranking = triad_means
  )
}

# best_middle(distances, "see something", "hear something", pick = "min")$best
# best_middle(distances, "choose what to do", "hear something", pick = "min")$best

targets <- tibble::tribble(
  ~first,               ~third,
  "see something",      "hear something",
  "choose what to do",  "hear something",
  "remember something", "hear something",
  "sit down",           "jump up and down",
  "jump up and down",   "sit down",
  "take a walk",        "reach for something",
  "get tired",          "feel scared",
  "become hungry",      "feel scared",
  "get sick",           "become hungry"
)

all_rankings <- targets %>%
  mutate(middle_items = map2(first, third, ~best_middle(distances, .x, .y, pick = "min")$ranking)) %>%
  unnest(middle_items) %>%
  group_by(first, third) %>%
  mutate(rank = row_number()) %>%
  ungroup() 

distances_causal_chain_common_causes <- all_rankings %>% 
  rename("first_item" = first,
         "third_item" = third,
         "middle_item" = other_item,
         "freesort_minus_causal_distance" = mean_joint)
#needs: causal_distance_middle_causal_first, causal_distance_middle_causal_third,
#freesort_distance_middle_causal_first, freesort_distance_middle_causal_first  (mean df to first and third)
#for now ignore, since I do not need for joint distances plot

distances_causal_chain_common_causes

# View(distances_causal_chain)

# write.csv(distances_causal_chain_common_causes, "distances_causal_chain.csv")

```

### Only the top middle items

```{r}
top_middles <- all_rankings %>%
  group_by(first, third) %>%
  slice(1) %>%
  ungroup()

top_middles

```


# Common Cause items

Selecting items for study - Freesort Distances

## first triad

```{r}
distances <- df_item_pair_means_freesort_minus_causal

triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "see something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "see something") %>% 
  mutate(other_item = ifelse(itemA == "see something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
            mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)
        
```


#---------------------------------------------------
## Using Causal Distances

### first triad

see something -> x -> hear something

Checks out distance between first target = see something, a middle choice item, and third target = hear something. So basically checks every permutation of see something -> [other of the 13 items] -> hear something.

```{r}
distances <- df_item_pair_means_freesort_minus_causal

triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "see something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "see something") %>% 
  mutate(other_item = ifelse(itemA == "see something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
            mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

# View(triad_means)
triad_means
        
```

Trying to make a long data frame

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "see something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "see something") %>% 
  mutate(other_item = ifelse(itemA == "see something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
            mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

# View(triad_means)

```


### second triad

choose what to do -> x -> hear something

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "choose what to do" & itemB != "hear something" |
           itemB == "hear something" & itemA != "choose what to do") %>% 
  mutate(other_item = ifelse(itemA == "choose what to do", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)
         
```

### third triad

remember something -> x -> hear something

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "remember something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "remember something") %>% 
  mutate(other_item = ifelse(itemA == "remember something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### fourth triad

sit down -> x -> jump up and down

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "sit down" & itemB != "jump up and down" |
           itemB == "jump up and down" & itemA != "sit down") %>% 
  mutate(other_item = ifelse(itemA == "sit down", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### fifth triad

jump up and down -> x -> sit down

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "jump up and down" & itemB != "sit down" |
           itemB == "sit down" & itemA != "jump up and down") %>% 
  mutate(other_item = ifelse(itemA == "jump up and down", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### sixth triad

take a walk -> x -> reach for something

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "take a walk" & itemB != "reach for something" |
           itemB == "reach for something" & itemA != "take a walk") %>% 
  mutate(other_item = ifelse(itemA == "take a walk", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### seventh triad

get tired -> x -> feel scared

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "get tired" & itemB != "feel scared" |
           itemB == "feel scared" & itemA != "get tired") %>% 
  mutate(other_item = ifelse(itemA == "get tired", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### eighth triad

become hungry -> x -> feel scared

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "become hungry" & itemB != "feel scared" |
           itemB == "feel scared" & itemA != "become hungry") %>% 
  mutate(other_item = ifelse(itemA == "become hungry", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

### ninth triad

get sick -> x -> become hungry

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "get sick" & itemB != "become hungry" |
           itemB == "become hungry" & itemA != "get sick") %>% 
  mutate(other_item = ifelse(itemA == "get sick", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_causal_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```




# Common Cause items

Selecting items for study - Freesort Distances

## first triad

```{r}
distances <- df_item_pair_means_freesort_minus_causal

triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "see something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "see something") %>% 
  mutate(other_item = ifelse(itemA == "see something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
            mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)
        
```

## second triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "choose what to do" & itemB != "hear something" |
           itemB == "hear something" & itemA != "choose what to do") %>% 
  mutate(other_item = ifelse(itemA == "choose what to do", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)
         
```

## third triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "remember something" & itemB != "hear something" |
           itemB == "hear something" & itemA != "remember something") %>% 
  mutate(other_item = ifelse(itemA == "remember something", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

## fourth triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "sit down" & itemB != "jump up and down" |
           itemB == "jump up and down" & itemA != "sit down") %>% 
  mutate(other_item = ifelse(itemA == "sit down", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

## fifth triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "jump up and down" & itemB != "sit down" |
           itemB == "sit down" & itemA != "jump up and down") %>% 
  mutate(other_item = ifelse(itemA == "jump up and down", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

## sixth triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "take a walk" & itemB != "reach for something" |
           itemB == "reach for something" & itemA != "take a walk") %>% 
  mutate(other_item = ifelse(itemA == "take a walk", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

## seventh triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "get tired" & itemB != "feel scared" |
           itemB == "feel scared" & itemA != "get tired") %>% 
  mutate(other_item = ifelse(itemA == "get tired", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

View(triad_means)

```

## eighth triad

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "become hungry" & itemB != "feel scared" |
           itemB == "feel scared" & itemA != "become hungry") %>% 
  mutate(other_item = ifelse(itemA == "become hungry", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```

## ninth triad

get sick -> remember

```{r}
triad_distances <- distances %>%
  select(-c(domain_itemA, domain_itemB)) %>% 
  mutate(itemA = as.character(itemA),
         itemB = as.character(itemB)) %>% 
  filter(itemA == "get sick" & itemB != "become hungry" |
           itemB == "become hungry" & itemA != "get sick") %>% 
  mutate(other_item = ifelse(itemA == "get sick", itemB, itemA)) %>% 
  group_by(itemA) %>% 
  arrange(other_item)

triad_means <- triad_distances %>% 
  group_by(other_item) %>% 
  mutate(mean_mean_freesort_distance = mean(mean_freesort_distance),
         mean_mean_causal_distance = mean(mean_causal_distance)) %>% 
  arrange(mean_mean_freesort_distance)

triad_means %>% 
  ungroup() %>% 
  slice(1) %>% 
  pull(other_item)

```


# END

```{r}
#placeholder
```

