---
title: "Item selection"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-07-16"
author: Joseph Outa
---

# Setup

## Load packages

```{r, setup, include = FALSE}
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

# paths
## script inputs
base_path <- here("code", "main", "analysis", "1.5_item_selection")
snapshots_input_path <- paste0(base_path, "/snapshots_study1_combined_analysis") 
data_input_path <- paste0(snapshots_input_path, "/combined_data_processed_step2.csv")
freesort_minus_causal_distances_output_path <- paste0(snapshots_input_path, "/freesort_minus_causals.csv")
snapshots_output_path <- paste0(base_path, "/figures/item-selection/") #for saving item selection csvs

```

## Read data

```{r}
df_combined <- read_csv(data_input_path)

#how many subjects
df_combined %>% 
  slice(length(df_combined$subject_id)) %>% 
  pull(subject_id)

rmarkdown::paged_table(df_combined)

```

# Experiment 2 (Explanation), 3 (Counterfactual), and 5 (Intervention) - Preceding causes

### Select long list 

```{r}
#get mean distances by item pairs
df_pair_means <- df_combined %>% 
  select(subject_id, itemA, itemB, freesort_distance, causal_distance) %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>%
  summarize(mean_causal_distance = mean(causal_distance, na.rm = TRUE),
         mean_freesort_distance = mean(freesort_distance, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # mutate(mean_causal_distance = (mean_causal_distance - min(mean_causal_distance)) / (max(mean_causal_distance) - min(mean_causal_distance)), 
  # mean_freesort_distance = (mean_freesort_distance - min(mean_freesort_distance)) / (max(mean_freesort_distance) - min(mean_freesort_distance))) %>% #re-normalizess
  separate(item_pairs, c("itemA", "itemB"), sep = "_")

#add domain labels
df_item_pair_means_domain <- df_pair_means %>%
  left_join(df_combined %>% 
              select(itemA, itemB, domain_itemA, domain_itemB) %>% 
              distinct(),
              by = c("itemA", "itemB")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order))

df_item_pair_means_domain_long <- df_item_pair_means_domain %>% 
  pivot_longer(
    cols = c("mean_causal_distance", "mean_freesort_distance"),
    names_to = "mean_type",
    values_to = "values") 

df_item_pair_means_freesort_minus_causal <- df_item_pair_means_domain_long %>% 
  pivot_wider(names_from = "mean_type",
              values_from = "values") %>% 
  mutate(freesort_minus_causal = mean_freesort_distance - mean_causal_distance)

df_item_pair_means_freesort_minus_causal

#save as csv
write.csv(df_item_pair_means_freesort_minus_causal,
          freesort_minus_causal_distances_output_path, row.names = F)

```

### Plot long list table

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemB) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemB) %>% 
  rename("cd" = mean_causal_distance,
         "fd" = mean_freesort_distance,
         "fd_minus_cd" = freesort_minus_causal) %>% 
  mutate(cd = round(cd, 2),
         fd = round(fd, 2),
         fd_minus_cd = round(fd_minus_cd, 2)) %>% 
  relocate(fd, .before = cd)

#Generate a unique color for each itemB
unique_items <- unique(long_list_items$itemB)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemB,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/preceding_long-list.png")


```

### Select short list 


```{r}
similar_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemB) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

causal_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemB) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
#join
short_list_selected_items_domain_constraints <- causal_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemA,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items_same_domain %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemA, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemB") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemB", .before = "causal_choice") %>% 
  rename(target_item = itemB) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

#view items
paged_table(short_list_selected_items_domain_constraints)

#save as csv
write_csv(file = "snapshots_study1_combined_analysis/preceding_short_list.csv",
          short_list_selected_items_domain_constraints)

```

### Plot short list table

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ", ", freesort_minus_causal_distance_causal, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ", ", freesort_minus_causal_distance_similar, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #db9728; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #d0495a; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #00788a; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item)) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("CC item<br>(CP distance, Freesort distance, joint distance)"),
    similar_choice = md("CO item<br>(CP distance, Freesort distance, joint distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#db9728", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "mind")) %>%
  tab_style(
    style = list(
      cell_text(color = "#d0495a", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "action")) %>%
  tab_style(
    style = list(
      cell_text(color = "#00788a", weight = "bold")),
    locations = cells_body(
      columns = group,
      rows = group == "body")) %>%
  tab_options(
    table.font.names = "Arial")

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/preceding_short-list.png")
```

# Experiment 5 (Prediction) - Following causes

## Plot long list table

```{r}
long_list_items <- df_item_pair_means_freesort_minus_causal %>% 
  group_by(itemA) %>% 
  arrange(desc(freesort_minus_causal)) %>% 
  ungroup() %>% 
  arrange(itemA)

#Generate a unique color for each itemA
unique_items <- unique(long_list_items$itemA)
color_palette <- scales::hue_pal()(length(unique_items))  # Generate distinct colors
color_map <- setNames(color_palette, unique_items)

#Create the table with conditional formatting
long_list_items <- long_list_items %>% 
  gt() %>% 
  data_color(
    columns = itemA,  #apply color to this column
    colors = color_map
  )

long_list_items 

gtsave(long_list_items, "figures/item-selection/following_long-list.png")

```

## Select short list 

```{r}
similar_items_same_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA == domain_itemB) %>% #first condition
  group_by(itemA) %>%
  slice_min(freesort_minus_causal, with_ties = FALSE) %>% #second and third condition
  ungroup()

causal_items_cross_domain <- df_item_pair_means_freesort_minus_causal %>%
  filter(domain_itemA != domain_itemB) %>% #firs condition
  group_by(itemA) %>%
  slice_max(freesort_minus_causal, with_ties = FALSE) %>% #2nd and third condition
  ungroup()
  
#join
short_list_selected_items_domain_constraints <- causal_items_cross_domain %>% 
  select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
  rename(causal_choice = itemB,
         causal_distance_causal_choice = mean_causal_distance,
         freesort_distance_causal_choice = mean_freesort_distance,
         freesort_minus_causal_distance_causal = freesort_minus_causal) %>% 
  left_join(similar_items_same_domain %>% 
              select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>%
              rename(similar_choice = itemB, 
                     causal_distance_similar_choice = mean_causal_distance,
                     freesort_distance_similar_choice = mean_freesort_distance,
                     freesort_minus_causal_distance_similar = freesort_minus_causal),
            by = "itemA") %>% 
  relocate("similar_choice", .after = "causal_choice") %>% 
  relocate("itemA", .before = "causal_choice") %>% 
  rename(target_item = itemA) %>% 
  mutate(causal_distance_causal_choice = round(causal_distance_causal_choice, 2),
         freesort_distance_causal_choice = round(freesort_distance_causal_choice, 2),
         causal_distance_similar_choice = round(causal_distance_similar_choice, 2),
         freesort_distance_similar_choice = round(freesort_distance_similar_choice, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2))

write_csv(file = "snapshots_study1_combined_analysis/following_short_list.csv",
          short_list_selected_items_domain_constraints)

#view items
paged_table(short_list_selected_items_domain_constraints)


```

## Plot short list table

```{r}
short_list_table_domain_constraints <- short_list_selected_items_domain_constraints %>%
  mutate(
    group = case_when(
      target_item %in% c("see something", "hear something", "remember something", "think about something", "choose what to do") ~ "mind",
      target_item %in% c("reach for something", "sit down", "jump up and down", "kick something", "take a walk") ~ "action",
      target_item %in% c("get tired", "become hungry", "feel scared", "experience pain", "get sick") ~ "body",
      TRUE ~ "other"
    ),
    causal_choice = paste0(causal_choice, " (", causal_distance_causal_choice, ", ", freesort_distance_causal_choice, ", ", freesort_minus_causal_distance_causal, ")"),
    similar_choice = paste0(similar_choice, " (", causal_distance_similar_choice, ", ", freesort_distance_similar_choice, ", ", freesort_minus_causal_distance_similar, ")"),
        #inline styles to highlight text for 'target_item' based on group
    target_item = case_when(
      group == "mind" ~ paste0("<span style='color: #db9728; font-weight: bold;'>", target_item, "</span>"),
      group == "action" ~ paste0("<span style='color: #d0495a; font-weight: bold;'>", target_item, "</span>"),
      group == "body" ~ paste0("<span style='color: #00788a; font-weight: bold;'>", target_item, "</span>"),
      TRUE ~ target_item
    )
  ) %>% 
  #replace group labels with blanks after the first row of each group
  group_by(group) %>%
  mutate(group = ifelse(row_number() == 1, group, "")) %>%
  ungroup() %>%
  select(group, target_item, causal_choice, similar_choice)  # Keep the domain column


df_table_domain_constraints <- short_list_table_domain_constraints %>%
  gt() %>%
  tab_header(
    title = "Target and Choice Items"
  ) %>%
  cols_label(
    group = "Domain",
    target_item = "Target Item",
    causal_choice = md("CC item<br>(CP distance, Freesort distance, joint distance)"),
    similar_choice = md("CO item<br>(CP distance, Freesort distance, joint distance)")
  ) %>%
  fmt_markdown(columns = target_item) %>%  # Render markdown for inline styles
  fmt_markdown(columns = c(causal_choice, similar_choice)) %>%
  #custom styles for domain (group) column
  tab_style(
    style = list(
      cell_text(color = "#db9728", weight = "bold")  
    ),
    locations = cells_body(
      columns = group,
      rows = group == "mind"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#d0495a", weight = "bold")
    ),
    locations = cells_body(
      columns = group,
      rows = group == "action"
    )
  ) %>%
  tab_style(
    style = list(
      cell_text(color = "#00788a", weight = "bold") 
    ),
    locations = cells_body(
      columns = group,
      rows = group == "body"
    )
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

df_table_domain_constraints

gtsave(df_table_domain_constraints,
       "figures/item-selection/following_short-list.png")
```

# Experiment 6 (Biological Reasoning v Causal Triads) - Middle items

```{r}
library(tidyverse)
library(gt)

choice_table <- tribble(
  ~domain, ~first_target, ~second_target, ~cc_item, ~cc_distance, ~co_item, ~co_distance,
  "mind", "see something", "hear something", "take a walk", 0.581, "remember something", 0.052,
  "mind", "choose what to do", "hear something", "take a walk", 0.492, "see something", -0.126,
  "mind", "remember something", "hear something", "feel scared", 0.458, "think about something", -0.086,
  "action", "sit down", "jump up and down", "experience pain", 0.401, "take a walk", -0.568,
  "action", "jump up and down", "sit down", "get tired", 0.664, "take a walk", -0.398,
  "action", "take a walk", "reach for something", "see something", 0.545, "jump up and down", -0.330,
  "body", "get tired", "feel scared", "choose what to do", 0.532, "become hungry", -0.118,
  "body", "become hungry", "feel scared", "think about something", 0.699, "get tired", -0.058,
  "body", "get sick", "become hungry", "remember something", 0.518, "experience pain", -0.052
) %>%
  group_by(domain) %>%
  mutate(domain_display = ifelse(row_number() == 1, domain, "")) %>%
  ungroup() %>%
  select(domain_display, first_target, second_target, cc_item, cc_distance, co_item, co_distance)

color_item <- function(item) {
  case_when(
    item %in% c("see something", "hear something", "remember something",
                "think about something", "choose what to do") ~
      paste0("<span style='color:#db9728;font-weight:bold;'>", item, "</span>"),

    item %in% c("reach for something", "sit down", "jump up and down",
                "kick something", "take a walk") ~
      paste0("<span style='color:#d0495a;font-weight:bold;'>", item, "</span>"),

    item %in% c("get tired", "become hungry", "feel scared",
                "experience pain", "get sick") ~
      paste0("<span style='color:#00788a;font-weight:bold;'>", item, "</span>"),

    TRUE ~ item
  )
}

choice_table <- choice_table %>%
  mutate(
    first_target = color_item(first_target),
    second_target = color_item(second_target)
  )

choice_table_gt <- choice_table %>%
  gt() %>%
  cols_label(
    domain_display = "domain",
    first_target = "First target",
    second_target = "Second target",
    cc_item = "CC item",
    cc_distance = md("Mean<br>joint<br>distance"),
    co_item = "CO item",
    co_distance = md("Mean<br>joint<br>distance")
  ) %>%
  tab_spanner(
    label = "Target items",
    columns = c(first_target, second_target)
  ) %>%
  tab_spanner(
    label = "Middle item in forced choice response",
    columns = c(cc_item, cc_distance, co_item, co_distance)
  ) %>%
  fmt_markdown(
    columns = c(first_target, second_target)
  ) %>% 
  fmt_number(
    columns = c(cc_distance, co_distance),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_text(color = "#db9728", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "mind")
  ) %>%
  tab_style(
    style = cell_text(color = "#d0495a", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "action")
  ) %>%
  tab_style(
    style = cell_text(color = "#00788a", weight = "bold"),
    locations = cells_body(columns = domain_display, rows = domain_display == "body")
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", align = "center"),
    locations = cells_column_spanners()
  ) %>%
  tab_options(
    table.font.names = "Arial",
    # table.font.size = px(22),
    table.border.top.width = px(2),
    table.border.bottom.width = px(2),
    column_labels.border.top.width = px(2),
    column_labels.border.bottom.width = px(2),
    data_row.padding = px(10)
  ) #%>%
#  opt_table_lines(extent = "all")

choice_table_gt

gtsave(
  choice_table_gt,
  "figures/item-selection/experiment_6.png"
)
```

# Demographics table

```{r}

experiment_table <- tribble(
  ~measure, ~experiment_1, ~experiment_2, ~experiment_3, ~experiment_4, ~experiment_5, ~experiment_6,
  "N after exclusions", "101", "104", "102", "102", "105", "104",
  "N excluded (reason)", "1 (failed attention check)", "1 (failed attention check)", "3 (failed attention check)", "5 (failed attention check)", "0", "0",
  "Mean age (min, max)", "38.06 (19, 73)", "40.10 (20, 80)", "41.07 (21, 70)", "42.73 (19, 79)", "41.5 (19, 79)", "42.61 (18, 75)",
  "Female", "41", "41", "53", "63", "59", "56",
  "Male", "60", "63", "52", "38", "45", "45",
  "Non-binary", "1", "3", "1", "NA", "NA", "1",
  "White", "73", "74", "82", "79", "85", "80",
  "Black/African American", "17", "9", "8", "8", "6", "8",
  "Asian", "8", "15", "12", "13", "12", "10",
  "Latino/Hispanic", "2", "1", "1", "NA", "NA", "NA",
  "Other", "7", "NA", "1", "5", "2", "6")

experiment_table_gt <- experiment_table %>%
  gt() %>%
  cols_label(
    measure = "",
    experiment_1 = md("Experiment 1<br>(Measure)"),
    experiment_2 = md("Experiment 2<br>(Explanation)"),
    experiment_3 = md("Experiment 3<br>(Counterfactuals)"),
    experiment_4 = md("Experiment 4<br>(Inference v Prediction)"),
    experiment_5 = md("Experiment 5<br>(Magical v Ordinary Intervention)"),
    experiment_6 = md("Experiment 6<br>(Biological Reasoning v Causal Triads)")
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = measure)
  ) %>%
  tab_options(
    table.font.names = "Arial"
  )

experiment_table_gt

gtsave(
  experiment_table_gt,
  "figures/item-selection/all_experiments_demographics.png"
)

```

# THE END

```{r}
#placeholder
```

