---
title: "study 1 analysis"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-7-1"
author: Joseph Outa
---

Background:
This is the analysis script for the combined dataset for study 1 (N = 152), consisting of:   
1: the pilot study (i.e. Study 1 of the 2025 Cogsci Paper: "Adults hold two parallel causal frameworks for reasoning about people’s minds, actions and bodies", ran on 12/13/24, N = 50).  
2: the main study (i.e. the replication of Study 1, ran on 6/30/25, N = 102)

Study 1 presented two tasks in a random order in a within-subjects design: a Freesorting Task and a Causal Task. Subjects sorted 15 items in a sorting canvas, and rated causal relatedness between all 210 pairs of the 15 items (excluding self pairs). 

The subjects were recruited online via Cloud Research Connect. Study demo: https://liulaboratory-experiments.github.io/mbc/study1

The two research questions are: (1) How do subjects sort items? Do they sort based on three latent causes, 2 latent causes, 6 latent causes, or feature-based similarity. (2) Do subjects' direct cause representations (from the Causal Task) reflect latent cause boundaries or do they go beyond, and if so, what is their structure?

The manuscript and project materials for the pilot study can be found at: https://github.com/liulaboratory-experiments/mind-body-action-causation

Script description:
This script:-  
- proceeds from the output of the preprocessing script.   
- takes as input `combined_data_processed_step1.csv`, and `data_model_prediction.csv`
- plots Sorting and Causal Task rdms, gets correlations between empirical and models RDM, gets within subject correlations.   
- outputs `combined_data_freesort_mins_causals.csv` for use in study 2 script for item selection.

What we do: calculate euclidean distances within subjects, then immediately normalize, then average to get mean rdm. Then we min-max normalize that mean. (so 2 normalizations are done)

# Setup

## Load packages

```{r, setup, include = FALSE}
#knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ 
       conflict_prefer(.x, "dplyr"))

conflicts_prefer(simr::fixed)
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")
domain_order <- c("mind", "action", "bio")
freesort_columns <- c("subject_id", "x", "y", "item")
freesort_columns_with_trial_order <- c("subject_id", "x", "y", "item", "trial_type", "trial_type_order")
causation_columns <- c("subject_id", "itemA", "itemB", "response")

# paths
## script inputs
base_path <- here("code", "main", "analysis", "1.5_item_selection")
snapshots_input_path <- paste0(base_path, "/snapshots_study1_preprocessing_analysis") 
data_input_path <- paste0(snapshots_input_path, "/combined_data_processed_step1.csv")

## script outputs
snapshots_output_path <- paste0(base_path, "/snapshots_study1_combined_analysis")

## saved dataframes 
data_processed_output_path <- paste0(snapshots_output_path, "/combined_data_processed_step2.csv") #used in item-selection-main script

```

## Read data

```{r}
d <- read_csv(data_input_path)

#how many subjects
d %>% 
  slice(length(d$subject_id)) %>% 
  pull(subject_id)

```

## Reshape data
Create separate data frames for Sorting Task, Causal Task and a combined data frame

```{r}
df_causal <- d %>%
  filter(trial_type == "causation", !attention_check, itemA != itemB) %>%
  select(all_of(causation_columns)) %>%
  
# Normalize causal distances and flip scale
  mutate(
    causal_distance = (1 - response / 100 - min(1 - response / 100, na.rm = TRUE)) /
                            (max(1 - response / 100, na.rm = TRUE) - min(1 - response / 100, na.rm = TRUE))
  ) %>%
  select(subject_id, itemA, itemB, causal_distance) %>% 
  mutate(domain_itemA = case_when(itemA == "hear something" ~ "mind", #labels for first item of pair
                             itemA == "choose what to do" ~ "mind",
                             itemA == "remember something" ~ "mind",
                             itemA == "think about something" ~ "mind",
                             itemA == "see something" ~ "mind",
                             itemA == "reach for something" ~ "action",
                             itemA == "sit down" ~ "action", 
                             itemA == "jump up and down" ~ "action",
                             itemA == "kick something" ~ "action",
                             itemA == "take a walk" ~ "action",
                             itemA == "get tired" ~ "bio", 
                             itemA == "become hungry" ~ "bio",
                             itemA == "feel scared"~ "bio",
                             itemA == "experience pain"~ "bio",
                             itemA == "get sick"~ "bio"),
         domain_itemB = case_when(itemB == "hear something" ~ "mind", 
                               itemB == "choose what to do" ~ "mind",
                               itemB == "remember something" ~ "mind",
                               itemB == "think about something" ~ "mind",
                               itemB == "see something" ~ "mind",
                               itemB == "reach for something" ~ "action",
                               itemB == "sit down" ~ "action", 
                               itemB == "jump up and down" ~ "action",
                               itemB == "kick something" ~ "action",
                               itemB == "take a walk" ~ "action",
                               itemB == "get tired" ~ "bio", 
                               itemB == "become hungry" ~ "bio",
                               itemB == "feel scared"~ "bio",
                               itemB == "experience pain"~ "bio",
                               itemB == "get sick"~ "bio")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemA = factor(itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) 


df_freesort <- d %>%
  filter(trial_type == "free_sort") %>%
  select(all_of(freesort_columns_with_trial_order)) %>%
  rename(item_freesort = item) %>%
  
  #expand pairs within each subject
  group_by(subject_id, trial_type_order) %>%
  summarize(pairs = list(expand.grid(itemA = item_freesort, itemB = item_freesort, stringsAsFactors = FALSE)), .groups = "drop") %>%
  unnest(pairs) %>%
  filter(itemA != itemB) %>%
  
  #join in freesort coordinates
  left_join(d %>% filter(trial_type == "free_sort") %>%
              select(subject_id, itemA = item, x, y),
            by = c("subject_id", "itemA")) %>%
  rename(x_itemA = x, y_itemA = y) %>%
  
  left_join(d %>% filter(trial_type == "free_sort") %>%
              select(subject_id, itemB = item, x, y),
            by = c("subject_id", "itemB")) %>%
  rename(x_itemB = x, y_itemB = y) %>%
  
  group_by(subject_id) %>% 
  
  #compute and normalize Euclidean distances
  mutate(
    euclidean_distance = sqrt((x_itemA - x_itemB)^2 + (y_itemA - y_itemB)^2),
    freesort_distance = round( (euclidean_distance - min(euclidean_distance, na.rm = TRUE)) /
                    (max(euclidean_distance, na.rm = TRUE) - min(euclidean_distance, na.rm = TRUE)),2),
    
    trial_type_order = ifelse(trial_type_order == "first", "causation_second", "causation_first"),
    
    itemA = factor(itemA, levels = desired_order),
    itemB = factor(itemB, levels = desired_order)) %>%
  select(subject_id, itemA, itemB, freesort_distance, trial_type_order) %>%
  ungroup() %>% 
  mutate(domain_itemA = case_when(itemA == "hear something" ~ "mind", #labels for first item of pair
                             itemA == "choose what to do" ~ "mind",
                             itemA == "remember something" ~ "mind",
                             itemA == "think about something" ~ "mind",
                             itemA == "see something" ~ "mind",
                             itemA == "reach for something" ~ "action",
                             itemA == "sit down" ~ "action", 
                             itemA == "jump up and down" ~ "action",
                             itemA == "kick something" ~ "action",
                             itemA == "take a walk" ~ "action",
                             itemA == "get tired" ~ "bio", 
                             itemA == "become hungry" ~ "bio",
                             itemA == "feel scared"~ "bio",
                             itemA == "experience pain"~ "bio",
                             itemA == "get sick"~ "bio"),
         domain_itemB = case_when(itemB == "hear something" ~ "mind", 
                               itemB == "choose what to do" ~ "mind",
                               itemB == "remember something" ~ "mind",
                               itemB == "think about something" ~ "mind",
                               itemB == "see something" ~ "mind",
                               itemB == "reach for something" ~ "action",
                               itemB == "sit down" ~ "action", 
                               itemB == "jump up and down" ~ "action",
                               itemB == "kick something" ~ "action",
                               itemB == "take a walk" ~ "action",
                               itemB == "get tired" ~ "bio", 
                               itemB == "become hungry" ~ "bio",
                               itemB == "feel scared"~ "bio",
                               itemB == "experience pain"~ "bio",
                               itemB == "get sick"~ "bio")) 

df_combined <- df_freesort %>%
  # left_join(df_causal, by = c("subject_id", "itemA", "itemB")) # %>% 
  left_join(df_causal, by = c("subject_id", "itemA", "itemB", "domain_itemA", "domain_itemB")) %>%
  mutate(domain_itemA = factor(domain_itemA, levels = domain_order),
         domain_itemB = factor(domain_itemB, levels = domain_order)) %>% 
  relocate(freesort_distance, .before = "causal_distance") %>%
  relocate(trial_type_order, .after = "domain_itemB")

paged_table(df_combined)

write.csv(df_combined, data_processed_output_path, row.names = F)

```

THE END

```{r}

```

