---
title: "study 2"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-1-10"
author: Joseph Outa
---

Background:
This is the analysis script for Study 2 of the project "Adults hold a causal explanatory framework that connects understanding of other people’s minds, actions and bodies" by Joseph Outa and Shari Liu. 

Study 2 had N = 100, with random assignment to two between-subjects conditions: Intervention and Trait Inference, with 15 trials per condition. 

Study conducted online with adults on Cloud Research Connect. Study demo: https://liulaboratory-experiments.github.io/mbc/study2

The question: Do subjects flexibly use their latent-cause and direct-cause representations depending on the task? Are subjects in the Intervention condition more likely to select the causal item (based on causal ratings of study 1), and are subjects in the Inference condition more likely to select the similar item (based on results of sorting task of study 1)?

Script description:
This script takes as input `study2_data_raw.csv` and `data_freesort_minus_causals.csv`, and plots Supplementary Table 1 in the SI materials, Figure 2 from the main manuscript, and runs statistical models to predict variability in responses from causal and freesort distances.

# Setup

## Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse, 
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               gt,
               webshot2,
               ragg,
               knitr,
               performance)
sessionInfo()

```

## Set variables

```{r, warnings = FALSE}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

# paths
## script inputs
base_path <- here("code", "pilot")
data_path <- paste0(base_path, "/data/data-study2/study2_data_raw.csv")
snapshots_input_path <- paste0(base_path,
                               "/analysis/study1-measure/snapshots_study1_pilot_analysis")
freesort_and_causal_distances_df_path <- paste0(snapshots_input_path,
                                                "/short_list_domain_constraints.csv")

```

## Read data

```{r}
d <- read.csv(data_path)

```


## Demographics

```{r}
df_demographics <- d %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("subject_id", "trial_id", 
         "feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Wrangle data frame

```{r}
 subjects_to_exclude <- d %>%
  filter(condition == "attention_check") %>% 
  rowwise() %>% 
  mutate(correct_attn_check = case_when(
    grepl(correct_response_attn, selected_choice) ~ "yes",
    TRUE ~ "no"
  )) %>% 
  filter(correct_attn_check == "no") %>% 
  pull(subject_id) #1 subject: subject 11

dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>% #exclude 1 subject who failed attn check
  filter(condition %in% c("intervention", "similarity")) %>%
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(causal_itemA, selected_choice) ~ "causal",
    grepl(similarity_itemA, selected_choice) ~ "similar",
    TRUE ~ "other"
  )) %>% 
  mutate(condition = case_when(
    condition == "similarity" ~ "inference",
    TRUE ~ condition
  )) %>% 
  ungroup() %>% 
  select(subject_id, condition, itemB, causal_itemA, similarity_itemA, response) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order),
         similarity_itemA = factor(similarity_itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(domain_itemB = case_when(itemB == "hear something" ~ "mind", #labels for first item of pair
                                 itemB == "choose what to do" ~ "mind",
                                 itemB == "remember something" ~ "mind",
                                 itemB == "think about something" ~ "mind",
                                 itemB == "see something" ~ "mind",
                                 itemB == "reach for something" ~ "action",
                                 itemB == "sit down" ~ "action", 
                                 itemB == "jump up and down" ~ "action",
                                 itemB == "kick something" ~ "action",
                                 itemB == "take a walk" ~ "action",
                                 itemB == "get tired" ~ "bio", 
                                 itemB == "become hungry" ~ "bio",
                                 itemB == "feel scared"~ "bio",
                                 itemB == "experience pain"~ "bio",
                                 itemB == "get sick"~ "bio"),
         domain_causalitemA = case_when(causal_itemA == "hear something" ~ "mind", 
                                 causal_itemA == "choose what to do" ~ "mind",
                                 causal_itemA == "remember something" ~ "mind",
                                 causal_itemA == "think about something" ~ "mind",
                                 causal_itemA == "see something" ~ "mind",
                                 causal_itemA == "reach for something" ~ "action",
                                 causal_itemA == "sit down" ~ "action", 
                                 causal_itemA == "jump up and down" ~ "action",
                                 causal_itemA == "kick something" ~ "action",
                                 causal_itemA == "take a walk" ~ "action",
                                 causal_itemA == "get tired" ~ "bio", 
                                 causal_itemA == "become hungry" ~ "bio",
                                 causal_itemA == "feel scared"~ "bio",
                                 causal_itemA == "experience pain"~ "bio",
                                 causal_itemA == "get sick"~ "bio"),
          domain_similarityitemA = case_when(similarity_itemA == "hear something" ~ "mind", 
                                 similarity_itemA == "choose what to do" ~ "mind",
                                 similarity_itemA == "remember something" ~ "mind",
                                 similarity_itemA == "think about something" ~ "mind",
                                 similarity_itemA == "see something" ~ "mind",
                                 similarity_itemA == "reach for something" ~ "action",
                                 similarity_itemA == "sit down" ~ "action", 
                                 similarity_itemA == "jump up and down" ~ "action",
                                 similarity_itemA == "kick something" ~ "action",
                                 similarity_itemA == "take a walk" ~ "action",
                                 similarity_itemA == "get tired" ~ "bio", 
                                 similarity_itemA == "become hungry" ~ "bio",
                                 similarity_itemA == "feel scared"~ "bio",
                                 similarity_itemA == "experience pain"~ "bio",
                                 similarity_itemA == "get sick"~ "bio")) 


```

# Barplot: condition effect

## summarize data

```{r}
dat_summarized <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>% 
  mutate(condition = ifelse(condition == "intervention",
                            "Intervention", "Inference")) %>% 
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(
    count = n(),  
    total = first(total), 
    mean_proportion = count / total, 
    se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
    .groups = "drop")

```

## plot stacked barplot

```{r}
#stacked
fig_result_summary <- ggplot(dat_summarized, aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "#000000")) + 
  geom_errorbar(data = filter(dat_summarized, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  theme_bw() +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  labs(y = "Proportion",
       x = "Condition",
       fill = "Response",
       ) +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),

        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        legend.background = element_rect(fill='transparent', color = NA),
        legend.box.background = element_rect(fill='transparent', color = NA),
        
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm"),
        
        plot.title = element_text(hjust = 0.5, size = 25)
        ) 


fig_result_summary

fig_result_summary <- ggsave("figures/intervention-inference.png", width = 6, height = 5, 
                             plot = fig_result_summary, bg = "white")

```

# Barplot: item level, stacked

## summarize df

```{r, fig.width = 12}
#this is what it was before I decided to remove all NAs
dat_summarized_by_item <- dat %>%
  mutate(response = fct_relevel(response, c("similar", "causal"))) %>%
  group_by(condition, itemB) %>%
  mutate(total = n()) %>%  #get total responses per condition
  # tidyr::complete(response, nesting(condition, itemB), fill = list(count = 0)) %>%
  group_by(condition, itemB, response) %>%
  mutate(
    count = n(),  #count responses for each response type
    total = first(total),  #total responses for the condition
    mean_proportion = count / total,  #prop response within condition
    se = sqrt(mean_proportion * (1 - mean_proportion) / total)) %>%
  distinct(condition, itemB, .keep_all = TRUE) %>%
  select(-subject_id) %>%
  ungroup()


```

## figure for paper

Includes item triads in paper

```{r, fig.width = 12, fig.height = 12}
d_distances <- read_csv(freesort_and_causal_distances_df_path)

mean_diff <- dat_summarized_by_item %>%
  filter(response == "causal") %>%
  mutate(condition = tolower(condition)) %>%
  select(itemB, condition, mean_proportion) %>%
  tidyr::pivot_wider(names_from = condition, values_from = mean_proportion) %>%
  mutate(inference = ifelse(is.na(inference), 0, inference)) %>% 
  mutate(meanInterv_minus_meanInf = round(intervention - inference, 2)) %>%
  select(itemB, meanInterv_minus_meanInf) %>% 
  mutate()

dat_labels <- dat_summarized_by_item %>% 
  distinct(itemB, causal_itemA, similarity_itemA) %>% 
  rename("similar_itemA" = similarity_itemA) %>% 
  left_join(d_distances %>% #join distances
              mutate("itemB" = target_item,
                     "causal_itemA" = causal_choice,
                     "similar_itemA" = similar_choice),
            by = c("itemB", "causal_itemA", "similar_itemA")) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
# mutate(facet_label = paste0(
#   itemB, "\n",
#   "", causal_itemA, "\n",  # black square
#   "", similarity_itemA    # white square (or use light gray block)
# ))
  distinct(itemB, causal_itemA, similar_itemA, 
           causal_distance_causal_choice,
           freesort_distance_causal_choice,
           causal_distance_similar_choice,
           freesort_distance_similar_choice,
           freesort_minus_causal_distance_causal,
           freesort_minus_causal_distance_similar) %>% 
  mutate(freesort_minus_causal_distance_similar = round(freesort_minus_causal_distance_similar, 2),
         freesort_minus_causal_distance_causal = round(freesort_minus_causal_distance_causal, 2),
         cds_minus_cdc = causal_distance_similar_choice - causal_distance_causal_choice,
         fdc_minus_fds = freesort_distance_causal_choice - freesort_distance_similar_choice,
         fdmcdc_minus_fdmcds = freesort_minus_causal_distance_causal - freesort_minus_causal_distance_similar) %>% 
  left_join(mean_diff, by = "itemB") %>%
  mutate(facet_label = paste0(itemB, 
                              "\n",
                              "causal: ", causal_itemA, 
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_causal_choice,
                              ",",
                              freesort_distance_causal_choice,
                              ",",
                              freesort_minus_causal_distance_causal,
                              ")",
                              "\n",  # black square
                              "similar: ", similar_itemA, # white square (or use light gray block)
                              "\n",
                              "cd,fd,f-c: (",
                              causal_distance_similar_choice,
                              ",",
                              freesort_distance_similar_choice,
                              ",",
                              freesort_minus_causal_distance_similar,
                              ")",
                              "\n",
                              "cdS - cdC: ",
                              cds_minus_cdc,
                              "\n",
                              "fdC - fdS: ",
                              fdc_minus_fds,
                              "\n",
                              "(f-cC) - (f-cS): ",
                              fdmcdc_minus_fdmcds,
                              "\n",
                              "meanInterv(C) - meanInf(C): ",
                              meanInterv_minus_meanInf
                              ))


#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  arrange(itemB) %>%
  pull(facet_label)

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))


dat_summarized_by_item_levels <- dat_summarized_by_item %>%
  left_join(dat_labels %>% select(itemB, facet_label), by = "itemB") %>% 
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_alt2 <- dat_summarized_by_item_levels %>% 
  ggplot(aes(x =condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity") +
  geom_bar(stat = "identity", colour = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_errorbar(data = filter(dat_summarized_by_item_levels, response == "causal"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  scale_fill_manual(values = c("grey80", "#000000")) +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 15),
        # legend.position = "none",
        strip.text = element_text(size = 15)) +
  labs(y = "proportion",
       title = "pilot") +
  facet_wrap(~facet_label, nrow = 3) 

p_alt2

ggsave(
  filename = "figures/p_study2_item-level_stacked.pdf",
  plot = p_alt2,          
  device = "pdf",           
  width = 20,               
  height = 15,             
  units = "in")

```

## Plotting effect sizes (10/2/2025)

```{r}
dat_summarized_by_item_levels

emp_effectsizes <- dat_summarized_by_item %>% 
  complete(condition, itemB, response, fill = list(total = 51, count = 0, mean_proportion = 0, se = 0)) %>% 
  filter(response == "causal") %>%
  select(condition, itemB, response, mean_proportion, se, total) %>% 
  pivot_wider(names_from = "condition",
              values_from = c(mean_proportion, se, total)) %>% 
  mutate(sd_intervention = se_intervention * sqrt(total_intervention),
         sd_inference = se_inference * sqrt(total_inference),
         sd_pooled = sqrt(((total_intervention - 1) * sd_intervention^2 + (total_inference - 1) * sd_inference^2) / (total_intervention + total_inference - 2)),
         smd = (mean_proportion_intervention - mean_proportion_inference) / sd_pooled ) 


mean_smd <- emp_effectsizes %>% 
  summarize(mean_emp_smd = mean(smd))

emp_effectsizes_plot <- emp_effectsizes %>% 
  ggplot(aes(x = itemB, y = smd)) +
  geom_point() +
  geom_hline(data = mean_smd, 
             aes(yintercept = mean_emp_smd),
             linetype = "dashed",
             color = "red") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = .5))

emp_effectsizes_plot

ggsave("empirical_effectsizes.png", emp_effectsizes_plot)

```

## Correlating emp and theor (10/2/25)

```{r}
theor_effectsizes <- read_csv(paste0(base_path, "/analysis/study1-measure/theoretical_effectsizes.csv")) %>% 
  rename("smd")

combined_es <- emp_effectsizes %>% 
  rename("target_item" = itemB,
         "es_empirical" = smd) %>% 
  left_join(theor_effectsizes %>% 
              select(target_item, es_theoretical),
            by = "target_item") 

combined_es %>% 
  ggplot(aes(x = es_empirical, y = es_theoretical)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw()

cor(combined_es$es_empirical, combined_es$es_theoretical)
summary(lm(es_empirical ~ es_theoretical, data = combined_es))

```




# Modelling

## prepare data frames

```{r}
d_model <- dat %>% 
  mutate(response = as.factor(response)) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  mutate(responses = ifelse(response == "causal", 1, 0)) %>% 
  mutate(condition = as.factor(condition)) %>%
  unite(col = "trial_ID", c(itemB, similarity_itemA, causal_itemA), sep = "_", remove = FALSE)
  
d_freesort_and_causal_distances <- read_csv(freesort_and_causal_distances_df_path) %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(itemA = factor(itemA, levels = desired_order)) 

intervention_condition <- d_model %>% 
  # select(-similarity_itemA) %>% # why - let's study both?
    filter(condition == "intervention") %>%
    left_join(d_freesort_and_causal_distances %>% 
                select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
                rename("causal_itemA" = itemA,
                       "causal_itemA_causal_distance" = mean_causal_distance,
                       "causal_itemA_freesort_distance" = mean_freesort_distance,
                       "causal_itemA_freesort_minus_causal" = freesort_minus_causal),
              by = c("itemB", "causal_itemA")) %>%
    left_join(d_freesort_and_causal_distances %>% 
                select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
                rename("similarity_itemA" = itemA,
                       "similarity_itemA_causal_distance" = mean_causal_distance,
                       "similarity_itemA_freesort_distance" = mean_freesort_distance, 
                       "similar_itemA_freesort_minus_causal" = freesort_minus_causal),
              by = c("itemB", "similarity_itemA"))

  
trait_inference_condition <- d_model %>% 
  # select(-causal_itemA) %>% 
  filter(condition == "inference") %>% 
    left_join(d_freesort_and_causal_distances %>% 
                select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
                rename("causal_itemA" = itemA,
                       "causal_itemA_causal_distance" = mean_causal_distance,
                       "causal_itemA_freesort_distance" = mean_freesort_distance,
                       "causal_itemA_freesort_minus_causal" = freesort_minus_causal),
              by = c("itemB", "causal_itemA")) %>%
    left_join(d_freesort_and_causal_distances %>% 
                select(itemA, itemB, mean_causal_distance, mean_freesort_distance, freesort_minus_causal) %>% 
                rename("similarity_itemA" = itemA,
                       "similarity_itemA_causal_distance" = mean_causal_distance,
                       "similarity_itemA_freesort_distance" = mean_freesort_distance, 
                       "similar_itemA_freesort_minus_causal" = freesort_minus_causal),
              by = c("itemB", "similarity_itemA"))

```

## Effect of condition

### run model

```{r}
#model
model_effect_of_condition <- glmer(responses ~ condition + (1|subject_id), data = d_model, family = binomial(link = 'logit'))
summary(model_effect_of_condition)
plot(allEffects(model_effect_of_condition))
#check_model(model_effect_of_condition) #binned residual issue?

#probabilities
effects_data <- allEffects(model_effect_of_condition)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

### predictions

model predictions for the probability of specific items, for writeup

(NB 10/2/2025 check if these are just two attempts?)
```{r}
#see something
model_with_itemB <- glmer(responses ~ condition * (itemB == "see something") + (1|subject_id), 
                          data = d_model, family = binomial(link = 'logit'))
summary(model_with_itemB)

new_data <- data.frame(
  condition = c("inference", "intervention"),
  itemB = "see something",
  subject_id = d_model$subject_id[1]  
)

new_data$predicted_response <- predict(model_with_itemB, newdata = new_data, type = "response")
new_data


#think about something
model_with_itemB <- glmer(responses ~ condition * (itemB == "think about something") + (1|subject_id), 
                          data = d_model, family = binomial(link = 'logit'))
summary(model_with_itemB)

new_data <- data.frame(
  condition = c("inference", "intervention"),
  itemB = "think about something",
  subject_id = d_model$subject_id[1] 
)

new_data$predicted_response <- predict(model_with_itemB, newdata = new_data, type = "response")
new_data

```


## Effect of distances: trait inference condition

### run model

```{r}
# Modelling predictors jointly
#model_effect_of_distances_inference <- glmer(responses ~ causal_itemA_freesort_minus_causal + similar_itemA_freesort_minus_causal + (1|subject_id), data = trait_inference_condition, family = binomial(link = "logit")) # TODO figure out failure to converge here --> removed subj_id random effect

model_effect_of_distances_inference <- glm(responses ~ causal_itemA_freesort_minus_causal + similar_itemA_freesort_minus_causal, data = trait_inference_condition, family = binomial(link = "logit"))

summary(model_effect_of_distances_inference)
plot(allEffects(model_effect_of_distances_inference))
#check_model(model_effect_of_distances_inference)

```

### figure for paper

```{r}
effects_data <- allEffects(model_effect_of_distances_inference)

causal_effect <- as.data.frame(effects_data$`causal_itemA_freesort_minus_causal`)
similar_effect <- as.data.frame(effects_data$`similar_itemA_freesort_minus_causal`)

causal_effect$Predictor <- "Causal Item"
similar_effect$Predictor <- "Similar Item"

colnames(causal_effect)[1] <- "PredictorValue"
colnames(similar_effect)[1] <- "PredictorValue"

combined_effects <- rbind(causal_effect, similar_effect)


base_plot <- ggplot(combined_effects, aes(x = PredictorValue, y = fit, color = Predictor)) +
  geom_line(size = 1.2) +  # Adjust line size for emphasis
  geom_hline(yintercept = .5, linetype = "dashed") +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Predictor), alpha = 0.2) +
  scale_color_manual(
    values = c("Causal Item" = "black", "Similar Item" = "grey")
  ) +
  scale_fill_manual(
    values = c("Causal Item" = "black", "Similar Item" = "grey")
  ) +
  labs(
    title = "Probability of Making A Causal Choice in Trait Inference Condition",
    x = "Distance between Choice and Target Item",
    y = "Probability",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  theme_cowplot() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 8),  
    axis.text.x = element_text(size = 20),  
    axis.text.y = element_text(size = 20),  
    axis.title.y = element_text(size = 20),  
    axis.title.x = element_text(size = 15),  
    legend.title = element_text(size = 20), 
    legend.text = element_text(size = 20),
    legend.position = c(0.5, 0.7) ,  #move legend inside the plot
    legend.background = element_rect(fill = "white", color = "black")  #border around the legend
  )

base_plot

```

## Effect of distances: intervention condition

### run model

```{r}
#Modelling both predictors 
model_effect_of_distances_intervention <- glmer(responses ~ causal_itemA_freesort_minus_causal + similar_itemA_freesort_minus_causal + (1|subject_id), data = intervention_condition, family = binomial(link = "logit"))
summary(model_effect_of_distances_intervention)
plot(allEffects(model_effect_of_distances_intervention))
#check_model(model_effect_of_distances_intervention )

fixed_effects <- fixef(model_effect_of_distances_intervention) #log odds
odds_ratios <- exp(fixed_effects)  #convert log-odds to odds ratios
probabilities <- 1 / (1 + exp(-fixed_effects)) #convert log odds to probability

#nb: fixed effects are intercept and slope. slope is change log odds of outcome for a unit increase in predictor
```

### figure for paper

```{r}
effects_data <- allEffects(model_effect_of_distances_intervention)

causal_effect <- as.data.frame(effects_data$`causal_itemA_freesort_minus_causal`)
similar_effect <- as.data.frame(effects_data$`similar_itemA_freesort_minus_causal`)

causal_effect$Predictor <- "Causal Item"
similar_effect$Predictor <- "Similar Item"

colnames(causal_effect)[1] <- "PredictorValue"
colnames(similar_effect)[1] <- "PredictorValue"

combined_effects <- rbind(causal_effect, similar_effect)

base_plot <- ggplot(combined_effects, aes(x = PredictorValue, y = fit, color = Predictor)) +
  geom_line(size = 1.2) +  # Adjust line size for emphasis
  geom_hline(yintercept = .5, linetype = "dashed") +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = Predictor), alpha = 0.2) +
  scale_color_manual(
    values = c("Causal Item" = "black", "Similar Item" = "grey")
  ) +
  scale_fill_manual(
    values = c("Causal Item" = "black", "Similar Item" = "grey")
  ) +
  labs(
    title = "Probability of Making A Causal Choice in Intervention Condition",
    x = "Distance between Choice and Target Item",
    y = "Probability",
    color = "Choice Item",
    fill = "Choice Item"
  ) +
  theme_cowplot() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 8),  
    axis.text.x = element_text(size = 20),  
    axis.text.y = element_text(size = 20),  
    axis.title.y = element_text(size = 20),  
    axis.title.x = element_text(size = 15),  
    legend.title = element_text(size = 20), 
    legend.text = element_text(size = 20),
    legend.position = c(0.5, 0.7) ,  #move legend inside the plot
    legend.background = element_rect(fill = "white", color = "black")  #border around the legend

    #plot.margin = margin(20, 20, 50, 20)
  )
base_plot

```














