---
title: "Causal Triads and Biological Reasoning"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-12-18"
author: Joseph Outa
---

# ReadMe

- Analysis script for experiment 6: Biological Reasoning vs Causal Triads study.  
- Date run: 12/18/25
- Sample: 105 before exclusions     
- Conditions: 2 between-subjects conditions
- Method: A gene makes a creature x, [blank], and z. Fill the blank (Biological Reasoning Condition). Someone x, which made them [blank], which made them z. Fill the blank (Causal Triads Condition). Response is a binary choice between CC (Causal Chain) item and CO (Causal Origins) item.   

# Setup

## Load packages

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               effectsize,
               corrplot,
               magick,
               pdftools,
               simr
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
theme_set(theme_bw())
sessionInfo()

```

## Global variables

```{r}
base_path <- here("code")

study_path <- paste0(base_path, "/analysis/6_biological_reasoning_v_causal_triads")

data_path <- paste0(base_path, "/data/6_biological_reasoning_v_causal_triads/JO-mbc-main-cc-v2-105N")

item_selection_base_path <- paste0(base_path,
                                        "/analysis/1.5_item_selection")

mean_joint_distances_path <- paste0(item_selection_base_path, 
                                    "/snapshots_item_selection", 
                                    "/mean_joint_distances_experiment_6.csv")

item_level_distances_path <- paste0(item_selection_base_path,
                         "/snapshots_experiment1_combined_analysis",
                         "/freesort_minus_causals.csv") #for item_level plot

desired_order <- c("see something", "choose what to do", "remember something", 
                   "sit down", "jump up and down", "take a walk", 
                   "get tired", "become hungry", "get sick")

```

# Confirmatory Analysis - Prep

## Read data

```{r, warnings = FALSE}
file_paths <- list.files(path = data_path, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    rename(
      middle_CC_item = middle_causal,
      middle_CO_item = middle_similar,
      selected_item = selected_choice
    ) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## Wrangle data

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  mutate(attn_correct = correct_response_attn == selected_item) %>% 
  filter(attn_correct == FALSE) %>%
  pull(subject_id) %>% 
  unique()

dat <- d %>%
  filter(condition %in% c("causal_chain", "common_cause")) %>% 
    mutate(condition = case_when(
      condition == "causal_chain" ~ "causal_triads",
      condition == "common_cause" ~ "biological_reasoning"
    )) %>%
  mutate(condition = as.factor(condition)) %>% 
  mutate(response = ifelse(response == "similar", "CO", "CC")) %>% 
  mutate(subject_id = factor(subject_id)) %>% 
  rowwise() %>%
  mutate(response = case_when(
    grepl(middle_CC_item, selected_item) ~ "CC",
    grepl(middle_CO_item, selected_item) ~ "CO",
    TRUE ~ "other"
  )) %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  select(subject_id, condition, first_item, middle_CC_item, 
         middle_CO_item, third_item, response) %>% 
  mutate(domain_first_item = case_when(first_item == "hear something" ~ "mind", 
                                 first_item == "choose what to do" ~ "mind",
                                 first_item == "remember something" ~ "mind",
                                 first_item == "think about something" ~ "mind",
                                 first_item == "see something" ~ "mind",
                                 first_item == "reach for something" ~ "action",
                                 first_item == "sit down" ~ "action", 
                                 first_item == "jump up and down" ~ "action",
                                 first_item == "kick something" ~ "action",
                                 first_item == "take a walk" ~ "action",
                                 first_item == "get tired" ~ "body", 
                                 first_item == "become hungry" ~ "body",
                                 first_item == "feel scared"~ "body",
                                 first_item == "experience pain"~ "body",
                                 first_item == "get sick"~ "body"),
         domain_third_item = case_when(third_item == "hear something" ~ "mind", 
                                 third_item == "choose what to do" ~ "mind",
                                 third_item == "remember something" ~ "mind",
                                 third_item == "think about something" ~ "mind",
                                 third_item == "see something" ~ "mind",
                                 third_item == "reach for something" ~ "action",
                                 third_item == "sit down" ~ "action", 
                                 third_item == "jump up and down" ~ "action",
                                 third_item == "kick something" ~ "action",
                                 third_item == "take a walk" ~ "action",
                                 third_item == "get tired" ~ "body", 
                                 third_item == "become hungry" ~ "body",
                                 third_item == "feel scared"~ "body",
                                 third_item == "experience pain"~ "body",
                                 third_item == "get sick"~ "body"),
         domain_middle_CC_item = case_when(middle_CC_item == "hear something" ~ "mind", 
                                 middle_CC_item == "choose what to do" ~ "mind",
                                 middle_CC_item == "remember something" ~ "mind",
                                 middle_CC_item == "think about something" ~ "mind",
                                 middle_CC_item == "see something" ~ "mind",
                                 middle_CC_item == "reach for something" ~ "action",
                                 middle_CC_item == "sit down" ~ "action", 
                                 middle_CC_item == "jump up and down" ~ "action",
                                 middle_CC_item == "kick something" ~ "action",
                                 middle_CC_item == "take a walk" ~ "action",
                                 middle_CC_item == "get tired" ~ "body", 
                                 middle_CC_item == "become hungry" ~ "body",
                                 middle_CC_item == "feel scared"~ "body",
                                 middle_CC_item == "experience pain"~ "body",
                                 middle_CC_item == "get sick" ~ "body"),
          domain_middle_CO_item = case_when(middle_CO_item == "hear something" ~ "mind", 
                                 middle_CO_item == "choose what to do" ~ "mind",
                                 middle_CO_item == "remember something" ~ "mind",
                                 middle_CO_item == "think about something" ~ "mind",
                                 middle_CO_item == "see something" ~ "mind",
                                 middle_CO_item == "reach for something" ~ "action",
                                 middle_CO_item == "sit down" ~ "action", 
                                 middle_CO_item == "jump up and down" ~ "action",
                                 middle_CO_item == "kick something" ~ "action",
                                 middle_CO_item == "take a walk" ~ "action",
                                 middle_CO_item == "get tired" ~ "body", 
                                 middle_CO_item == "become hungry" ~ "body",
                                 middle_CO_item == "feel scared"~ "body",
                                 middle_CO_item == "experience pain"~ "body",
                                 middle_CO_item == "get sick"~ "body")) %>% 
  ungroup() %>% 
  mutate(response = as.factor(response)) 

rmarkdown::paged_table(dat)

```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_type == "survey-html-form") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 
cat("\n") 

paste0("pre-exclusion N: ", d %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
paste0("post-exclusion N: ", dat %>% distinct(subject_id) %>% summarize(n = n()) %>% pull(n))
cat("\n") 

paste0(
  "Post-exclusion condition count: ",
  dat %>% 
    distinct(subject_id, .keep_all = TRUE) %>% 
    count(condition) %>% 
    mutate(label = paste0(condition, " = ", n)) %>% 
    pull(label) %>% 
    paste(collapse = ", ")
)
cat("\n") 

paste0("Age summary: ")
summary(df_demographics$age)
cat("\n") 

c("Gender: " =  "Count", table(df_demographics$gender))
cat("\n")
c("Ethnicity: " =  "Count", table(df_demographics$ethnicity))
cat("\n")
c("Race: " =  "Count", table(df_demographics$race))

```

## Summarize data 

```{r}
# Condition-level, with cis
dat_summarized_conditions <- dat %>%
  group_by(condition) %>%
  mutate(total = n()) %>% 
  group_by(condition, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = count / total, 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
            .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  select(-c(count, total))

rmarkdown::paged_table(dat_summarized_conditions)

# Trial-level summary
dat_summarized_trials <- dat %>% #not using but good for proofing
  unite("joined", c(first_item, middle_CC_item, 
                    middle_CO_item, third_item), sep = "_") %>% 
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = count / total, 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),  
            .groups = "drop") %>% 
  complete(condition, joined, response,
           fill = list(count = 0, mean_proportion = 0, se = 0)) %>%
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) 

rmarkdown::paged_table(dat_summarized_trials)

```

# Confirmatory Analysis - Figures

## Figure with slope 

Black and white

```{r, fig.width = 3, fig.height = 5}
fig_slope <- dat_summarized_conditions %>%
  mutate(response = fct_relevel(response, "CC", "CO")) %>% 
  mutate(condition = fct_relevel(condition, "biological_reasoning", "causal_triads")) %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_col(colour = "black") +
  geom_errorbar(data = filter(dat_summarized_conditions, response == "CO"), 
                  aes(ymax = ci_high,
                      ymin = ci_low,
                      width = 0.3)) +
  geom_point(data = dplyr::filter(dat_summarized_trials, response == "CO"),
    aes(group = joined,
        fill = response),
             alpha = 0.8, 
             size = 5,
             shape = 21,
             color = "black") +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_line(
    data = dplyr::filter(dat_summarized_trials, response == "CO"),
    aes(group = joined),
    alpha = 0.4, color = "black") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_x_discrete(labels = c("causal_triads" = "Causal\nTriads", 
                              "biological_reasoning" = "Biological\nReasoning")) +
  theme_cowplot() +
  labs(y = "Proportion (CC)", 
       x = "Condition", 
       fill = "Response") +
  ylim(0, 1) +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 25),
    legend.position = "top",
    legend.title = element_text(size = 25),
    legend.text = element_text(size = 25),
    panel.background = element_rect(fill='transparent', color=NA),
    plot.background = element_rect(fill='transparent', color=NA))

fig_slope

fig_slope <- ggsave("figures/biological_causal_triads_slope_black_and_white.png", 
                    width = 3.5, height = 6, plot = fig_slope, bg = "white")

```

## Item-level with distances

```{r, fig.height = 12, fig.width = 12}
preceding_distances_path <- item_level_distances_path

d_preceding_distances <- read_csv(preceding_distances_path) %>%
  mutate(mean_causal_pairs_distance = round(mean_causal_pairs_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2))

dat_summarized_itemlevel <- dat %>%
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  group_by(condition, first_third) %>%
  mutate(total = n()) %>% 
  group_by(condition, first_third, response) %>%
  summarize(count = n(),  
            total = first(total), 
            mean_proportion = round(count / total, 2), 
            se = sqrt(mean_proportion * (1 - mean_proportion) / total),
            .groups = "drop")

dat_labels <- dat %>% 
  unite("first_third", c(first_item, third_item), sep = "_") %>% 
  distinct(first_third, middle_CC_item, middle_CO_item) %>% 
  separate(first_third, c("first_item", "third_item"),
           sep = "_", remove = FALSE) %>%
  left_join(d_preceding_distances %>% #join causal distances
              rename("third_item" = itemB,
                     "middle_CC_item" = itemA,
                     "causal_pairs_distance_CC_third" = mean_causal_pairs_distance,
                     "freesort_distance_CC_third" = mean_freesort_distance,
                     "freesort_minus_causal_CC_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_CC_item,
                     causal_pairs_distance_CC_third,
                     freesort_distance_CC_third,
                     freesort_minus_causal_CC_third), 
            by = c("third_item", "middle_CC_item")) %>% 
  left_join(d_preceding_distances %>% #join similar distances
              rename("third_item" = itemB,
                     "middle_CO_item" = itemA,
                     "causal_pairs_distance_CO_third" = mean_causal_pairs_distance,
                     "freesort_distance_CO_third" = mean_freesort_distance,
                     "freesort_minus_causal_CO_third" = freesort_minus_causal) %>% 
              select(third_item, 
                     middle_CO_item,
                     causal_pairs_distance_CO_third,
                     freesort_distance_CO_third,
                     freesort_minus_causal_CO_third), 
            by = c("third_item", "middle_CO_item")) %>% 
  
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_CC_item" = itemB,
                     "causal_pairs_distance_CC_first" = mean_causal_pairs_distance,
                     "freesort_distance_CC_first" = mean_freesort_distance,
                     "freesort_minus_causal_CC_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_CC_item,
                     causal_pairs_distance_CC_first,
                     freesort_distance_CC_first,
                     freesort_minus_causal_CC_first), 
            by = c("first_item", "middle_CC_item")) %>% 
  left_join(d_preceding_distances %>% 
              rename("first_item" = itemA,
                     "middle_CO_item" = itemB,
                     "causal_pairs_distance_CO_first" = mean_causal_pairs_distance,
                     "freesort_distance_CO_first" = mean_freesort_distance,
                     "freesort_minus_causal_CO_first" = freesort_minus_causal) %>% 
              select(first_item, 
                     middle_CO_item,
                     causal_pairs_distance_CO_first,
                     freesort_distance_CO_first,
                     freesort_minus_causal_CO_first), 
            by = c("first_item", "middle_CO_item")) %>% 

  mutate(facet_label = paste0("first item: ", first_item,
                              "\n",
                              "third item: ", third_item,
                              "\n",
                              "CC: ", middle_CC_item, 
                              "\n",  
                              "CO: ", middle_CO_item,
                              "\n",
                              "\n",
                              "1st item-cdS,fdS,cdC,fdC: ", "(", 
                              causal_pairs_distance_CO_first, ",",
                              freesort_distance_CO_first, ",",
                              causal_pairs_distance_CC_first, ",",
                              freesort_distance_CC_first, ")", "\n", 
                              "3rd item-cdS, fdS, cdC, fdC: ", "(", 
                              causal_pairs_distance_CO_third, ",",
                              freesort_distance_CO_third, ",",
                              causal_pairs_distance_CC_third, ",",
                              freesort_distance_CC_third, ")"
                              )) 

#sort by itemB and extract the ordered facet labels
ordered_facet_labels <- dat_labels %>%
  mutate(first_item = factor(first_item, levels = desired_order)) %>% 
  arrange(first_item) %>% 
  pull(facet_label)

#join labels + order AFTER labels exist
dat_summarized_itemlevel <- dat_summarized_itemlevel %>%
  left_join(dat_labels %>% select(first_third, facet_label), by = "first_third") %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

#set facet_label as a factor with that order
dat_labels <- dat_labels %>%
  mutate(facet_label = factor(facet_label, levels = ordered_facet_labels))

p_itemlvl <- dat_summarized_itemlevel %>%
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  ggplot(aes(x = condition, y = mean_proportion, fill = response)) +
  geom_bar(stat = "identity", colour = "black") +
  scale_fill_manual(values = c("grey80", "white")) + #or whatever you'd like!
  geom_errorbar(data = filter(dat_summarized_itemlevel, response == "CC"), aes(ymax = mean_proportion + se,
                                                                         ymin = mean_proportion - se),
                stat = "identity", position = "identity", width = 0.3) +
  geom_hline(yintercept = .5, linetype = "dashed") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(size = 25, hjust = 0.5),
        # legend.position = "none",
        strip.text = element_text(size = 18)) +
  labs(y = "Proportion (CC)",
       title = "Causal Triads") +
  facet_wrap(~facet_label, nrow = 3)

p_itemlvl

# ggsave(
#   filename = paste0(study_path, "/figures/p_causal_chain_item-level-distances.pdf"),
#   plot = p_itemlvl,
#   device = "pdf",
#   width = 22,
#   bg = "white",
#   height = 15,
#   units = "in")

```

# Confirmatory Analysis - Analysis

## Logistic regression

```{r}
##factor outcome variables
d_model <- dat %>%
  mutate(subject_id = factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("CC", "CO"))) %>% 
  mutate(condition = factor(condition, levels = c("causal_triads", "biological_reasoning")))

##run the model
model_condition_difference <- glmer(response ~ condition + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_model)

summary(model_condition_difference)

std_parameters <- standardize_parameters(model_condition_difference, 
                                         ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Get specific probabilities

```{r}
effects_data <- allEffects(model_condition_difference)
effects_df <- as.data.frame(effects_data$condition)
effects_df

```

## Causal Triads only

```{r}
d_causal_triad <- d_model %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "causal_triads") 

model_effect_of_causal_triad <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_causal_triad)

summary(model_effect_of_causal_triad)

paste0("probability: ", plogis(fixef(model_effect_of_causal_triad)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_causal_triad)[1]))

```

## Biological Reasoning only

```{r}
d_biological <- d_model %>% 
  mutate(condition = as.character(condition)) %>% 
  filter(condition == "biological_reasoning") 

model_effect_of_biological <- glmer(response ~ 1 + (1 | subject_id), 
      family = binomial(link = 'logit'), 
      data = d_biological)
summary(model_effect_of_biological)

paste0("probability: ", plogis(fixef(model_effect_of_biological)[1]))
paste0("odds ratio: ", exp(fixef(model_effect_of_biological)[1]))

```

# Exploratory Analysis - Prep

## Append distances

```{r}
distances <- read_csv(mean_joint_distances_path) %>%
  select(-1) 

colnames(distances)
```

## Merge and save distances

```{r}
d_biological_causal_triads_distances <- dat %>% 
  left_join(distances %>% 
              rename("middle_CC_item" = middle_item,
                     "rank_CC" = rank,
                     "freesort_minus_causal_pairs_distance_CC" = freesort_minus_causal_pairs_distance),
              by = c("first_item", "third_item", "middle_CC_item")) %>% 
  left_join(distances %>% 
              rename("middle_CO_item" = middle_item,
                    "freesort_minus_causal_pairs_distance_CO" = freesort_minus_causal_pairs_distance,
                    "rank_CO" = rank), 
              by = c("first_item", "third_item", "middle_CO_item")) %>% 
  mutate(freesort_minus_causal_pairs_distance_CC = 
           round(freesort_minus_causal_pairs_distance_CC, 2),
         freesort_minus_causal_pairs_distance_CO = 
           round(freesort_minus_causal_pairs_distance_CO, 2) 
         ) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_pairs_distance_CC - freesort_minus_causal_pairs_distance_CO) 

rmarkdown::paged_table(d_biological_causal_triads_distances)

write_csv(d_biological_causal_triads_distances,
          "snapshots_experiment_6_analysis/dat_biological_causal_triad_distances.csv")

```

## Read back in distances

```{r}
analysis_path <- here("code", "analysis")

d_biological_causal_triads_distances <- read_csv(paste0(analysis_path,
                "/6_biological_reasoning_v_causal_triads",
                "/snapshots_experiment_6_analysis",
                "/dat_biological_causal_triad_distances.csv"))

```

# Exploratory Analysis - Figures

## Causal Triads condition

```{r}
short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

#first summarize
d_biological_causal_triads_distances_summarized <- d_biological_causal_triads_distances %>% #rename all these to summarized
  unite("joined", c(first_item, middle_CC_item, middle_CO_item, third_item), sep = "_") %>%
  group_by(condition, joined) %>%
  mutate(total = n()) %>% 
  group_by(condition, joined, response, freesort_minus_causal_pairs_distance_CC,
           freesort_minus_causal_pairs_distance_CO) %>%
  summarize(count = n(),  
         total = first(total), 
         mean_proportion = count / total, 
         se = sqrt(mean_proportion * (1 - mean_proportion) / total), 
         .groups = "drop") %>% 
  mutate(ci_low = pmax(0, mean_proportion - 1.96 * se),
         ci_high = pmin(1, mean_proportion + 1.96 * se)) %>% 
  mutate(joint_distance_difference = freesort_minus_causal_pairs_distance_CC - freesort_minus_causal_pairs_distance_CO) %>% 
  arrange(mean_proportion) %>% 
  relocate(mean_proportion, .after = joined) 

d_causal_triads_distances_summarized <- d_biological_causal_triads_distances_summarized %>% 
  filter(condition == "causal_triads") %>% 
  # filter(response == "CO")  %>% 
  filter(response == "CC")  %>% 
  separate(joined, into = c("first_item", "middle_CC_item", "middle_CO_item", "third_item"),
         sep = "_") %>%
  mutate(joined = paste0("first: ", first_item, "\n", "CC: ", middle_CC_item, "\n", "CO: ", middle_CO_item, "third: ", third_item, "\n"))  %>% 
  mutate(
    first_item         = recode(first_item, !!!short_names),
    third_item         = recode(third_item, !!!short_names),
    middle_CC_item   = recode(middle_CC_item, !!!short_names),
    middle_CO_item  = recode(middle_CO_item, !!!short_names)) %>%
  mutate(labels = paste0("first: ", first_item, "\n", "CC: ", middle_CC_item, "\n", "CO: ",
                         middle_CO_item, "\n", "third: ", third_item))

fig_causal_triads_distances <- d_causal_triads_distances_summarized %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  scale_x_continuous(breaks = seq(0, 1.1, by = 0.25)) +
  # geom_text(aes(label = labels), size = 3, vjust = 1.3) +
  theme_bw() +
  labs(
      title = "Causal Triads Condition",
       x = "Joint distance difference",
       y = "Proportion (CO)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1.1)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        # plot.title = element_blank(),
        legend.position = "none") 

fig_causal_triads_distances

fig_causal_triads_distances <- ggsave("figures/causal_triads_distances.png", width = 6, height = 4.5, #height was 4
                        plot = fig_causal_triads_distances, bg = "white")

```

## Biological Reasoning condition

```{r}
d_biological_distances_summarized <- d_biological_causal_triads_distances_summarized %>% 
  filter(condition == "biological_reasoning") %>% 
  filter(response == "CC")  %>% 
  separate(joined, into = c("first_item", "middle_CC_item", "middle_CO_item", "third_item"),
         sep = "_") %>%
  mutate(joined = paste0("first: ", first_item, "\n", "CC: ", middle_CC_item, "\n", "CO: ", middle_CO_item, "third: ", third_item, "\n"))  %>% 
  mutate(
    first_item         = recode(first_item, !!!short_names),
    third_item         = recode(third_item, !!!short_names),
    middle_CC_item   = recode(middle_CC_item, !!!short_names),
    middle_CO_item  = recode(middle_CO_item, !!!short_names)) %>%
  mutate(labels = paste0("first: ", first_item, "\n", "CC: ", middle_CC_item, "\n", "CO: ",
                         middle_CO_item, "\n", "third: ", third_item))

fig_biological_distances <- d_biological_distances_summarized %>% 
  ggplot(aes(x = joint_distance_difference, y = mean_proportion)) +
  geom_point(size = 5, alpha = 0.4) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  # geom_text(aes(label = labels), size = 3, vjust = -.2) +
  theme_bw() +
  labs(
      title = "Biological Reasoning Condition",
       x = "Joint distance difference",
       y = "Proportion (CC)") +
  coord_cartesian(ylim = c(0,1), xlim = c(0,1.1)) +
  scale_x_continuous(breaks = seq(0, 1.1, by = 0.25)) +
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        plot.title = element_text(hjust = .5, size = 25),
        legend.position = "none") 

fig_biological_distances

fig_biological_distances <- ggsave("figures/biological_reasoning_distances.png", width = 6, height = 4.5, 
                        plot = fig_biological_distances, bg = "white")

```

# Exploratory Analysis - Analysis

## Prepare for modelling

```{r}
d_biological_causal_triads_distances_model <- d_biological_causal_triads_distances %>%
  mutate(joint_distance_difference = freesort_minus_causal_pairs_distance_CC -
           freesort_minus_causal_pairs_distance_CO) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  mutate(response = fct_relevel(response, c("CO", "CC"))) %>% 
  mutate(condition = factor(condition, levels = c("causal_triads", "biological_reasoning"))) 
```

## Biological Reasoning

```{r}
model_biological_distances <- glmer(response ~ joint_distance_difference + 
                              (1 | subject_id), 
    data = d_biological_causal_triads_distances %>% 
      filter(condition == "biological_reasoning") %>% 
      mutate(response = fct_relevel(response, c("CO", "CC"))),
    family = binomial(link = 'logit'))

summary(model_biological_distances)

std_parameters <- standardize_parameters(model_biological_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```

## Causal Triads

```{r}
model_causal_triads_distances <- glmer(response ~ joint_distance_difference + 
                              (1 | subject_id), 
    data = d_biological_causal_triads_distances %>% 
      filter(condition == "causal_triads") %>% 
      mutate(response = fct_relevel(response, c("CO", "CC"))),
    family = binomial(link = 'logit'))

summary(model_causal_triads_distances)

std_parameters <- standardize_parameters(model_causal_triads_distances, 
                                  ci = 0.95) %>% 
  as.data.frame() %>%
  mutate(OR = exp(Std_Coefficient),
         OR_low = exp(CI_low),
         OR_high = exp(CI_high)) %>% 
  rename("Log_odds" = Std_Coefficient) %>% 
  relocate(c("OR", "OR_low", "OR_high"), .before = "Log_odds")

std_parameters

```



# THE END

```{r}

```




