---
title: "Explanation"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-09-19"
author: "Joseph Outa"

---

# ReadMe

This is the analysis script for the Explanations study.  
N = 104 (before exclusions).  
The independent variable is whether the explanation provided for a target event is a CC or CO item (within-subjects).  
The dependent variable is how satisfactory the explanation is, ranging from not at all (0) to extremely satisfying (100). 

# Setup

## Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(
               lme4, 
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               emmeans,
               gt,
               webshot2,
               knitr,
               performance,
               effectsize,
               simr,
               see,
               conflicted,
               tidyverse)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()


```

## Global variables

```{r}
base_path <- here("code")
snapshots_item_selection_path <- paste0(base_path,
                                        "/analysis/1.5_item_selection/snapshots_experiment1_combined_analysis")
freesort_and_causal_distances_df_path <- paste0(snapshots_item_selection_path,
                                                "/freesort_minus_causals.csv")

short_names <- c(
  "see something" = "see",
  "hear something" = "hear",
  "choose what to do" = "choose",
  "remember something" = "remember",
  "think about something" = "think",
  
  "take a walk" = "walk", 
  "jump up and down" = "jump",
  "reach for something" = "reach",
  "sit down" = "sit",
  "kick something" = "kick",
  
  "get sick" = "sick",
  "feel scared" = "scared",
  "become hungry" = "hungry",
  "experience pain" = "pain",
  "get tired" = "tired")

compact_names <- c(
  "see something" = "see\nsomething",
  "hear something" = "hear\nsomething",
  "choose what to do" = "choose",
  "remember something" = "remember\nsomething",
  "think about something" = "think\nabout\nsomething",
  
  "take a walk" = "take\na walk", 
  "jump up and down" = "jump up\nand down",
  "reach for something" = "reach for\nsomething",
  "sit down" = "sit down",
  "kick something" = "kick\nsomething",
  
  "get sick" = "get sick",
  "feel scared" = "feel\nscared",
  "become hungry" = "become\nhungry",
  "experience pain" = "experience\npain",
  "get tired" = "get tired")

```

# Confirmatory Analysis - Prep

## Read data

```{r}
data_path <- paste0(base_path, "/data/2_explanation/JO-mbc-main-explanation-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    rename(
      CC_item = causal_itemA,
      CO_item = similar_itemA
    ) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

rmarkdown::paged_table(d)
```

## Wrangle data

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  filter(attn_correct == "no") %>% 
  pull(subject_id) %>% 
  unique()

paste("no. of subjects excluded: ", length(subjects_to_exclude))
paste0("subjects excluded:")
paste(subjects_to_exclude, collapse = ", ")

dat <- d %>% 
  filter(condition %in% c("causal", "similar")) %>%
  filter(!subject_id %in% subjects_to_exclude) %>% #exclude 1 subject who failed attn check
  mutate(response = as.numeric(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  select(-condition) %>% 
  select(subject_id, itemB, CC_item, CO_item, response) %>% 
  mutate(CC_item = factor(CC_item, levels = desired_order),
         CO_item = factor(CO_item, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) %>% 
  mutate(item_type = case_when(
        !is.na(CC_item) ~ "CC_item",
        !is.na(CO_item) ~ "CO_item"),
        item = coalesce(as.character(CC_item), as.character(CO_item))) %>% 
  select(-CC_item, -CO_item) %>% 
  pivot_wider(names_from = item_type,
              values_from = c(item, response)) %>% 
  rename("CC_item" = item_CC_item,
         "CO_item" = item_CO_item, 
         "CC_item_explanation" = response_CC_item,
         "CO_item_explanation" = response_CO_item,
         "target" = itemB) 

rmarkdown::paged_table(dat)

```

## Demographics

```{r}
df_demographics <- d %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("subject_id", "trial_id","feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Summary stats

```{r}
# Raw Long form data
dat_long <- dat %>% 
  rename("CC" = CC_item_explanation,
         "CO" = CO_item_explanation) %>% 
  pivot_longer(cols = c(CC, CO), 
               names_to = "explanation_type",
               values_to = "satisfactory") %>% 
  mutate(explanation_type = factor(explanation_type, levels = c("CC", "CO"))) %>% 
  mutate(explanation = case_when(
    explanation_type == "CC" ~ CC_item,
    explanation_type == "CO" ~ CO_item)) %>% 
  select(subject_id, target, explanation, explanation_type, satisfactory) %>% 
  arrange(subject_id, target)

rmarkdown::paged_table(dat_long)

# Trial-level summary
dat_trials_summarized <- dat_long %>%
  group_by(target, explanation, explanation_type) %>%
  summarise(mean_satisfactory = mean(satisfactory, na.rm = TRUE),
            se_satisfactory = sd(satisfactory, na.rm = TRUE) / sqrt(n_distinct(subject_id)),
            .groups = "drop") 

rmarkdown::paged_table(dat_trials_summarized)

# Condition-level summary
dat_condition_level <- dat_long %>% 
  group_by(explanation_type) %>% 
  summarize(mean = mean(satisfactory, na.rm = TRUE),
            sd = sd(satisfactory, na.rm = TRUE))

rmarkdown::paged_table(dat_condition_level)

```

# Confirmatory Analysis - Figures

## Figure with slope 

Black and white dots

```{r, fig.width = 3.5, fig.height = 6}
fig_slope <- dat_long %>% 
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .2) +
  # geom_point(data = dat_trials_summarized, 
  #            aes(x = explanation_type, y = mean_satisfactory), 
  #            alpha = 0.4, size = 5) +
  geom_point(data = dat_trials_summarized,
             aes(x = explanation_type, y = mean_satisfactory, 
                 fill = explanation_type),
             alpha = 0.8, 
             size = 5,
             shape = 21,
             color = "black") +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_line(data = dat_trials_summarized, 
            aes(x = explanation_type, 
                y = mean_satisfactory, 
                group = target), 
            alpha = 0.2, color = "black") +
  labs(y = "How Satisfactory?", 
       x = "Explanation Type",
       fill = "Explanation Type") +
  theme_cowplot() +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),
        legend.position = "top",
        legend.justification = "center",
        legend.key.size = unit(1, "cm"),
        legend.spacing.x = unit(1, "cm")
        ) +
  ylim(0, 100)

fig_slope

ggsave("figures/explanation_slope_black_and_white.png", width = 3, height = 6, plot = fig_slope, bg = "white")

```

## Figure facet by trial

```{r, fig.width = 12, fig.height = 12}
# Wide version fig - short names
dat_plot_long_wide <- dat_long %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(explanation = recode(explanation, !!!short_names)),
            aes(label = explanation, y = 95),
            vjust = 1, size = 6) + 
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
    facet_wrap(~target, nrow = 3, ncol = 5)

dat_plot_long_wide

# Wide version fig - compact names
dat_plot_long_wide_compact <- dat_long %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  geom_jitter(width = .05, alpha = .1) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(explanation = recode(explanation, !!!compact_names)),
            aes(label = explanation, y = 95),
            vjust = 1, size = 6) + 
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 25),
    axis.text.y = element_text(size = 25),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    legend.position = "none",
    strip.text = element_text(size = 18),
    strip.background = element_rect(fill = NA, color = "black")) +
    facet_wrap(~target, nrow = 3, ncol = 5)

dat_plot_long_wide_compact

# Long version fig - short names
dat_plot_long_long <- dat_long %>%
  mutate(target = recode(target, !!!short_names)) %>%
  ggplot(aes(x = explanation_type, y = satisfactory, fill = explanation_type)) +
  stat_summary(fun = mean, geom = "bar", color = "black") +
  # geom_point(alpha = 0.1) +
  geom_point(aes(fill = explanation_type),
                      shape = 21,
                      color = "black",
                      size = 3.5,
                      alpha = 0.2) +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_line(aes(group = subject_id), alpha = 0.1) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  # scale_fill_manual(values = c("grey80", "white")) +
  geom_text(data = dat_trials_summarized %>%
              mutate(explanation = recode(explanation, !!!short_names)) %>% 
              mutate(target = recode(target, !!!short_names)),
            aes(label = explanation, y = 95),
            vjust = 1, size = 6) +
  labs(y = "How Satisfactory", x = "Explanation type") +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 16),
    axis.text.y = element_text(size = 16),
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17),
    legend.position = "none",
    strip.text = element_text(size = 16),
    strip.background = element_rect(fill = NA, color = "black")
    ) +
  facet_wrap(~target) 
  
dat_plot_long_long

ggsave("figures/explanation_slope_facet_by_trial.png", 
                                width = 7,
                                height = 10,
                    plot = dat_plot_long_long, 
                    bg = "white") 

```

# Confirmatory Analysis - Analysis

## Prepare data
```{r}
dat_model <- dat_long %>% 
  mutate(explanation_type = factor(explanation_type, levels = c("CO", "CC")),
         subject_id = as_factor(subject_id)) 

rmarkdown::paged_table(dat_model)
```

## Run model

```{r}
#model
model_effect_of_explanation_type <- lmerTest::lmer(satisfactory ~ explanation_type +
                                              (1|subject_id), data = dat_model)

#model outputs
summary(model_effect_of_explanation_type)
standardize_parameters(model_effect_of_explanation_type)
confint(model_effect_of_explanation_type)

#odds ratios
fixef(model_effect_of_explanation_type)  # Check parameter name
or <- exp(fixef(model_effect_of_explanation_type)[1])
or

#probabilities
effects_data <- allEffects(model_effect_of_explanation_type)
effects_df <- as.data.frame(effects_data$explanation)
effects_df

#plot model
plot(allEffects(model_effect_of_explanation_type))

```

## Check model

```{r}
performance::check_model(model_effect_of_explanation_type)
```

# Exploratory Distances Analysis - Prep

## Read distances 

```{r}
distances <- read_csv(freesort_and_causal_distances_df_path)

```

## Append distances 

```{r}
#join distances to Trial level data
dat_trials_summarized_distances_long <- dat_trials_summarized %>% 
  left_join(distances %>% 
              rename("target" = itemB,
                     "explanation" = itemA,
                     "domain_explanation" = domain_itemA,
                     "domain_target" = domain_itemB,
                     "joint_distance" = freesort_minus_causal) %>% 
              mutate(target = factor(target, levels = desired_order)) %>% 
              relocate(target, .before = "explanation"),
            by = c("target", "explanation")) %>% 
  select(target, explanation, explanation_type, domain_target, 
         domain_explanation, mean_satisfactory, joint_distance)

rmarkdown::paged_table(dat_trials_summarized_distances_long)

```

## Save joined distances

```{r}
write_csv(dat_trials_summarized_distances_long, "dat_explanation_distances.csv")

```

## Read back in data frame

```{r}
analysis_path <- here("code", "analysis")

dat_trials_summarized_distances_long <- read_csv(paste0(analysis_path,
                "/2_explanation/dat_explanation_distances.csv"))

```

# Exploratory Distances Analysis - Figures

## 1 fit line 

```{r}
fig_distances <- dat_trials_summarized_distances_long %>% 
  mutate(target = recode(target, !!!short_names),
         explanation = recode(explanation,!!!short_names)) %>% 
  mutate(labels = paste0("target: ", target, "\n", explanation_type, ": ", explanation)) %>% 
  ggplot(aes(y = mean_satisfactory, x = joint_distance)) +
  geom_point(aes(fill = explanation_type),
                      shape = 21,
                      color = "black",
                      size = 5,
                      alpha = 0.8) +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_smooth(method = "lm", color = "black") +
  # geom_text(aes(label = labels), vjust = -0.5, size = 2) + #uncomment this to include labels
  ylim(0, 100) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Explanation",
    color = "CC/CO Item",
    fill = "CC/CO Item",
    x = "More CO relevant, More CC relevant",
    y = "Satisfactory ratings"
  ) 

fig_distances

ggsave("figures/explanation_distances_1_line_black_and_white.png", width = 6, height = 4,
                        plot = fig_distances, bg = "white")

```

## 2 fit lines 

```{r}
fig_distances <- dat_trials_summarized_distances_long %>% 
  mutate(target = recode(target, !!!short_names),
         explanation = recode(explanation,!!!short_names)) %>% 
  mutate(labels = paste0("target: ", target, "\n", explanation_type, ": ", explanation)) %>% 
  ggplot(aes(y = mean_satisfactory, x = joint_distance)) +
  geom_point(aes(fill = explanation_type),
                      shape = 21,
                      color = "black",
                      size = 5,
                      alpha = 0.8) +
  scale_fill_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  geom_smooth(aes(color = explanation_type), method = "lm") +
  scale_color_manual(values = c(
          "CC" = "#CCCCCC",
          "CO" = "white")) +
  
   ylim(0, 100) +
  # geom_text(aes(label = labels), vjust = -0.5, size = 2) + #uncomment this to include labels
  theme_bw() +
  theme(axis.text.x = element_text(size = 30),
        axis.text.y = element_text(size = 30),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18),
        legend.position = "top",
        plot.title = element_text(hjust = 0.5)
        ) +
  labs(
    title = "Explanation",
    color = "CC/CO Item",
    fill = "CC/CO Item",
    x = "More CO relevant, More CC relevant",
    y = "How satifying?"
  ) 

fig_distances

ggsave("figures/explanation_distances_2_lines_black_and_white.png", width = 6, height = 4,
                        plot = fig_distances, bg = "white")


```




# Exploratory Distances Analysis - Analysis

## Append distances 

```{r}
#join distances to subject-level data
dat_long_distances <- dat_long %>% 
  left_join(distances %>% 
              rename("target" = itemB,
                     "explanation" = itemA,
                     "domain_explanation" = domain_itemA,
                     "domain_target" = domain_itemB,
                     "joint_distance" = freesort_minus_causal) %>% 
              mutate(target = factor(target, levels = desired_order)) %>% 
              relocate(target, .before = "explanation"),
            by = c("target", "explanation")) %>% 
  select(subject_id, target, explanation, explanation_type, satisfactory,
         domain_target, domain_explanation, joint_distance)

rmarkdown::paged_table(dat_long_distances)

```

## Model - Distance 

```{r}
model_effect_of_distance <- lmerTest::lmer(satisfactory ~ joint_distance + (1|subject_id), 
               data = dat_long_distances)

#model outputs
summary(model_effect_of_distance)
confint(model_effect_of_distance) #cis unstandardized
standardize_parameters(model_effect_of_distance) #cis standardized

#plot
plot(allEffects(model_effect_of_distance))

```

## Model - Joint_CC + Joint_CO

Modelling joint distances independently. Not reported in paper or SI.

```{r}
dat_model_separate <-dat_long_distances %>%
  pivot_wider(names_from = "explanation_type",
              values_from = "joint_distance") %>%
  group_by(target) %>%
  mutate(joint_CO = first(na.omit(CO))) %>%
  mutate(joint_CC = first(na.omit(CC))) %>%
  ungroup()

# View(dat_model_separate)
model_separate <- lmerTest::lmer(satisfactory ~ joint_CC + joint_CO + (1|subject_id),
               data = dat_model_separate)

summary(model_separate)
standardize_parameters(model_separate)
  
```

## Model - Distance * Type

Modelling interaction effect. Not reported in paper or SI.

```{r}
# For overall slope
model_interaction <- lmerTest::lmer(satisfactory ~ 
                                      joint_distance * explanation_type 
                                    + (1|subject_id), 
               data = dat_long_distances)

#model outputs
summary(model_interaction)
confint(model_interaction) #cis unstandardized
standardize_parameters(model_interaction) #cis standardized

#standardized betas
model_interaction_standardized <- standardize(model_interaction, method = "refit")

beta_CC_std <- fixef(model_interaction_standardized)["joint_distance"]
beta_CC_std

beta_CO_std <- beta_CC_std +
  fixef(model_interaction_standardized)["joint_distance:explanation_typeCO"]
beta_CO_std

#==standardized betas with cis 
model_std <- standardize(model_interaction_standardized, method = "refit")

emtrends(model_std, 
         ~ explanation_type, 
         var = "joint_distance")

```

# THE END

```{r}

```


