---
title: "Experiment 1 preprocessing"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      number_sections: true
date: "2024-7-7"
author: Joseph Outa
---

This script does the following:  
1. Takes raw data from the main study `data_raw.csv`. 
2. Processes it into a combined (i.e. Freesort Task + Causal Pairs Task) data frame and saves into csv `data_processed_step1.csv`. 
3. Generates model predictions (model RDM data) and saves into csv `data_model_predictions.csv`.  
4. Plots RDMs and saves them into `figures/model-rdms`. 

Study description:    
- This study was ran on 6/30/25 on Connect CloudResearch, N = 102 participants   
- Subject selection criteria: 95% approval rate, minimum 10 previous submissions, and fluent in English. 

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
pacman::p_load(tidyverse, here, corrplot, jsonlite, RColorBrewer)
sessionInfo()
```

# Read data

```{r}
base_path <- here("code")
data_path <- paste0(base_path, "/data/1_measure/data_raw.csv")
# d <- read_csv(data_path)

d <- read_csv(data_path, col_types = cols(
  .default = col_guess(),
  final_locations = col_character(),
  init_locations = col_character(),
  moves = col_character()
))

```

# Set variables

```{r}
items <- c("choose what to do", "reach for something", "feel scared", 
           "experience pain", "get sick", "get tired", "become hungry", 
           "see something", "think about something", "hear something", 
           "remember something", "jump up and down", "kick something", 
           "take a walk", "sit down")

desired_order <- c("see something", "hear something", "choose what to do", 
                  "remember something", "think about something", "reach for something", 
                  "kick something", "sit down", "jump up and down", "take a walk", 
                  "feel scared","experience pain", "get tired", "become hungry","get sick")

#paths: data outputs
analysis_path <- paste0(base_path, "/analysis/1_measure")
rdm_figures_outputs_path <- paste0(analysis_path, "/figures/model-rdms/")
combined_output_csv <- "data_processed_step1"
snapshots_path <- paste0(analysis_path, "/snapshots_experiment1_preprocessing_analysis")
combined_output_path <- paste0(snapshots_path, "/", combined_output_csv, ".csv") 
model_predictions_output_path <- paste0(snapshots_path, "/data_model_predictions.csv") 

```


# Parse data frames

## Parse Sorting Task data

```{r}
data_freesort <- d %>%
  filter(trial_type == "freesort") %>% 
  select(subject_id, trial_index, final_locations) %>% 
  mutate(parsed_location = map(final_locations, ~ fromJSON(.))) %>% #parse JSON
  unnest(parsed_location) %>% #unnest the list column
  mutate(
    img_number = as.numeric(str_extract(src, "\\d+")), #etract image numbers from `src`
    item = items[img_number] #map image numbers to item labels
  ) %>%
  select(-c("final_locations", "src", "img_number")) %>% 
  mutate(trial_type = "freesort") %>% 
  relocate(trial_type, .after = subject_id) %>% 
  rename(original_trial_index = trial_index)

#write.csv(data_freesort, file = freesort_output_path, row.names = F)
```

## Parse Causal Pairs Task data

```{r}
response_data <- d %>%
  filter(trial_type == "survey-slider") %>% 
  select(subject_id, trial_index, response) %>%
  mutate(response = map(response, ~ tryCatch(
    fromJSON(.) %>%
      enframe(name = "question_id", value = "response"),
    error = function(e) tibble(question_id = character(), response = character())
  ))) %>%
  unnest(response) %>% 
  mutate(
    response = unlist(response), 
    response = as.numeric(response), 
    question_index = str_remove(question_id, "Q") 
  ) %>%
  select(subject_id, trial_index, question_index, response)

metadata_data <- d %>%
  select(subject_id, trial_index, `0`:`14`, `15`) %>% 
  pivot_longer(
    cols = -c(subject_id, trial_index),  
    names_to = "question_index",      
    values_to = "metadata"            
  ) %>% 
  mutate(
    parsed_metadata = map(metadata, ~ {
      if (is.na(.x)) {
        tibble() # Handle NA metadata
      } else {
        fromJSON(.x, simplifyVector = FALSE) %>%
          map(~ if (is.null(.)) NA else .) %>%  #replace NULL with NA
          as_tibble()
      }
    })
  ) %>% 
  unnest(parsed_metadata) %>%    
  select(-metadata)           

#merge the response_data and metadata_data into data_causal_pairs
data_causal_pairs <- response_data %>%
  inner_join(metadata_data, by = c("subject_id", "trial_index", "question_index")) %>% 
  mutate(trial_type = "causal_pairs") %>% 
  relocate(trial_type, .after = subject_id) %>%
  rename(original_trial_index = trial_index, 
         original_question_index = question_index) %>% 
  group_by(subject_id, trial_type) %>%
  mutate(trial_index = dense_rank(original_trial_index),
         question_index = row_number()) %>%
  ungroup() %>% 
  relocate(c("trial_index", "question_index"), .after = "trial_type") %>% 
  relocate(c("original_trial_index", "original_question_index"), .after = "correct_response")

```

## Exclusions

- In Causal Pairs Task we have 4 attention checks at pages 4, 8, 10 and 13. No attention checks in Sorting Task 
- We are excluding subjects who fail at least 2 attention checks (Other possible criteria: time taken to complete study)

```{r}
data_causal_pairs <- data_causal_pairs %>%
  mutate(attention_check_id = case_when(
    attention_check == TRUE & trial_index == 4  ~ 1, 
    attention_check == TRUE & trial_index == 8  ~ 2, 
    attention_check == TRUE & trial_index == 10 ~ 3, 
    attention_check == TRUE & trial_index == 13 ~ 4, 
    TRUE ~ NA_integer_ #non-attention check rows
  )) %>%
  mutate(correct_response = case_when(
    attention_check == TRUE & trial_index == 4  ~ 0, #"Move slider all the way to left"
    attention_check == TRUE & trial_index == 8  ~ 75,  #"Move slider to 'Maybe yes'"
    attention_check == TRUE & trial_index == 10 ~ 100, #"Move slider all the way to right"
    attention_check == TRUE & trial_index == 13 ~ 0,   #"Move slider to 'Definitely not'"
    TRUE ~ correct_response # Retain existing values for non-attention check rows
  )) %>%
  mutate(correct = case_when(
    attention_check == TRUE & trial_index == 4  & response >= 0 & response <= 5   ~ TRUE, 
    attention_check == TRUE & trial_index == 8  & response >= 70 & response <= 80 ~ TRUE, 
    attention_check == TRUE & trial_index == 10 & response >= 0 & response <= 5 ~ TRUE, #3 and 4 are switched for some reason
    attention_check == TRUE & trial_index == 13 & response >= 95 & response <= 100   ~ TRUE,
    attention_check == TRUE ~ FALSE, #outside acceptable range
    TRUE ~ NA #non-attn check rows
  ))

excluded_participants <- data_causal_pairs %>%
  filter(attention_check == TRUE) %>% 
  group_by(subject_id) %>% 
  summarize(
    num_incorrect = sum(correct == FALSE, na.rm = TRUE), 
    .groups = "drop"
  ) %>%
  filter(num_incorrect >= 2) %>% #identify participants with x or more incorrect
  pull(subject_id) 

data_causal_pairs <- data_causal_pairs %>%
  filter(!subject_id %in% excluded_participants)

data_freesort <- data_freesort %>%
  filter(!subject_id %in% excluded_participants)

#excluded 1 subject: subj_14

```

## Add trial order column

```{r}
#Combine trial types to compare their starting original_trial_index
trial_order_info <- bind_rows(
  data_causal_pairs %>% distinct(subject_id, trial_type, original_trial_index),
  data_freesort %>% distinct(subject_id, trial_type, original_trial_index)
) %>%
  group_by(subject_id) %>%
  summarize(
    trial_type_order = case_when(
      min(original_trial_index[trial_type == "causal_pairs"]) < min(original_trial_index[trial_type == "freesort"]) ~ 
        list(c(causal_pairs = "first", freesort = "second")),
      TRUE ~ list(c(causal_pairs = "second", freesort = "first"))
    )
  ) %>%
  unnest_wider(trial_type_order)

#Add trial_type_order to data_causal_pairs
data_causal_pairs <- data_causal_pairs %>%
  left_join(
    trial_order_info %>% select(subject_id, causal_pairs),
    by = "subject_id"
  ) %>%
  rename(trial_type_order = causal_pairs) %>%
  relocate(trial_type_order, .after = trial_type)

# Add trial_type_order to data_freesort
data_freesort <- data_freesort %>%
  left_join(
    trial_order_info %>% select(subject_id, freesort),
    by = "subject_id"
  ) %>%
  rename(trial_type_order = freesort) %>%
  relocate(trial_type_order, .after = trial_type)

```

## Create combined data frame

```{r}
data_combined <- bind_rows(
  data_causal_pairs,
  data_freesort
)

assign(combined_output_csv, data_combined)

write.csv(data_combined, combined_output_path, row.names = F)

```

# Generate model RDM data 

These are the model predictions for the 4 hypotheses

```{r}
d_models_first3 <- expand.grid(itemA = desired_order, itemB = desired_order) %>% 
  filter(itemA != itemB) %>%  # Remove self-pairs
  
  #model 1: mind, action, body
  mutate(mind_action_body_itemA = case_when(itemA == "hear something" ~ "mind", #labels for first item of pair
                               itemA == "choose what to do" ~ "mind",
                               itemA == "remember something" ~ "mind",
                               itemA == "think about something" ~ "mind",
                               itemA == "see something" ~ "mind",
                               itemA == "reach for something" ~ "act",
                               itemA == "sit down" ~ "act", 
                               itemA == "jump up and down" ~ "act",
                               itemA == "kick something" ~ "act",
                               itemA == "take a walk" ~ "act",
                               itemA == "get tired" ~ "body", 
                               itemA == "become hungry" ~ "body",
                               itemA == "feel scared"~ "body",
                               itemA == "experience pain"~ "body",
                               itemA == "get sick"~ "body"),
         mind_action_body_itemB = case_when(itemB == "hear something" ~ "mind", #labels for second item of pair
                               itemB == "choose what to do" ~ "mind",
                               itemB == "remember something" ~ "mind",
                               itemB == "think about something" ~ "mind",
                               itemB == "see something" ~ "mind",
                               itemB == "reach for something" ~ "act",
                               itemB == "sit down" ~ "act", 
                               itemB == "jump up and down" ~ "act",
                               itemB == "kick something" ~ "act",
                               itemB == "take a walk" ~ "act",
                               itemB == "get tired" ~ "body", 
                               itemB == "become hungry" ~ "body",
                               itemB == "feel scared"~ "body",
                               itemB == "experience pain"~ "body",
                               itemB == "get sick"~ "body")) %>% 
  
  #model 2: fine-grained, mba: perceptual, cognition, object & non-object directed, phasic & non phasic changes
   mutate(fine_grained_itemA = case_when(itemA == "hear something" ~ "per",
                               itemA == "see something" ~ "per",
                               itemA == "choose what to do" ~ "cog",
                               itemA == "remember something" ~ "cog",
                               itemA == "think about something" ~ "cog",
                               itemA == "reach for something" ~ "odAct",
                               itemA == "sit down" ~ "SpAct", 
                               itemA == "jump up and down" ~ "SpAct",
                               itemA == "kick something" ~ "odAct",
                               itemA == "take a walk" ~ "SpAct",
                               itemA == "get tired" ~ "BnS", 
                               itemA == "become hungry" ~ "BnS",
                               itemA == "feel scared"~ "BS",
                               itemA == "experience pain"~ "BS",
                               itemA == "get sick"~ "BnS",),
         fine_grained_itemB = case_when(itemB == "hear something" ~ "per",
                               itemB == "see something" ~ "per",
                               itemB == "choose what to do" ~ "cog",
                               itemB == "remember something" ~ "cog",
                               itemB == "think about something" ~ "cog",
                               itemB == "reach for something" ~ "odAct",
                               itemB == "sit down" ~ "SpAct", 
                               itemB == "jump up and down" ~ "SpAct",
                               itemB == "kick something" ~ "odAct",
                               itemB == "take a walk" ~ "SpAct",
                               itemB == "get tired" ~ "BnS", 
                               itemB == "become hungry" ~ "BnS",
                               itemB == "feel scared"~ "BS",
                               itemB == "experience pain"~ "BS",
                               itemB == "get sick"~ "BnS")) %>% 

      #model 3: (2 groups) physical and non-physical/psychological events:
      mutate(psychological_physical_itemA = case_when(itemA == "hear something" ~ "ethereal",
                               itemA == "see something" ~ "ethereal",
                               itemA == "choose what to do" ~ "ethereal",
                               itemA == "remember something" ~ "ethereal",
                               itemA == "think about something" ~ "ethereal",
                               itemA == "reach for something" ~ "phys",
                               itemA == "sit down" ~ "phys", 
                               itemA == "jump up and down" ~ "phys",
                               itemA == "kick something" ~ "phys",
                               itemA == "take a walk" ~ "phys",
                               itemA == "get tired" ~ "phys", 
                               itemA == "become hungry" ~ "phys",
                               itemA == "feel scared"~ "phys",
                               itemA == "experience pain"~ "phys",
                               itemA == "get sick"~ "phys"),
             psychological_physical_itemB = case_when(itemB == "hear something" ~ "ethereal",
                               itemB == "see something" ~ "ethereal",
                               itemB == "choose what to do" ~ "ethereal",
                               itemB == "remember something" ~ "ethereal",
                               itemB == "think about something" ~ "ethereal",
                               itemB == "reach for something" ~ "phys",
                               itemB == "sit down" ~ "phys", 
                               itemB == "jump up and down" ~ "phys",
                               itemB == "kick something" ~ "phys",
                               itemB == "take a walk" ~ "phys",
                               itemB == "get tired" ~ "phys", 
                              itemB == "become hungry" ~ "phys",
                               itemB == "feel scared"~ "phys",
                               itemB == "experience pain"~ "phys",
                               itemB == "get sick"~ "phys")) %>% 
  
  #scoring the items
  mutate("model1_mind_action_body" = ifelse(mind_action_body_itemA == mind_action_body_itemB, 0, 1),
         "model2_fine_grained" = ifelse(fine_grained_itemA == fine_grained_itemB, 0, 1),
         "model3_psychological_physical" = ifelse(psychological_physical_itemA == psychological_physical_itemB, 0, 1)) 

# write.csv(d_models_first3, models_output_path, row.names = F)
```

## Add USE embeddings

```{r}
#load USE embeddings
embedding_df <- readRDS(here(analysis_path, "embeddings", "item_embeddings.rds")) 

d_models <- d_models_first3 %>% 
  select(-c("mind_action_body_itemA", "mind_action_body_itemB", 
            "fine_grained_itemA","fine_grained_itemB", 
            "psychological_physical_itemA", "psychological_physical_itemB"))

#merge embeddings to original data frame
d_models_with_embeddings <- d_models %>%
  left_join(embedding_df, by = c("itemA" = "item")) %>%
  rename(embeddingA = embedding) %>%
  left_join(embedding_df, by = c("itemB" = "item")) %>%
  rename(embeddingB = embedding)

#compute cosine similarity for each row
d_all_models <- d_models_with_embeddings %>%
  rowwise() %>% 
  mutate(cosine_similarity = sum(unlist(embeddingA) * unlist(embeddingB)) /
                 (sqrt(sum(unlist(embeddingA)^2)) * sqrt(sum(unlist(embeddingB)^2)))) %>%
  ungroup() %>% 
  rowwise() %>% 
  mutate(cosine_similarity = (1 - cosine_similarity) / 2) %>% #turn c.s. to a disimilarity measure
  ungroup() %>% 
  select(-c("embeddingA", "embeddingB")) %>% 
  rename("model4_use_embeddings" = cosine_similarity) %>% 
  ungroup() 

write.csv(d_all_models, model_predictions_output_path, row.names = F)

```

# Plot model RDMs

```{r}
plot_rdm_model <- function(data, column_name, desired_order, plot_title) {

  df_matrix <- data %>%
    mutate(
      itemA = factor(itemA, levels = desired_order),
      itemB = factor(itemB, levels = desired_order)
    ) %>%
    select(itemA, itemB, all_of(column_name)) %>%
    pivot_wider(names_from = itemB, values_from = all_of(column_name)) %>%
    column_to_rownames("itemA")
  
  df_matrix <- df_matrix[desired_order, desired_order]
  diag(df_matrix) <- NA 
  
  #min-max normalize
  min_val <- min(df_matrix, na.rm = TRUE)
  max_val <- max(df_matrix, na.rm = TRUE)
  df_matrix <- (df_matrix - min_val) / (max_val - min_val)

  custom_palette <- colorRampPalette(c("red", "white", "blue"))

  corrplot(
    as.matrix(df_matrix), method = "color", is.corr = FALSE,
    # col = custom_palette(200),
    tl.col = "black", 
    #title = plot_title,
    title = "",
    col = brewer.pal(11, "RdBu"),
    cex.main = 3, #title text size
    tl.pos = "n", #remove labels
    mar = c(0, 0, 2, 0), addgrid.col = "darkgray",
    na.label = "square",       
    na.label.col = "darkgrey",
    cl.offset = 1.0,  
    cl.cex = 2, #legend label text size
    cl.ratio = 0.22, #widen the legend bar: change this to push words far away
  )
}

plot_rdm_model(d_all_models, "model4_use_embeddings", desired_order, "Cosine Distance")
plot_rdm_model(d_all_models, "model1_mind_action_body", desired_order, "3 categories: MBA")
plot_rdm_model(d_all_models, "model2_fine_grained", desired_order, "6 categories: PCOS")
plot_rdm_model(d_all_models, "model3_psychological_physical", desired_order, "2 categories: PE")
# save them

models <- list(
  list(column_name = "model4_use_embeddings", order = desired_order, title = "Cosine Distance"),
  list(column_name = "model1_mind_action_body", order = desired_order, title = "3 categories: MBA"),
  list(column_name = "model2_fine_grained", order = desired_order, title = "6 categories: PCOS"),
  list(column_name = "model3_psychological_physical", order = desired_order, title = "2 categories: PE")
)

for (i in seq_along(models)) {
  model <- models[[i]]
  output_file <- paste0(rdm_figures_outputs_path, "model_", i, ".png")
  # pdf(file = output_file, width = 8, height = 6) #open PDF device
  png(file = output_file, width = 2400, height = 1800, bg = "transparent", res = 300)
  plot_rdm_model(
    data = d_all_models,
    column_name = model$column_name,
    desired_order = model$order,
    plot_title = model$title
  )
  dev.off() #close PDF device
}

```

# Demographics

```{r}
df_demographics <- d %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("subject_id", "trial_id","feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```



```{r}

```


