---
title: "Experiment 1 analysis"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-7-1"
author: Joseph Outa
---

Background:
This is the analysis script for the measure experiment (experiment 1).

This experiment was conducted on 6/30/25 on Connect CloudResearch, N = 102 participants.  

Experiment 1 presented two tasks in a random order in a within-subjects design: a Freesort Task and a Causal Pairs Task. Subjects sorted 15 items in a sorting canvas, and rated causal relatedness between all 210 pairs of the 15 items (excluding self pairs). 

The N was 102 adults (before exclusions), recruited online via Cloud Research Connect.

The two research questions are: (1) How do subjects sort items? Do they sort into 3 groups, 2 group, 6 groups, or based on feature-based similarity. (2) Do subjects' causal pairs ratings (from the Causal Pairs Task) reflect boundaries in Freesort Task or do they go beyond, and if so, what is their structure?

Script description:
This script:-  
- proceeds from the output of the preprocessing script.   
- takes as input `data_processed_step1.csv`, and `data_model_prediction.csv`
- plots Sorting and Causal Pairs Task rdms, gets correlations between empirical and models RDM, gets within subject correlations.   
- outputs `data_freesort_mins_causals.csv` for use in study 2 script for item selection.

What this script does: Per-subject normalize, followed by average, followed be renormalizing. For correlations with models: only correlates upper tris. 

# Setup

## Load packages

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(tidyverse,
               ggforce,
               conflicted,
               here,
               cowplot,
               lme4,
               lmerTest,
               colorspace,
               effects,
               Hmisc,
               performance,
               rmarkdown,
               purrr,
               gt,
               ragg,
               readr,
               scales,
               patchwork,
               corrplot,
               magick,
               pdftools,
               simr,
               viridis,
               rcartocolor,
               RColorBrewer,
               effectsize,
               parameters,
               flextable
               )

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ 
       conflict_prefer(.x, "dplyr"))

conflicts_prefer(simr::fixed)
theme_set(theme_bw())
sessionInfo()

```

## Set variables

```{r}
# variables
desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")
domain_order <- c("mind", "action", "body")
freesort_columns <- c("subject_id", "x", "y", "item")
freesort_columns_with_trial_order <- c("subject_id", "x", "y", "item", "trial_type", "trial_type_order")
causal_pairs_columns <- c("subject_id", "itemA", "itemB", "response")

# paths
## script inputs
base_path <- here("code", "analysis", "1_measure")
snapshots_input_path <- paste0(base_path, "/snapshots_experiment1_preprocessing_analysis") 
data_input_path <- paste0(snapshots_input_path, "/data_processed_step1.csv")
model_predictions_input_path <- paste0(snapshots_input_path, "/data_model_predictions.csv") 
rdms_input_path <- paste0(base_path, "/figures/model-rdms")

## script outputs
snapshots_output_path <- paste0(base_path, "/snapshots_experiment1_analysis")
rdms_outputs_path <- paste0(base_path, "/figures")
freesort_minus_causal_pairs_distances_output_path <- paste0(snapshots_output_path, "/freesort_minus_causals.csv")

## saved dataframes 
data_processed_output_path <- paste0(snapshots_output_path, "/data_processed_step2.csv") #used in item-selection script
correlations_output_path <- paste0(snapshots_output_path, "/correlations.csv") #not used in this script

```

# Confirmatory Findings - Prep

## Read data

```{r}
d <- read_csv(data_input_path)

#how many subjects
d %>% 
  slice(length(d$subject_id)) %>% 
  pull(subject_id)

```

## Reshape data

Create separate data frames for Sorting Task, Causal Pairs Task and a combined data frame. 

```{r}
df_causal_pairs <- d %>%
  filter(trial_type == "causal_pairs", !attention_check, itemA != itemB) %>%
  select(all_of(causal_pairs_columns)) %>%
  
  #normalize causal distances and flip scale
  mutate(
    causal_pairs_distance = (1 - response / 100 - min(1 - response / 100, na.rm = TRUE)) /
                            (max(1 - response / 100, na.rm = TRUE) - min(1 - response / 100, na.rm = TRUE))
  ) %>%
  select(subject_id, itemA, itemB, causal_pairs_distance) %>% 
  mutate(domain_itemA = case_when(itemA == "hear something" ~ "mind", #labels for first item of pair
                             itemA == "choose what to do" ~ "mind",
                             itemA == "remember something" ~ "mind",
                             itemA == "think about something" ~ "mind",
                             itemA == "see something" ~ "mind",
                             itemA == "reach for something" ~ "action",
                             itemA == "sit down" ~ "action", 
                             itemA == "jump up and down" ~ "action",
                             itemA == "kick something" ~ "action",
                             itemA == "take a walk" ~ "action",
                             itemA == "get tired" ~ "body", 
                             itemA == "become hungry" ~ "body",
                             itemA == "feel scared"~ "body",
                             itemA == "experience pain"~ "body",
                             itemA == "get sick"~ "body"),
         domain_itemB = case_when(itemB == "hear something" ~ "mind", 
                               itemB == "choose what to do" ~ "mind",
                               itemB == "remember something" ~ "mind",
                               itemB == "think about something" ~ "mind",
                               itemB == "see something" ~ "mind",
                               itemB == "reach for something" ~ "action",
                               itemB == "sit down" ~ "action", 
                               itemB == "jump up and down" ~ "action",
                               itemB == "kick something" ~ "action",
                               itemB == "take a walk" ~ "action",
                               itemB == "get tired" ~ "body", 
                               itemB == "become hungry" ~ "body",
                               itemB == "feel scared"~ "body",
                               itemB == "experience pain"~ "body",
                               itemB == "get sick"~ "body")) %>% 
  relocate(domain_itemA, .after = "itemB") %>% 
  relocate(domain_itemB, .after = "domain_itemA") %>% 
  mutate(itemA = factor(itemA, levels = desired_order),
         itemB = factor(itemB, levels = desired_order)) 


df_freesort <- d %>%
  filter(trial_type == "freesort") %>%
  select(all_of(freesort_columns_with_trial_order)) %>%
  rename(item_freesort = item) %>%
  
  #expand pairs within each subject
  group_by(subject_id, trial_type_order) %>%
  summarize(pairs = list(expand.grid(itemA = item_freesort, itemB = item_freesort, stringsAsFactors = FALSE)), .groups = "drop") %>%
  unnest(pairs) %>%
  filter(itemA != itemB) %>%
  
  #join in freesort coordinates
  left_join(d %>% filter(trial_type == "freesort") %>%
              select(subject_id, itemA = item, x, y),
            by = c("subject_id", "itemA")) %>%
  rename(x_itemA = x, y_itemA = y) %>%
  
  left_join(d %>% filter(trial_type == "freesort") %>%
              select(subject_id, itemB = item, x, y),
            by = c("subject_id", "itemB")) %>%
  rename(x_itemB = x, y_itemB = y) %>%
  
  group_by(subject_id) %>% 
  
  #compute and normalize Euclidean distances
  mutate(
    euclidean_distance = sqrt((x_itemA - x_itemB)^2 + (y_itemA - y_itemB)^2),
    freesort_distance = round( (euclidean_distance - min(euclidean_distance, na.rm = TRUE)) /
                    (max(euclidean_distance, na.rm = TRUE) - min(euclidean_distance, na.rm = TRUE)),2),
    
    trial_type_order = ifelse(trial_type_order == "first", "causal_pairs_second", "causal_pairs_first"),
    
    itemA = factor(itemA, levels = desired_order),
    itemB = factor(itemB, levels = desired_order)) %>%
  select(subject_id, itemA, itemB, freesort_distance, trial_type_order) %>%
  ungroup() %>% 
  mutate(domain_itemA = case_when(itemA == "hear something" ~ "mind", #labels for first item of pair
                             itemA == "choose what to do" ~ "mind",
                             itemA == "remember something" ~ "mind",
                             itemA == "think about something" ~ "mind",
                             itemA == "see something" ~ "mind",
                             itemA == "reach for something" ~ "action",
                             itemA == "sit down" ~ "action", 
                             itemA == "jump up and down" ~ "action",
                             itemA == "kick something" ~ "action",
                             itemA == "take a walk" ~ "action",
                             itemA == "get tired" ~ "body", 
                             itemA == "become hungry" ~ "body",
                             itemA == "feel scared"~ "body",
                             itemA == "experience pain"~ "body",
                             itemA == "get sick"~ "body"),
         domain_itemB = case_when(itemB == "hear something" ~ "mind", 
                               itemB == "choose what to do" ~ "mind",
                               itemB == "remember something" ~ "mind",
                               itemB == "think about something" ~ "mind",
                               itemB == "see something" ~ "mind",
                               itemB == "reach for something" ~ "action",
                               itemB == "sit down" ~ "action", 
                               itemB == "jump up and down" ~ "action",
                               itemB == "kick something" ~ "action",
                               itemB == "take a walk" ~ "action",
                               itemB == "get tired" ~ "body", 
                               itemB == "become hungry" ~ "body",
                               itemB == "feel scared"~ "body",
                               itemB == "experience pain"~ "body",
                               itemB == "get sick"~ "body")) 

df_combined <- df_freesort %>%
  # left_join(df_causal_pairs, by = c("subject_id", "itemA", "itemB")) # %>% 
  left_join(df_causal_pairs, by = c("subject_id", "itemA", "itemB", "domain_itemA", "domain_itemB")) %>%
  mutate(domain_itemA = factor(domain_itemA, levels = domain_order),
         domain_itemB = factor(domain_itemB, levels = domain_order)) %>% 
  relocate(freesort_distance, .before = "causal_pairs_distance") %>%
  relocate(trial_type_order, .after = "domain_itemB")

paged_table(df_combined)

```

## Write data into csvs

```{r}
write.csv(df_combined, data_processed_output_path, row.names = F)
write.csv(df_combined, paste0(snapshots_output_path, "/df_combined.csv"), row.names = F)
write.csv(df_causal_pairs, paste0(snapshots_output_path, "/df_causal_pairs.csv"), row.names = F)
write.csv(df_freesort, paste0(snapshots_output_path, "/df_freesort.csv"), row.names = F)
```

# Confirmatory Findings - RDM Figures

## Freesort Task

## Figure 02A: Mean Freesort RDM 

```{r, fig.width = 12, fig.height = 12}
df_mean_freesort <- df_freesort %>% 
  unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
  group_by(item_pairs) %>% 
  mutate(mean_freesort_distance = mean(freesort_distance)) %>% 
  ungroup()  
  
# matrixify and plot
df_mean_freesort_rdm <- df_mean_freesort %>% 
  distinct(item_pairs, .keep_all = TRUE) %>% 
  select(itemA, itemB, mean_freesort_distance) %>% 
  pivot_wider(names_from = itemB, values_from = mean_freesort_distance) %>% 
  column_to_rownames("itemA")  
  
df_mean_freesort_rdm <- df_mean_freesort_rdm[desired_order, desired_order]

diag(df_mean_freesort_rdm) <- NA #set diagonals 

#min max normalize
df_mean_freesort_matrix <- as.matrix(df_mean_freesort_rdm) 
min_val <- min(df_mean_freesort_matrix, na.rm = TRUE) 
max_val <- max(df_mean_freesort_matrix, na.rm = TRUE) 
df_mean_freesort_matrix <- (df_mean_freesort_matrix - min_val) / (max_val - min_val) 

group_colors <- c("#db9728", "#d0495a", "#00788a")


my_cols <- brewer.pal(11, "RdBu")

custom_palette <- colorRampPalette(c("#5E0E20", "white", "#132F5E")) 

png(
  file = paste0(rdms_outputs_path, "/freesort/averageFreesortRDM.png"),
  width = 12,
  height = 12,
  units = "in",
  res = 300,
  bg = "transparent"
)

#large image
corrplot(
  df_mean_freesort_matrix,
  method = "color",
  is.corr = FALSE,
  col = brewer.pal(11, "RdBu"),
  tl.col = "black",
  tl.cex = 2,
  na.label = "square",       
  na.label.col = "darkgrey",   
  mar = c(0, 0, 2, 0),
  # addgrid.col = "darkgray",
  addgrid.col = "grey65",
  cl.offset = 1.0,  # Push labels even further
  cl.cex = 2,     # Slightly smaller label text
  cl.ratio = 0.22,   # Widen the legend bar. Change this to push words far away
  cex.main = 3
)

#run this with the above to include legend for the domain colors
legend(
  "topleft",
  inset = c(0.1, 0.1), #move the legend outside the plot
  legend = c("Mind", "Action", "Body"),
  fill = group_colors,
  border = NA,
  bty = "n", #no box around the legend
  cex = 2, #text size
  xpd = TRUE, #allow drawing outside the plot area
  #ncol = 1,
  y.intersp = 1.4 #increase this for more space between rows
)

```

## Figure S1A: Mean Freesort RDM with numbers

```{r}

png(
  file = paste0(rdms_outputs_path, "/freesort/averageFreesortRDM-numbers.png"),
  width = 12,
  height = 12,
  units = "in",
  res = 300,
  bg = "transparent"
)

#large image
corrplot(
  df_mean_freesort_matrix,
  method = "color",
  is.corr = FALSE,
  # col = brewer.pal(11, "RdBu"),
  # col = brewer.pal(11, "RdBu")[3:9],
  col = lighten(
    brewer.pal(11, "RdBu"),
    amount = 0.2),
  tl.col = "black",
  tl.cex = 2,
  na.label = "square",
  na.label.col = "darkgrey",
  addCoef.col = "black",
  number.cex = 1.2,
  number.digits = 2,
  mar = c(0, 0, 2, 0),
  addgrid.col = "grey65",
  cl.offset = 1.0,
  cl.cex = 2,
  cl.ratio = 0.22,
  cex.main = 3
)


#run this with the above to include legend for the domain colors
legend(
  "topleft",
  inset = c(0.1, 0.1), #move the legend outside the plot
  legend = c("Mind", "Action", "Body"),
  fill = group_colors,
  border = NA,
  bty = "n", #no box around the legend
  cex = 2, #text size
  xpd = TRUE, #allow drawing outside the plot area
  #ncol = 1,
  y.intersp = 1.4 #increase this for more space between rows
)
```

# Causal Pairs Task

## Figure 02B: Mean Causal Pairs RDM

```{r, fig.width = 12, fig.height = 12}
df_mean_causal_pairs <- df_causal_pairs %>% 
  mutate(item_pairs = str_c(itemA, itemB, sep = "-"))  %>%
  group_by(item_pairs) %>%
  mutate(mean_causal_pairs_distance = mean(causal_pairs_distance, na.rm = TRUE)) %>%  #average across participants
  ungroup() 

df_mean_causal_pairs_rdm <- df_mean_causal_pairs %>%
  distinct(item_pairs, .keep_all = TRUE) %>% 
  select(itemA, itemB, mean_causal_pairs_distance) %>% 
  pivot_wider(names_from = itemB, values_from = mean_causal_pairs_distance) %>%
  column_to_rownames("itemA")  

df_mean_causal_pairs_rdm <- df_mean_causal_pairs_rdm[desired_order, desired_order]

diag(df_mean_causal_pairs_rdm) <- NA 

#min max normalize
df_mean_causal_pairs_matrix <- as.matrix(df_mean_causal_pairs_rdm) 
min_val <- min(df_mean_causal_pairs_matrix, na.rm = TRUE) 
max_val <- max(df_mean_causal_pairs_matrix, na.rm = TRUE) 
df_mean_causal_pairs_matrix <- (df_mean_causal_pairs_matrix - min_val) / (max_val - min_val) 

#colors
group_colors <- c("#db9728", "#d0495a", "#00788a") 


item_colors <- setNames(c(rep(group_colors[1], 5), #mind
                          rep(group_colors[2], 5), #action
                          rep(group_colors[3], 5)), #body
                        desired_order)

label_colors <- item_colors[rownames(df_mean_causal_pairs_rdm)]

png(
  file = paste0(rdms_outputs_path, "/causal_pairs/averageCausalPairsRDM.png"),
  width = 12,
  height = 12,
  units = "in",
  res = 300,
  bg = "transparent"
)


#large image
corrplot(
  df_mean_causal_pairs_matrix,
  method = "color",
  is.corr = FALSE,
  # col = custom_palette(200),
  col = brewer.pal(11, "RdBu"),
  tl.col = "black",
  # tl.col = label_colors, 
  tl.cex = 2,
  mar = c(0, 0, 2, 0),
  addgrid.col = "darkgray",
  na.label = "square",       
  na.label.col = "darkgrey",
  cl.offset = 1.0, 
  cl.cex = 2, #label text
  cl.ratio = 0.22, #push words far away
  cex.main = 3
)

#run this together with above to include a domains color legend
legend(
  "topleft",
  inset = c(0.1, 0.1),
  legend = c("Mind", "Action", "Body"),
  fill = group_colors,
  border = NA,
  bty = "n",
  cex = 2, #text size
  xpd = TRUE, #draw outside the plot area
  #ncol = 1,
  y.intersp = 1.4 #more space between rows
)

```

## Figure S1B: Mean Causal Pairs RDM with numbers

```{r}

png(
  file = paste0(rdms_outputs_path, "/causal_pairs/averageCausalPairsRDM-numbers.png"),
  width = 12,
  height = 12,
  units = "in",
  res = 300,
  bg = "transparent"
)

#large image
corrplot(
  df_mean_causal_pairs_matrix,
  method = "color",
  is.corr = FALSE,
  # col = brewer.pal(11, "RdBu"),
  col = lighten(
    brewer.pal(11, "RdBu"),
    amount = 0.2),
  tl.col = "black",
  tl.cex = 2,
  na.label = "square",
  na.label.col = "darkgrey",
  addCoef.col = "black",
  number.cex = 1.2,
  number.digits = 2,
  mar = c(0, 0, 2, 0),
  addgrid.col = "grey65",
  cl.offset = 1.0,
  cl.cex = 2,
  cl.ratio = 0.22,
  cex.main = 3
)


#run this together with above to include a domains color legend
legend(
  "topleft",
  inset = c(0.1, 0.1),
  legend = c("Mind", "Action", "Body"),
  fill = group_colors,
  border = NA,
  bty = "n",
  cex = 2, #text size
  xpd = TRUE, #draw outside the plot area
  #ncol = 1,
  y.intersp = 1.4 #more space between rows
)

```

# Confirmatory Findings - RDM Descriptive Analyses

## Specific Freesort Task relations reported in paper 

```{r}
compute_ci_freesort <- function(df, condition_label) {
  mean_distance <- mean(df$freesort_distance, na.rm = TRUE)
  sem <- sd(df$freesort_distance, na.rm = TRUE) / sqrt(nrow(df))
  ci_lower <- mean_distance - qt(0.975, df = nrow(df) - 1) * sem
  ci_upper <- mean_distance + qt(0.975, df = nrow(df) - 1) * sem

  cat(sprintf("%s: mean distance = %.3f [95%% CI: %.3f, %.3f]\n", 
              condition_label, mean_distance, ci_lower, ci_upper))
}

#compute and print within domain similarities
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "mind", domain_itemB == "mind"), "mind → mind")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "action", domain_itemB == "action"), "action → action")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "body"), "body → body")

#compute and print cross domain similarities
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "action", domain_itemB == "mind"), "mind → mind")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "mind"), "action → action")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "action"), "body → body")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "mind", domain_itemB == "action"), "body → body")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "mind", domain_itemB == "body"), "body → body")
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "action", domain_itemB == "body"), "body → body")


#average cross-domain similarity
(.565 + .574 + .582 + .565 + .574 + .583) / 6

#average within domain similarity
(.355 + .37 + .368) / 3

#feeling scared and physio
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "body") %>% filter(itemA == "feel scared"), "scared → body")

#feeling scared and mind
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "mind") %>% filter(itemA == "feel scared"), "scared → mind")

#all other body/physio and mind
compute_ci_freesort(df_freesort %>% filter(domain_itemA == "body", domain_itemB == "mind") %>% filter(itemA != "feel scared"), "scared → mind")

#sitting and jumping
compute_ci_freesort(df_freesort %>% filter(itemA == "sit down") %>% filter(itemB == "jump up and down"), "sit → jump")

```

## Specific Causal Pairs relations reported in paper 

```{r}
#========Function========#
compute_ci <- function(df, condition_label) {
  mean_distance <- mean(df$causal_pairs_distance, na.rm = TRUE)
  sem <- sd(df$causal_pairs_distance, na.rm = TRUE) / sqrt(nrow(df))
  ci_lower <- mean_distance - qt(0.975, df = nrow(df) - 1) * sem
  ci_upper <- mean_distance + qt(0.975, df = nrow(df) - 1) * sem

  cat(sprintf("%s: mean distance = %.3f [95%% CI: %.3f, %.3f]\n", 
              condition_label, mean_distance, ci_lower, ci_upper))
}

#========Mind & Action========#

#Mind → Action
compute_ci(df_causal_pairs %>% filter(domain_itemA == "mind", domain_itemB == "action"), "mind → action")

#Action → Mind
compute_ci(df_causal_pairs %>% filter(domain_itemA == "action", domain_itemB == "mind"), "action → mind")

##Effect size of Mind → Action vs Action → Mind
df_mind_to_action <- df_causal_pairs %>%
  filter(domain_itemA == "mind") %>%
  filter(domain_itemB == "action") %>% 
  mutate(type = "mind_to_action") %>% 
  select(subject_id, domain_itemA, domain_itemB, causal_pairs_distance, type) 

df_action_to_mind <- df_causal_pairs %>% 
              filter(domain_itemA == "action") %>%
              filter(domain_itemB == "mind") %>% 
              mutate(type = "action_to_mind") %>% 
              select(subject_id, domain_itemA, domain_itemB, causal_pairs_distance, type)

df_mind_action <- rbind(df_mind_to_action, df_action_to_mind) %>% 
  mutate(type = factor(type, levels = c("mind_to_action", "action_to_mind")))

paste0("ES of walk to mind to action vs action to mind")
model_mind_action <- lmerTest::lmer(causal_pairs_distance ~ type + (1 | subject_id),
                             data = df_mind_action)

summary(model_mind_action)
standardize_parameters(model_mind_action)

#========Walk & Actions vs Mind========#

#Walking → Mind
compute_ci(df_causal_pairs %>% filter(itemA == "take a walk", domain_itemB == "mind"), "walk → mind")

#All other actions → Mind
compute_ci(df_causal_pairs %>% filter(itemA != "take a walk", domain_itemB == "mind"), "other actions → mind")

#Effect size of Walk → Mind vs All other actions → Mind
df_walk <- df_causal_pairs %>%
  filter(domain_itemB == "mind") %>%  
  mutate(walking = ifelse(itemA == "take a walk", "walk", "not_walk"),
         walking = factor(walking, levels = c("walk", "not_walk")))

paste0("ES of Walk to Mind vs ALl other Actions to Mind")
model_walk <- lmerTest::lmer(causal_pairs_distance ~ walking + (1 | subject_id),
  data = df_walk)

summary(model_walk)
standardize_parameters(model_walk)

#========Assorted pairs========#

compute_ci(df_causal_pairs %>% filter(domain_itemA == "action", domain_itemB == "action"), "action → action")
compute_ci(df_causal_pairs %>% filter(domain_itemA == "body", domain_itemB == "body"), "body → body")
compute_ci(df_causal_pairs %>% filter(domain_itemA == "body", domain_itemB == "action"), "body → action")
compute_ci(df_causal_pairs %>% filter(domain_itemA == "action", domain_itemB == "body"), "action → body")

#========Perception & Cognition========#

#Perception → Cognition
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "mind", domain_itemB == "mind", 
                    itemA %in% c("hear something", "see something"),
                    itemB %in% c("choose what to do", "think about something", "remember something")),
           "perception → cognition")

#Cognition → Perception
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "mind", domain_itemB == "mind", 
                    itemB %in% c("hear something", "see something"),
                    itemA %in% c("choose what to do", "think about something", "remember something")),
           "cognition → perception")

#Effect size of Per → Cog vs Cog to Per
df_perception_to_cognition <- df_causal_pairs %>%
  filter(domain_itemA == "mind", domain_itemB == "mind", 
         itemA %in% c("hear something", "see something"),
         itemB %in% c("choose what to do", "think about something", "remember something")) %>% 
  mutate(type = "perception_to_cognition") %>% 
  select(subject_id, domain_itemA, domain_itemB, causal_pairs_distance, type) 

df_cognition_to_perception <- df_causal_pairs %>% 
  filter(domain_itemA == "mind", domain_itemB == "mind", 
         itemB %in% c("hear something", "see something"),
         itemA %in% c("choose what to do", "think about something", "remember something")) %>% 
  mutate(type = "cognition_to_perception") %>% 
  select(subject_id, domain_itemA, domain_itemB, causal_pairs_distance, type)

df_perception_cognition <- rbind(df_perception_to_cognition, df_cognition_to_perception) %>% 
  mutate(type = factor(type, levels = c("perception_to_cognition", 
                                        "cognition_to_perception")))

paste0("ES of Per to Cog vs Cog to Per")
model_perception_cognition <- lmerTest::lmer(causal_pairs_distance ~ type + (1 | subject_id),
                             data = df_perception_cognition)

summary(model_perception_cognition)
standardize_parameters(model_perception_cognition)

#========Other Assorted========#

#Seeing → Sick
compute_ci(df_causal_pairs %>% filter(itemA == "see something", itemB == "get sick"), "seeing → sick")

#Hearing → Sick
compute_ci(df_causal_pairs %>% filter(itemA == "hear something", itemB == "get sick"), "hearing → sick")

#Sitting → Jumping
compute_ci(df_causal_pairs %>% filter(itemA == "sit down", itemB == "jump up and down"), "sit → jump")

#Jumping → Sitting
compute_ci(df_causal_pairs %>% filter(itemA == "jump up and down", itemB == "sit down"), "jump → sit")

#========Walk & Actions vs Mind========#

#Walking → Mind
compute_ci(df_causal_pairs %>% filter(itemA == "take a walk", domain_itemB == "mind"), "walk → mind")

#All other actions → Mind
compute_ci(df_causal_pairs %>% filter(itemA != "take a walk", domain_itemB == "mind"), "other actions → mind")

##Effect size of Walk → Mind vs All Other actions → Mind
df_walk <- df_causal_pairs %>%
  filter(domain_itemB == "mind") %>%  
  mutate(walking = ifelse(itemA == "take a walk", "walk", "not_walk"),
         walking = factor(walking, levels = c("walk", "not_walk")))

model_walk <- lmerTest::lmer(causal_pairs_distance ~ walking + (1 | subject_id),
  data = df_walk)

summary(model_walk)
standardize_parameters(model_walk)

#========Jump & Kick vs Mind========#

#Jumping → Mind
compute_ci(df_causal_pairs %>% filter(itemA == "jump up and down", domain_itemB == "mind"), "jump → mind")

#Kicking → Mind
compute_ci(df_causal_pairs %>% filter(itemA == "kick something", domain_itemB == "mind"), "jump → mind")

#=======Causal Promiscuity Across Domains========#

#Mind -> All
compute_ci(df_causal_pairs %>% filter(domain_itemA == "mind"), "mind → all")

#Action -> All
compute_ci(df_causal_pairs %>% filter(domain_itemA == "action"), "action → all")

#Body -> All
compute_ci(df_causal_pairs %>% filter(domain_itemA == "body"), "body → all")

#effect size: mind vs action vs body
df_from_three_way <- df_causal_pairs %>%
  mutate(domain_source = domain_itemA) %>% 
  mutate(domain_source = factor(domain_source, levels = c("mind", "action", "body")))

model_from_three_way <- lmerTest::lmer(causal_pairs_distance ~ domain_source + (1|subject_id), 
                     data = df_from_three_way)
summary(model_from_three_way)

##standardized betas
standardize_parameters(model_from_three_way)

#effect size 2: mind vs mean od body and action
df_from_two_way <- df_causal_pairs %>%
  mutate(domain_source = domain_itemA) %>% 
  mutate(domain_source = ifelse(domain_itemA == "mind", "mind", "other")) %>% 
  mutate(domain_source = factor(domain_source, levels = c("mind", "other")))

model_from_two_way <- lmerTest::lmer(causal_pairs_distance ~ domain_source + (1|subject_id), 
                     data = df_from_two_way)
summary(model_from_two_way)

##standardized betas
standardize_parameters(model_from_two_way)


#===========Mind & Body===========#

#Mind -> Body
compute_ci(df_causal_pairs %>% filter(domain_itemA == "mind", domain_itemB == "body"), "mind → body")

#Body -> Mind
compute_ci(df_causal_pairs %>% filter(domain_itemA == "body", domain_itemB == "mind"), "body → mind")

df_mind_body <- df_causal_pairs %>%
  filter(
    (domain_itemA == "mind" & domain_itemB == "body") |
    (domain_itemA == "body" & domain_itemB == "mind")
  ) %>%
  mutate(direction = case_when(
    domain_itemA == "mind" & domain_itemB == "body" ~ "mind_to_body",
    domain_itemA == "body" & domain_itemB == "mind" ~ "body_to_mind"
  ),
  direction = factor(direction,
                     levels = c("body_to_mind", "mind_to_body")))

model_mind_body <- lmerTest::lmer(
  causal_pairs_distance ~ direction + (1 | subject_id),
  data = df_mind_body
)

summary(model_mind_body)
parameters::standardize_parameters(model_mind_body)

#===========Body to Cog vs Body to Percep and Body to Action===========#

#Body -> Cog
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "body", domain_itemB == "mind", 
                    itemB %in% c("choose what to do", "think about something", "remember something")),
           "body → cognition")
#Body -> Per
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "body", domain_itemB == "mind", 
                    itemB %in% c("see something", "hear something")),
           "body → perception")

#Body -> Action
compute_ci(df_causal_pairs %>% filter(domain_itemA == "body", domain_itemB == "action"), "body → action")

##Effect size of Body -> Cog vs Body -> Per and Body -> Action
df_body <- df_causal_pairs %>%
  filter(domain_itemA == "body") %>%
  mutate(effect_type = case_when(
      itemB %in% c("choose what to do", 
                   "think about something", 
                   "remember something") ~ "cognitive",
      itemB %in% c("see something", "hear something") ~ "perceptual",
      domain_itemB == "action" ~ "action",
      TRUE ~ NA_character_),
    effect_type = factor(effect_type, levels = c("cognitive", "perceptual", "action"))
  ) %>%
  filter(!is.na(effect_type))

model_body_targets <- lmerTest::lmer(causal_pairs_distance ~ effect_type + (1 | subject_id),
  data = df_body
)
summary(model_body_targets)
standardize_parameters(model_body_targets)

#===========Action, Cog & Per===========#

#Action -> Cog
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "action", domain_itemB == "mind", 
                    itemB %in% c("choose what to do", "think about something", "remember something")),
           "action → cognition")

#Action -> Per
compute_ci(df_causal_pairs %>% 
             filter(domain_itemA == "action", domain_itemB == "mind", 
                    itemB %in% c("see something", "hear something")),
           "action → perception")

```

# Checkpoint: Read back in data

Can start running code at this point!

```{r}
df_combined <- read_csv(paste0(snapshots_output_path, "/df_combined.csv"))
df_causal_pairs <- read_csv( paste0(snapshots_output_path, "/df_causal_pairs.csv"))
df_freesort <- read_csv(paste0(snapshots_output_path, "/df_freesort.csv"))
d_model_predictions <- read_csv(model_predictions_input_path)
```

# Confirmatory Findings - Noise ceiling Analysis

### Prepare functions 

```{r}
###============================ Noise ceiling functio ============================ ###

calculate_freesort_noise_ceiling <- function(data, subjects, desired_order, metric = "kendall") {
  # Initialize storage for correlations
  upper_bound <- numeric(length(subjects))
  lower_bound <- numeric(length(subjects))
  
  for (i in seq_along(subjects)) {
    subject <- subjects[i]
    
    #Subject's RDM
    subject_rdm <- data %>%
        filter(subject_id == subject) %>%
        select(subject_id, itemA, itemB, freesort_distance) %>% 
        pivot_wider(names_from = itemB, values_from = freesort_distance) %>%
        column_to_rownames("itemA") %>%
        as.matrix()
    subject_rdm <- subject_rdm[desired_order, desired_order]
    
    #Grand average RDM
    grand_avg_rdm <- data %>%
        select(subject_id, itemA, itemB, freesort_distance) %>% 
        unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
        group_by(item_pairs) %>%
        mutate(freesort_distance = mean(freesort_distance)) %>%
        ungroup() %>% 
        distinct(item_pairs, .keep_all = TRUE) %>% 
        select(-c(item_pairs, subject_id)) %>% 
        pivot_wider(names_from = itemB, values_from = freesort_distance) %>%
        column_to_rownames("itemA") %>%
        as.matrix()
    grand_avg_rdm <- grand_avg_rdm[desired_order, desired_order]
    
    #Other subjects' average RDM
    other_avg_rdm <- data %>%
      select(subject_id, itemA, itemB, freesort_distance) %>% 
      filter(subject_id != subject) %>%
      unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
      group_by(item_pairs) %>%
      mutate(freesort_distance = mean(freesort_distance)) %>%
      ungroup() %>% 
      distinct(item_pairs, .keep_all = TRUE) %>% 
      select(-c(item_pairs, subject_id)) %>% 
      pivot_wider(names_from = itemB, values_from = freesort_distance) %>%
      column_to_rownames("itemA") %>%
      as.matrix()
    other_avg_rdm <- other_avg_rdm[desired_order, desired_order]
    
    subject_upper <- as.numeric(subject_rdm[upper.tri(subject_rdm)])
    other_upper <- as.numeric(other_avg_rdm[upper.tri(other_avg_rdm)])
    grand_upper <- as.numeric(grand_avg_rdm[upper.tri(grand_avg_rdm)])
    
    lower_bound[i] <- cor(subject_upper, other_upper, method = metric) 
    upper_bound[i] <- cor(subject_upper, grand_upper, method = metric) 
  }
  
  # Return average bounds
  list(
    upper_bound = mean(upper_bound, na.rm = TRUE),
    lower_bound = mean(lower_bound, na.rm = TRUE)
  )
}

calculate_causal_pairs_noise_ceiling <- function(data, subjects, desired_order, metric = "kendall") {
  #Initialize storage for correlations
  upper_tri_upper_bound <- numeric(length(subjects))
  upper_tri_lower_bound <- numeric(length(subjects))
  
  lower_tri_upper_bound <- numeric(length(subjects))
  lower_tri_lower_bound <- numeric(length(subjects))
  
  #Loop through each subject
  for (i in seq_along(subjects)) {
    subject <- subjects[i]
    
    #subject's RDM
    subject_rdm <- data %>%
        filter(subject_id == subject) %>%
        select(subject_id, itemA, itemB, causal_pairs_distance) %>% 
        pivot_wider(names_from = itemB, values_from = causal_pairs_distance) %>%
        column_to_rownames("itemA") %>%
        as.matrix()
    subject_rdm <- subject_rdm[desired_order, desired_order]
    
    #grand average RDM
    grand_avg_rdm <- data %>%
        select(subject_id, itemA, itemB, causal_pairs_distance) %>% 
        unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
        group_by(item_pairs) %>%
        mutate(causal_pairs_distance = mean(causal_pairs_distance)) %>%
        ungroup() %>% 
        distinct(item_pairs, .keep_all = TRUE) %>% 
        select(-c(item_pairs, subject_id)) %>% 
        pivot_wider(names_from = itemB, values_from = causal_pairs_distance) %>%
        column_to_rownames("itemA") %>%
        as.matrix()
    grand_avg_rdm <- grand_avg_rdm[desired_order, desired_order]
    
    #other subjects' average RDM
    other_avg_rdm <- data %>%
      select(subject_id, itemA, itemB, causal_pairs_distance) %>% 
      filter(subject_id != subject) %>%
      unite("item_pairs", itemA, itemB, sep = "_", remove = FALSE) %>% 
      group_by(item_pairs) %>%
      mutate(causal_pairs_distance = mean(causal_pairs_distance)) %>%
      ungroup() %>% 
      distinct(item_pairs, .keep_all = TRUE) %>% 
      select(-c(item_pairs, subject_id)) %>% 
      pivot_wider(names_from = itemB, values_from = causal_pairs_distance) %>%
      column_to_rownames("itemA") %>%
      as.matrix()
    other_avg_rdm <- other_avg_rdm[desired_order, desired_order]
    
    #upper tri noise ceiling
    subject_upper <- as.numeric(subject_rdm[upper.tri(subject_rdm)])
    other_upper <- as.numeric(other_avg_rdm[upper.tri(other_avg_rdm)])
    grand_upper <- as.numeric(grand_avg_rdm[upper.tri(grand_avg_rdm)])

    upper_tri_lower_bound[i] <- cor(subject_upper, other_upper, method = metric)
    upper_tri_upper_bound[i] <- cor(subject_upper, grand_upper, method = metric)

    #lower tri noise ceiling
    subject_lower <- as.numeric(subject_rdm[lower.tri(subject_rdm)])
    other_lower <- as.numeric(other_avg_rdm[lower.tri(other_avg_rdm)])
    grand_lower <- as.numeric(grand_avg_rdm[lower.tri(grand_avg_rdm)])
    
    lower_tri_lower_bound[i] <- cor(subject_lower, other_lower, method = metric)
    lower_tri_upper_bound[i] <- cor(subject_lower, grand_lower, method = metric)

  }
  
  #return average bounds
  list(
    upper_tri_upper_bound = mean(upper_tri_upper_bound, na.rm = TRUE),
    upper_tri_lower_bound = mean(upper_tri_lower_bound, na.rm = TRUE),
    
    lower_tri_upper_bound = mean(lower_tri_upper_bound, na.rm = TRUE),
    lower_tri_lower_bound = mean(lower_tri_lower_bound, na.rm = TRUE)
  )
}



###============================ Rdm correlation function ============================ ###


extract_upper_tri <- function(matrix) {
  matrix[upper.tri(matrix)]
}

compute_rdm_correlation <- function(data, emp_col, model_col, desired_order, method = "kendall") {
  rdm1 <- data %>%
    select(itemA, itemB, {{ emp_col }}) %>%
    pivot_wider(names_from = itemB, values_from = {{ emp_col }}) %>%
    column_to_rownames("itemA") %>%
    as.matrix()
  
  rdm2 <- data %>%
    select(itemA, itemB, {{ model_col }}) %>%
    pivot_wider(names_from = itemB, values_from = {{ model_col }}) %>%
    column_to_rownames("itemA") %>%
    as.matrix()
  
  rdm1 <- rdm1[desired_order, desired_order]
  rdm2 <- rdm2[desired_order, desired_order]
  
  diag(rdm1) <- NA
  diag(rdm2) <- NA
  
  upper_rdm1 <- extract_upper_tri(rdm1)
  upper_rdm2 <- extract_upper_tri(rdm2)
  
  cor(upper_rdm1, upper_rdm2, method = method, use = "complete.obs")
}

```

### Sorting Task noise ceiling

```{r}
d_freesort_correlations <- df_combined %>%
  left_join(d_model_predictions, by = c("itemA", "itemB")) %>%
  group_by(subject_id) %>%
  mutate(
    `model1_mind_action_body` = compute_rdm_correlation(pick(everything()), freesort_distance, `model1_mind_action_body`, desired_order),
    `model2_fine_grained` = compute_rdm_correlation(pick(everything()), freesort_distance, `model2_fine_grained`, desired_order),
    `model3_psychological_physical` = compute_rdm_correlation(pick(everything()), freesort_distance, `model3_psychological_physical`, desired_order),
    `model4_use_embeddings` = compute_rdm_correlation(pick(everything()), freesort_distance, `model4_use_embeddings`, desired_order),
    `5_causal_judgments` = compute_rdm_correlation(pick(everything()), freesort_distance, `causal_pairs_distance`, desired_order)
  ) %>%
  ungroup() %>%
  relocate(causal_pairs_distance, .after = "freesort_distance")

subjects_freesort <- unique(d_freesort_correlations$subject_id)
noise_ceiling_sorting <- calculate_freesort_noise_ceiling(d_freesort_correlations, subjects_freesort, desired_order)
noise_ceiling_sorting

```

### Causal Pairs Task noise ceiling

```{r}
d_causal_pairs_correlations <- df_combined %>%
  left_join(d_model_predictions, by = c("itemA", "itemB")) %>% 
  group_by(subject_id) %>%
  mutate(
    `model1_mind_action_body` = compute_rdm_correlation(pick(everything()), causal_pairs_distance, `model1_mind_action_body`, desired_order),
    `model2_fine_grained` = compute_rdm_correlation(pick(everything()), causal_pairs_distance, `model2_fine_grained`, desired_order),
    `model3_psychological_physical` = compute_rdm_correlation(pick(everything()), causal_pairs_distance, `model3_psychological_physical`, desired_order),
    `model4_use_embeddings` = compute_rdm_correlation(pick(everything()), causal_pairs_distance, `model4_use_embeddings`, desired_order),
    `5_causal_judgments` = compute_rdm_correlation(pick(everything()), causal_pairs_distance, `causal_pairs_distance`, desired_order)
  ) %>%
  ungroup() #%>% 
  # distinct(subject_id, RDM_type, tau) #added 5/7/26

# Compute noise ceiling for all subjects
subjects_causal_pairs <- unique(d_causal_pairs_correlations$subject_id)
noise_ceiling_causal_pairs <- calculate_causal_pairs_noise_ceiling(d_causal_pairs_correlations,subjects_causal_pairs, desired_order)
noise_ceiling_causal_pairs

```

# Confirmatory Findings - Model Correlations 

## Linear models describing Freesort 

```{r}
freesort_correlations <- d_freesort_correlations %>% 
  rename("mind_action_physiology_model" = `model1_mind_action_body`,
         "finegrained_mind_action_physiology_model" = `model2_fine_grained`,
         "physical_psychological_model" = `model3_psychological_physical`,
         "use_phrase_embeddings_model" = `model4_use_embeddings`) %>% 
  pivot_longer(
    cols = c("mind_action_physiology_model":"use_phrase_embeddings_model"),
    names_to = "RDM_type",
    values_to = "tau"
  ) %>%
  select(subject_id, itemA, itemB, domain_itemA, domain_itemB, 
         trial_type_order, freesort_distance, causal_pairs_distance, RDM_type, tau) %>% 
  mutate(
    RDM_type = as.factor(RDM_type), 
    RDM_type = relevel(RDM_type, ref = "mind_action_physiology_model") 
  ) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  distinct(subject_id, RDM_type, .keep_all = TRUE) %>%
  select(subject_id, RDM_type, tau)

#Note: mind action physiology is reference model. Estimates are mean kendall's taus
model_freesort <- lmerTest::lmer(tau ~ RDM_type + (1 | subject_id), 
              data = freesort_correlations)

summary(model_freesort)

confint(model_freesort)


##======================== Freesort Model table for SI ======================##

model_freesort_table <- model_parameters(model_freesort,
                                         ci = 0.95,
                                         # standardize = "refit")
                                         standardize = NULL) #do not standardize

model_freesort_table <- model_freesort_table %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))

model_freesort_table

model_freesort_table %>%
  flextable() %>%
  save_as_docx(path = "model_tables/model_freesort_table.docx")

```

## Linear models describing Causal Pairs data 

```{r}
causal_pairs_correlations <- d_causal_pairs_correlations %>% 
  rename("mind_action_physiology_model" = `model1_mind_action_body`,
         "finegrained_mind_action_physiology_model" = `model2_fine_grained`,
         "physical_psychological_model" = `model3_psychological_physical`,
         "use_phrase_embeddings_model" = `model4_use_embeddings`) %>% 
  pivot_longer(
    cols = c("mind_action_physiology_model":"use_phrase_embeddings_model"),
    names_to = "RDM_type",
    values_to = "tau"
  ) %>%
  select(subject_id, itemA, itemB, domain_itemA, domain_itemB, trial_type_order, freesort_distance, causal_pairs_distance, RDM_type, tau) %>% 
  mutate(RDM_type = as.factor(RDM_type), 
         RDM_type = relevel(RDM_type, ref = "mind_action_physiology_model")) %>% 
  mutate(subject_id = as.factor(subject_id)) %>% 
  distinct(subject_id, RDM_type, .keep_all = TRUE) %>% #summarize to 1 row per subject per model
  select(subject_id, RDM_type, tau)

#Note: mind action physiology is reference model. Estimates are mean kendall's taus
model_causal_pairs <- lmerTest::lmer(tau ~ RDM_type + (1 | subject_id), 
              data = causal_pairs_correlations)

summary(model_causal_pairs)

confint(model_causal_pairs)

##======================== Causal pairs model table for SI====================##

model_causal_pairs_table <- model_parameters(model_causal_pairs,
                                         ci = 0.95,
                                         standardize = NULL) #do not standardize

model_causal_pairs_table <- model_causal_pairs_table %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))

model_causal_pairs_table

model_causal_pairs_table %>%
  flextable() %>%
  save_as_docx(path = "model_tables/model_causal_pairs_table.docx")


```

## Linear model comparing best model of Freesort (MAP) to Causal Pairs Task

```{r}
causal_pairs_subject_level <- causal_pairs_correlations %>% 
  mutate(task = "Causal Pairs")

freesort_subject_level <- freesort_correlations %>% 
  mutate(task = "Sorting")

combined_taus <- bind_rows(causal_pairs_subject_level,
                           freesort_subject_level) %>% 
  mutate(task = factor(task),
         task = relevel(task, ref = "Sorting")) %>% 
  mutate(RDM_type = as.character(RDM_type)) %>% 
  filter(RDM_type == "mind_action_physiology_model")

model_taus <- lmerTest::lmer(tau ~ task + (1 | subject_id),
                             data = combined_taus)

summary(model_taus)

standardize_parameters(model_taus) #NB: intercept is comparison to grand mean, slope is comparison to intercept

# Manual standardization
# standardized_data <- combined_data %>% 
#   mutate(mean_tau = mean(tau), #grand mean
#          sd_tau = sd(tau)) %>% 
#   ungroup() %>% 
#   rowwise() %>% 
#   mutate(z_scored_taus = (tau - mean_tau) / sd_tau)
# 
# model_standardized_data <- lmerTest::lmer(z_scored_taus ~ task + (1 | subject_id),
#                data = standardized_data)
# 
# summary(model_standardized_data)

## =============== model table for SI ================ ##

model_taus_table <- model_parameters(model_taus,
                                         ci = 0.95,
                                         standardize = "refit") #do not standardize

model_taus_table <- model_taus_table %>%
  mutate(across(where(is.numeric), ~ round(.x, 2)))

model_taus_table

model_taus_table %>%
  flextable() %>%
  save_as_docx(path = "model_tables/model_taus_table.docx")

```

## Reshape correlations

```{r}
aggregated_freesort_correlations <- d_freesort_correlations %>% 
  rename("3 Category" = `model1_mind_action_body`,
         "6 Category" = `model2_fine_grained`,
         "2 Category" = `model3_psychological_physical`,
         "Cosine Similarity" = `model4_use_embeddings`) %>% 
  pivot_longer(
    cols = c("2 Category", "3 Category", "6 Category", "Cosine Similarity"),
    names_to = "correlation_type",
    values_to = "correlation_value"
  ) %>%
  group_by(subject_id, correlation_type) %>%
  summarize(mean_correlation = mean(correlation_value, na.rm = TRUE), .groups = "drop") %>% 
  mutate(method = "Sorting Task")

aggregated_causal_pairs_correlations <- d_causal_pairs_correlations %>% 
  rename("3 Category" = `model1_mind_action_body`,
         "6 Category" = `model2_fine_grained`,
         "2 Category" = `model3_psychological_physical`,
         "Cosine Similarity" = `model4_use_embeddings`) %>% 
  pivot_longer(
    cols = c("2 Category", "3 Category", "6 Category", "Cosine Similarity"),
    names_to = "correlation_type",
    values_to = "correlation_value"
  ) %>%
  group_by(subject_id, correlation_type) %>%
  summarize(mean_correlation = mean(correlation_value, na.rm = TRUE), .groups = "drop") %>% 
  mutate(method = "Causal Pairs Task")

#combine both corrs into one
d_combined_correlations <- bind_rows(aggregated_freesort_correlations, aggregated_causal_pairs_correlations) %>% 
  mutate(method = factor(method, levels = c("Sorting Task", "Causal Pairs Task")))

# d_freesort_correlations <- d_combined_correlations %>% 
#   mutate(method = as.character(method)) %>% 
#   filter(method == "Sorting Task")

```


## T-tests of correlations

This compared correlations to 0.

```{r}
t_test_results <- d_combined_correlations %>%
  group_by(method, correlation_type) %>%
  summarise(
    mean_mean_correlation = mean(mean_correlation, na.rm = TRUE),

    test = list(t.test(mean_correlation, mu = 0)),
    
    t_value = test[[1]]$statistic,
    p_value = test[[1]]$p.value,
    ci_low  = test[[1]]$conf.int[1],
    ci_high = test[[1]]$conf.int[2],
    
    .groups = "drop"
  ) %>%
  select(-test)

print(t_test_results)

```

# Confirmatory Findings - Model Correlation - Figures

## Figure S2: RSA Model Correlations

```{r, fig.height = 10, fig.width = 12}
bar_plot <- ggplot(d_combined_correlations, 
                   aes(x = reorder(correlation_type, mean_correlation, FUN = function(x) -mean(x)), 
                        y = mean_correlation, fill = method)) +
  stat_summary(
    fun = "mean",
    geom = "bar",
    position = "dodge",  
    color = "black"
  ) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.3,
    position = position_dodge(width = 0.9), 
    color = "black"
  ) +
  geom_point(aes(color = method), alpha = 0.3, size = 3, position = position_jitterdodge(jitter.width = 0.2)) +
  scale_fill_manual(values = c("Sorting Task" = "grey80", "Causal Pairs Task" = "#000000")) + #bar fill
  scale_color_manual(values = c("Sorting Task" = "darkgray", "Causal Pairs Task" = "#4A4A4A")) + #point colors
  
  geom_hline(yintercept = noise_ceiling_sorting$upper_bound, color = "darkgray", linetype = "dashed", linewidth = 0.5) +
  geom_hline(yintercept = noise_ceiling_sorting$lower_bound, color = "darkgray", linetype = "dashed", linewidth = 0.5) +
  geom_hline(yintercept = noise_ceiling_causal_pairs$upper_tri_upper_bound, color = "black", linetype = "dashed", linewidth = 0.5) +
  geom_hline(yintercept = noise_ceiling_causal_pairs$upper_tri_lower_bound, color = "black", linetype = "dashed", linewidth = 0.5) +
  theme_cowplot() +
  # ylim(-0.5, 0.5) +
  scale_y_continuous(limits = c(-0.5, 0.5), breaks = seq(-0.5, 0.5, by = 0.1)) +
  theme(
    panel.background = element_rect(fill = NA, color = NA),
    plot.background = element_rect(fill = NA, color = NA),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 16),
    axis.ticks.length = unit(.25, "cm"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 18),
    legend.position = "top",
    legend.title = element_blank(),
    plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
    plot.margin = margin(t = 10, r = 10, b = 20, l = 20)
  ) +
  labs(
    y = "Kendall's Tau Correlations",
    title = "Comparison of Theoretical and Empirical RDM Correlations"
  )

# Load and create RDM images
rdm_2_category <- ggdraw() + draw_image(paste0(rdms_input_path, "/model_4.png"), scale = 1.2)
rdm_3_category <- ggdraw() + draw_image(paste0(rdms_input_path, "/model_2.png"), scale = 1.2)
rdm_6_category <- ggdraw() + draw_image(paste0(rdms_input_path, "/model_3.png"), scale = 1.2)
rdm_cosine <- ggdraw() + draw_image(paste0(rdms_input_path, "/model_1.png"), scale = 1.2)

rdm_row <- rdm_3_category + rdm_6_category + rdm_2_category + rdm_cosine +
  plot_layout(ncol = 4)
# 
# plot_correlations <- bar_plot / rdm_row + 
#   plot_layout(heights = c(5, 2)) #adjusts height ratio


plot_correlations <- bar_plot / rdm_row +
  plot_layout(heights = c(5, 2)) &
  theme(plot.background = element_rect(fill = NA, color = NA))

plot_correlations

# ggsave(
#   filename = "figures/rdm_correlation_plot.pdf",
#   plot = plot_correlations,
#   device = "pdf",
#   #path = "path/to/directory",
#   width = 12,
#   height = 5,
#   units = "in"
# )

#this is the chunk to run:
ggsave(
  filename = "figures/correlations/rdm_correlation_plot.png", 
  plot = plot_correlations,
  device = "png",
  width = 12,
  height = 6,
  units = "in",
  dpi = 300,
  bg = "transparent" 
)

```

# Checkpoint: Read back in csvs

```{r}
#inputs
df_combined <- read_csv(paste0(snapshots_output_path, "/df_combined.csv"))

```

# Exploratory Findings - Order effects Freesort task 

## Generate Freesort rdms

```{r}
#mean helper functions
mean_freesort_rdm <- function(data, subjects) {

  data %>%
    filter(subject_id %in% subjects) %>%
    group_by(itemA, itemB) %>%
    summarise(mean_distance = mean(freesort_distance),
              .groups = "drop")
}

#split into individual rdms
df_freesort_rdm_freesort_first <- df_combined %>%
  select(-causal_pairs_distance) %>% 
  filter(trial_type_order == "causal_pairs_second")

df_freesort_rdm_freesort_second <- df_combined %>%
  select(-causal_pairs_distance) %>% 
  filter(trial_type_order == "causal_pairs_first")

#grab unique subjects 
first_subjects <- sort(unique(df_freesort_rdm_freesort_first$subject_id)) #same as for causal pairs rdm
second_subjects <- sort(unique(df_freesort_rdm_freesort_second$subject_id))

#grab odd & even subjects
first_odd_subjects <- first_subjects[c(TRUE, FALSE)]
first_even_subjects <- first_subjects[c(FALSE, TRUE)]

second_odd_subjects <- second_subjects[c(TRUE, FALSE)]
second_even_subjects <- second_subjects[c(FALSE, TRUE)]

#build the 4 mean rdms
freesort_task_first_odd <- mean_freesort_rdm(df_freesort_rdm_freesort_first, 
                                 first_odd_subjects)
freesort_task_first_even <- mean_freesort_rdm(df_freesort_rdm_freesort_first, 
                                 first_even_subjects)

freesort_task_second_odd <- mean_freesort_rdm(df_freesort_rdm_freesort_second, 
                                   second_odd_subjects)
freesort_task_second_even <- mean_freesort_rdm(df_freesort_rdm_freesort_second, 
                                   second_even_subjects)

#view one of the rdms as example:
freesort_task_first_odd
# freesort_task_first_even
# freesort_task_second_odd
# freesort_task_second_even

```

## Compute Odd-even split correlations

```{r}
#correlation function
rdm_tau <- function(first_rdm, second_rdm) {

  merged_rdm <- first_rdm %>%
    inner_join(second_rdm,
               by = c("itemA", "itemB"),
               suffix = c("_first", "_second"))

  cor(merged_rdm$mean_distance_first,
      merged_rdm$mean_distance_second,
      method = "kendall")
}

#within-order split-half similarities
within_first_tau <- rdm_tau(freesort_task_first_odd,
                            freesort_task_first_even)

within_second_tau <- rdm_tau(freesort_task_second_odd,
                             freesort_task_second_even)

#cross-order similarities 
cross_order_tau_1 <- rdm_tau(freesort_task_first_odd,
                             freesort_task_second_odd)

cross_order_tau_2 <- rdm_tau(freesort_task_first_odd,
                             freesort_task_second_even)

cross_order_tau_3 <- rdm_tau(freesort_task_first_even,
                             freesort_task_second_odd)

cross_order_tau_4 <- rdm_tau(freesort_task_first_even, 
                             freesort_task_second_even)


freesort_task_order_correlations <- tibble(freesort_comparison = c(
                                            "within_first_odd_even", "within_second_odd_even",
                                            "cross_order_first_odd_second_odd", 
                                            "cross_order_first_odd_second_even",
                                            "cross_order_first_even_second_odd", 
                                            "cross_order_first_even_second_even"),
                                           freesort_comparison_type = c(rep("within", 2), 
                                                               "cross_within",
                                                               "cross-cross",
                                                               "cross-cross",
                                                               "cross-within"),
                                           tau = c(
                                            within_first_tau, within_second_tau,
                                            cross_order_tau_1, cross_order_tau_2,
                                            cross_order_tau_3, cross_order_tau_4)) %>% 
  group_by(freesort_comparison_type) %>% 
  mutate(mean_comparison_type_tau = mean(tau)) %>% 
  ungroup()

freesort_task_order_correlations 

write.csv(freesort_task_order_correlations, paste0(snapshots_output_path, "/freesort_task_order_correlations.csv"), row.names = F)

```

# Exploratory Findings - Order effects Causal Pairs task 

## Generate Causal Pairs RDMs

```{r}
#mean helper function
mean_causal_pairs_rdm <- function(data, subjects) {

  data %>%
    filter(subject_id %in% subjects) %>%
    group_by(itemA, itemB) %>%
    summarise(mean_distance = mean(causal_pairs_distance),
              .groups = "drop")
}

#split into individual rdms
df_causal_pairs_rdm_freesort_first <- df_combined %>%
  select(-freesort_distance) %>%
  filter(trial_type_order == "causal_pairs_second")

df_causal_pairs_rdm_freesort_second <- df_combined %>%
  select(-freesort_distance) %>%
  filter(trial_type_order == "causal_pairs_first")

#grab unique subjects
first_subjects <- sort(unique(df_causal_pairs_rdm_freesort_first$subject_id))
second_subjects <- sort(unique(df_causal_pairs_rdm_freesort_second$subject_id))

first_odd_subjects <- first_subjects[c(TRUE, FALSE)]
first_even_subjects <- first_subjects[c(FALSE, TRUE)]

second_odd_subjects <- second_subjects[c(TRUE, FALSE)]
second_even_subjects <- second_subjects[c(FALSE, TRUE)]

#build the 4 mean rdms
causal_pairs_task_first_odd <- mean_causal_pairs_rdm(
  df_causal_pairs_rdm_freesort_first,
  first_odd_subjects)

causal_pairs_task_first_even <- mean_causal_pairs_rdm(
  df_causal_pairs_rdm_freesort_first,
  first_even_subjects)

causal_pairs_task_second_odd <- mean_causal_pairs_rdm(
  df_causal_pairs_rdm_freesort_second,
  second_odd_subjects)

causal_pairs_task_second_even <- mean_causal_pairs_rdm(
  df_causal_pairs_rdm_freesort_second,
  second_even_subjects)

#view one of the rdms as example:
causal_pairs_task_first_odd
# causal_pairs_task_first_even
# causal_pairs_task_second_odd
# causal_pairs_task_second_even

```

## Odd-even split correlations

```{r}
#within-order split-half similarities
within_first_tau <- rdm_tau(causal_pairs_task_first_odd,
                            causal_pairs_task_first_even)

within_second_tau <- rdm_tau(causal_pairs_task_second_odd,
                             causal_pairs_task_second_even)

#cross-order similarities 
cross_order_tau_1 <- rdm_tau(causal_pairs_task_first_odd,
                             causal_pairs_task_second_odd)

cross_order_tau_2 <- rdm_tau(causal_pairs_task_first_odd,
                             causal_pairs_task_second_even)

cross_order_tau_3 <- rdm_tau(causal_pairs_task_first_even,
                             causal_pairs_task_second_odd)

cross_order_tau_4 <- rdm_tau(causal_pairs_task_first_even, 
                             causal_pairs_task_second_even)


causal_task_order_correlations <- tibble(causal_comparison = c(
                                            "within_first_odd_even", "within_second_odd_even",
                                            "cross_order_first_odd_second_odd", 
                                            "cross_order_first_odd_second_even",
                                            "cross_order_first_even_second_odd", 
                                            "cross_order_first_even_second_even"),
                                           causal_comparison_type = c(rep("within", 2), 
                                                               "cross_within",
                                                               "cross-cross",
                                                               "cross-cross",
                                                               "cross-within"),
                                           tau = c(
                                            within_first_tau, within_second_tau,
                                            cross_order_tau_1, cross_order_tau_2,
                                            cross_order_tau_3, cross_order_tau_4)) %>% 
  group_by(causal_comparison_type) %>% 
  mutate(mean_comparison_type_tau = mean(tau)) %>% 
  ungroup()

causal_task_order_correlations 

```

# THE END

```{r}

```

