---
title: "study 2"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
date: "2025-08-22"
author: ""
---

# ReadMe

This is the analysis for the counterfactual study of the MBC project.
The study had N = 105 (before exclusions), and subjects saw two conditions: Intervention and Similarity, with 15 trials per condition.

# Set options

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
pacman::p_load(
               lme4, 
               lmerTest,
               here, 
               patchwork, 
               cowplot, 
               viridis, 
               effects, 
               conflicted,
               gt,
               webshot2,
               knitr,
               performance,
               tidyverse,
               simr)

walk(c("select", "filter", "rename", "mutate", "summarise", "summarize"), ~ conflict_prefer(.x, "dplyr"))
conflicts_prefer(simr::fixed)
sessionInfo()

```

# Global variables

```{r}
base_path <- here("code", "main")
freesort_and_causal_distances_df_path <- paste0(base_path,
                                                "/analysis/study1-measure-main-and-pilot/snapshots_study1_main_analysis/freesort_minus_causals.csv")

```

# Study 3 - Counterfactuals

# Prepare data

## Read data

```{r, warnings = FALSE}
data_path_cf <- paste0(base_path, "/data/counterfactuals/JO-mbc-main-study2-counterfactuals-105N")

desired_order <- c("see something", "hear something", "choose what to do", 
                   "remember something", "think about something", "reach for something", 
                   "sit down", "jump up and down", "kick something", "take a walk", 
                   "get tired", "become hungry", "feel scared", "experience pain", "get sick")

file_paths <- list.files(path = data_path_cf, pattern = "^2025-", full.names = TRUE)

d <- imap_dfr(file_paths, ~ {
  read_csv(.x, col_types = cols(response = col_character())) %>%
    mutate(
      filename = basename(.x),
      subject_id = paste0("subj_", str_pad(.y, 2, pad = "0"))
    )}) %>%
  select(-c(mturk_participant_id, mturk_assignment_id, mturk_project_id)) %>%
  relocate(subject_id, .before = "success")

```

## Demographics

```{r}
# demographics
df_demographics <- d %>% 
  filter(trial_id == "demographics_survey") %>% 
  select("trial_id", "filename", 
         "feedback", "age", "ethnicity", "gender", "race") 

summary(df_demographics$age)
table(df_demographics$gender)
table(df_demographics$ethnicity)
table(df_demographics$race)

```

## Wrangle data

initial: 30 trials * 48 subjects = 1440 rows.
dat: (30 trials / 2 trials per row) * 48 subjects = 720 rows.

TODO: rename itemB to target item.

```{r}
subjects_to_exclude <- d %>%
  filter(grepl("attention_check", condition)) %>% 
  filter(attn_correct == "no") %>% 
  pull(subject_id) %>% 
  unique()

print(subjects_to_exclude)

dat <- d %>% 
  filter(!subject_id %in% subjects_to_exclude) %>%
  filter(condition %in% c("counterfactual", "similarity")) %>% 
  mutate(condition = ifelse(condition == "counterfactual", "causal", condition)) %>% #meant to call it causal (both are counterfactuals)
  mutate(response = as.factor(response)) %>% 
  mutate(condition = as.factor(condition)) %>% 
  select(-condition) %>% 
  select(subject_id, itemB, causal_itemA, similar_itemA, response_value) %>% 
  mutate(causal_itemA = factor(causal_itemA, levels = desired_order), #this col has unique values; we're assigning 15 lvls
         similar_itemA = factor(similar_itemA, levels = desired_order), #this col has unique values; we're assigning 15 lvls
         itemB = factor(itemB, levels = desired_order)) %>% 
  # filter(subject_id == "subj_01" & itemB == "see something") %>% 
  mutate(item_type = case_when(
        !is.na(causal_itemA) ~ "causal_itemA",
        !is.na(similar_itemA) ~ "similar_itemA"),
        item = coalesce(as.character(causal_itemA), as.character(similar_itemA))) %>% 
  select(-causal_itemA, -similar_itemA) %>% 
  pivot_wider(names_from = item_type,
              values_from = c(item, response_value)) %>% 
  rename("causal_itemA" = item_causal_itemA,
         "similar_itemA" = item_similar_itemA, 
         "causal_itemA_counterfactual" = response_value_causal_itemA,
         "similar_itemA_counterfactual" = response_value_similar_itemA) 

rmarkdown::paged_table(dat)

n_subjects <- dat %>%
  distinct(subject_id) %>% 
  summarize(n_subjects = n())

n_subjects 

```

# Plot dv vs conditions

## Prepare to plot

```{r}
dat_plot <- dat %>% 
  rename("causal" = causal_itemA_counterfactual,
         "similar" = similar_itemA_counterfactual) %>% 
  pivot_longer(cols = c("causal", "similar"), 
               names_to = "counterfactual_type",
               values_to = "likelihood") 

```

## Plot dv vs counterfactual type

figure for spp poster 2025

```{r, fig.width = 4, fig.height = 5.5}
main_fig <- 
dat_plot %>% 
  mutate(counterfactual_type = ifelse(counterfactual_type == "similar", "Latent", "Direct")) %>% 
  mutate(counterfactual_type = factor(counterfactual_type, levels = c("Direct", "Latent"))) %>% 
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  labs(y = "Likelihood of Counterfactual", 
       x = "Preceding Item Type",
       #fill = "Preceding Item Type"
       ) +
  scale_x_discrete(labels = c("counterfactual" = "Causal", "similarity" = "Similar")) +
  theme_cowplot() +
  scale_fill_manual(values = c("#000000", "grey80")) + 
  theme(axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_blank(),
        legend.position = "none",

        
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)#,
        ) +
  ylim(0, 100)

main_fig

# main_fig <- ggsave(paste0(base_path, "/analysis/study2-counterfactuals/figures/main_counterfactuals.png"), width = 5, height = 5, plot = main_fig, bg = "transparent")
main_fig <- ggsave(paste0(base_path, "/analysis/study2-counterfactuals/figures/main_counterfactuals_white.png"), width = 5, height = 5, plot = main_fig, bg = "white")

```

# Figure for spp 2026

```{r, fig.width = 4, fig.height = 5}
spp_26 <- dat_plot %>% 
  mutate(counterfactual_type = factor(counterfactual_type, 
                                      levels = c("similar", "causal"))) %>% 
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  # geom_hline(yintercept = 50, linetype = "dashed") +
  labs(y = "Counterfactual Likelihood", 
       x = "Preceding Item Type",
       ) +
  scale_x_discrete(labels = c(similar = "Latent", 
                              causal = "Direct")) +
  theme_cowplot() +
  scale_fill_manual(values = c("grey80", "#000000")) + 
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25,
                                    hjust = 1),
        axis.title.y = element_text(size = 25),
        legend.position = "none",
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)#,
        ) +
  ylim(0, 100)

spp_26 

# spp_26 <- ggsave(paste0(base_path,
#                           "/analysis/study2-counterfactuals/figures/spp_26.png"), 
#                    width = 5, height = 5, 
#                    plot = spp_26, bg = "white")

ggsave(paste0(base_path,
                          "/analysis/study2-counterfactuals/figures/spp_26.svg"), 
       plot = spp_26,
       device = svglite::svglite,
       width = 4,
       height = 5,
       units = "in"
)

```

# figure with slope

```{r}
dat_plot <- dat %>% 
  rename("causal" = causal_itemA_counterfactual,
         "similar" = similar_itemA_counterfactual) %>% 
  pivot_longer(cols = c("causal", "similar"), 
               names_to = "counterfactual_type",
               values_to = "likelihood") 

rmarkdown::paged_table(dat_plot)

dat_trial_mean <- dat_plot %>% 
  unite("joined", c(itemB, causal_itemA, similar_itemA), sep = "_") %>% 
  group_by(counterfactual_type, joined) %>% 
  summarize(mean_likelihood = mean(likelihood)) 


dat_trial_mean_plot <- dat_trial_mean %>% 
  mutate(counterfactual_type = factor(counterfactual_type, 
                                      levels = c("similar", "causal"))) 

rmarkdown::paged_table(dat_trial_mean_plot)

dat_trial_mean_plot %>% 
  ggplot(aes(x = counterfactual_type, y = mean_likelihood, fill = counterfactual_type)) +
  stat_summary(fun.data = mean_se, geom = "bar", color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  geom_point(alpha = 0.9, color = "darkgray") +
  geom_line(aes(group = joined), alpha = 0.9, color = "darkgray") +
  labs(y = "Counterfactual Likelihood", 
       x = "Preceding Item Type",
       fill = "Counterfactual Type") +
  scale_x_discrete(labels = c(similar = "Latent", 
                              causal = "Direct")) +
  theme_cowplot() +
  scale_fill_manual(values = c("grey80", "#000000")) + 
  theme(
        axis.text.x = element_text(size = 25),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 25),
        legend.position = "top",
        legend.title = element_text(size = 25),
        legend.text = element_text(size = 25),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA)#,
        ) +
  ylim(0, 100)


```


## Plot, facet by target items

```{r, fig.width = 12, fig.height = 12}
dat_plot_long <- dat_plot %>%
  pivot_longer(cols = c("causal_itemA", "similar_itemA"),
               names_to = "item_type",
               values_to = "item") %>%
  mutate(counterfactual_type = ifelse(counterfactual_type == "causal", "Direct", "Latent")) %>% 
  group_by(subject_id, itemB) %>%
  slice(-c(2, 3))

rmarkdown::paged_table(dat_plot_long)

label_data <- dat_plot_long %>%
  ungroup() %>% 
  distinct(itemB, counterfactual_type, item)

dat_plot_long %>%
  ggplot(aes(x = counterfactual_type, y = likelihood, fill = counterfactual_type)) +
  stat_summary(fun.data = mean_se, geom = "bar") +
  geom_jitter(width = .05, alpha = .1) +
  # stat_summary(fun = mean, geom = "point", size = 4, color = "red") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .2) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_text(data = label_data, aes(label = item), y = 95, vjust = 1, size = 3.5) +
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  # scale_x_discrete(labels = c("counterfactual" = "Causal", "similarity" = "Similar")) +
  scale_fill_manual(values = c("#000000", "grey80")) +
  theme_cowplot() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12),
    legend.position = "none") +
  facet_wrap(~itemB)

```

## Plot single subject

```{r, fig.width = 12, fig.height = 12}
dat_plot_long %>% 
  filter(subject_id == "subj_01") %>% 
  ggplot(aes(x = counterfactual_type, y = likelihood, color = counterfactual_type)) +
  geom_point() +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_text(aes(label = item), y = 95, vjust = 1, size = 3.5) +
  labs(y = "Likelihood of Occurring", x = "Counterfactual type") +
  theme_bw() +
  theme(
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        legend.position = "none") +
  facet_wrap(~itemB)

```

# Modelling

## Effect of preceding item type

```{r}
dat_model <- dat_plot %>% 
  mutate(target_likelihood = likelihood,
         preceding_item_type = relevel(
           factor(counterfactual_type),
           ref = "causal"),
         subject_id = as_factor(subject_id)
         ) %>% 
  select(-c("likelihood", "counterfactual_type")) 

#model
model_effect_of_preceding <- lmerTest::lmer(target_likelihood ~ preceding_item_type +
                                              (1|subject_id), data = dat_model)
summary(model_effect_of_preceding)
plot(allEffects(model_effect_of_preceding))
#check_model(model_effect_of_condition) #binned residual issue?

#probabilities
effects_data <- allEffects(model_effect_of_preceding)
effects_df <- as.data.frame(effects_data$preceding)
effects_df

```

## Check model

```{r}
check_model(model_effect_of_preceding)
```

# Plot dv vs distances

## Prepare append distances 

```{r}
distances <- read_csv(freesort_and_causal_distances_df_path)

dat_distances <- dat_plot_long %>% 
  ungroup() %>% 
  rename("itemA" = item) %>% 
  left_join(distances %>% 
              select(itemB, itemA, mean_causal_distance, mean_freesort_distance, freesort_minus_causal),
            by = c("itemB", "itemA")) %>% 
  mutate(mean_causal_distance = round(mean_causal_distance, 2),
         mean_freesort_distance = round(mean_freesort_distance, 2),
         freesort_minus_causal = round(freesort_minus_causal, 2)) %>% 
  mutate(itemB = factor(itemB, levels = desired_order))


# View(dat_plot_long)
```

## Plot difference scores

15 similar item - target item pairs, 15 causal item - target item pairs. 
The more causal (right of x -axis), the less likely the counterfactual event will occur

```{r, fig.width = 12}
#make separate data frame with only distances and difference scores?
#or, get the mean responses and an error bar for it?

#parcel out labels
label_distances <- dat_distances %>%
  distinct(itemB, counterfactual_type, itemA, freesort_minus_causal)
    

#plot
dat_distances %>% 
  ggplot(aes(x = freesort_minus_causal, y = likelihood, color = counterfactual_type)) +
  geom_point(alpha = .2) +
  geom_text(data = label_distances, aes(label = itemB), y = 95, vjust = .5, size = 3.5, angle = 80) +
  geom_text(data = label_distances, aes(label = itemA), y = 85, vjust = .5, size = 3.5, angle = 80) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .01, color = "black") +
  stat_summary(fun = "mean", geom = "point", shape = 1, size = 3, color = "black") +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 50, linetype = "dashed") +
  theme_bw() +
  labs(y = "Likelihood of Occurring", x = "Freesort minus Causal Distance") +
  theme_bw() +
  theme(
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12))
```

## Itemwise difference scores

```{r, fig.width = 12}
dat_distances %>% 
  ggplot(aes(x = freesort_minus_causal, y = likelihood, color = counterfactual_type)) +
  geom_point(alpha = .2) +
  geom_text(data = label_distances, aes(label = itemA), y = 90, size = 3.5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .03, color = "black") +
  stat_summary(fun = "mean", geom = "point", shape = 1, size = 2, color = "black") +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 50, linetype = "dashed") +
  theme_bw() +
  labs(y = "Likelihood of Occurring", x = "Freesort minus Causal Distance") +
  theme_bw() +
  theme(
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12)) +
  facet_wrap(~itemB)


```


## Plot individual distances

```{r, fig.width = 8}
dat_distances %>% 
  pivot_longer(cols = c("mean_causal_distance", "mean_freesort_distance"),
               names_to = "distance_type", 
               values_to = "distances") %>% 
  ggplot(aes(x = distances, y = likelihood, color = distance_type)) +
  geom_jitter(width = .01, alpha = .2) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 50, linetype = "dashed") +
  theme_bw() +
  labs(y = "Likelihood of Occurring", x = "Distance") +
  theme_bw() +
  theme(
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12)) +
  facet_wrap(~item_type)

```

# Distances analysis - real

## Append distances

```{r}
dat_plot_distances <- dat_plot %>% 
  left_join(distances %>% 
              select(itemA, itemB, mean_causal_distance, 
                     mean_freesort_distance, freesort_minus_causal) %>% 
              rename("causal_itemA" = itemA,
                     "causal_itemA_causal_distance" = mean_causal_distance,
                     "causal_itemA_freesort_distance" = mean_freesort_distance,
                     "causal_itemA_freesort_minus_causal" = freesort_minus_causal),
            by = c("itemB", "causal_itemA")) %>% 
  left_join(distances %>% 
              select(itemA, itemB, mean_causal_distance, 
                     mean_freesort_distance, freesort_minus_causal) %>% 
              rename("similar_itemA" = itemA,
                     "similar_itemA_causal_distance" = mean_causal_distance,
                     "similar_itemA_freesort_distance" = mean_freesort_distance,
                     "similar_itemA_freesort_minus_causal" = freesort_minus_causal),
            by = c("itemB", "similar_itemA")) %>% 
  mutate(causal_itemA_causal_distance = round(causal_itemA_causal_distance, 2),
         causal_itemA_freesort_distance = round(causal_itemA_freesort_distance, 2),
         causal_itemA_freesort_minus_causal = round(causal_itemA_freesort_minus_causal, 2),
         similar_itemA_causal_distance = round(similar_itemA_causal_distance, 2),
         similar_itemA_freesort_distance = round(similar_itemA_freesort_distance, 2),
         similar_itemA_freesort_minus_causal = round(similar_itemA_freesort_minus_causal, 2))

# View(dat_plot_distances)

#save data frame:
write_csv(dat_plot_distances, "dat_counterfactuals_distances.csv")

```

## Read back in data frame

```{r}
analysis_path <- here("code", "main", "analysis")

dat_plot_distances <- read_csv(paste0(analysis_path,
                "/study2-counterfactuals/dat_counterfactuals_distances.csv"))

```

## Summarize data

```{r}
dat_plot_distances_summarized <- dat_plot_distances %>% 
  group_by(itemB, causal_itemA, similar_itemA, counterfactual_type) %>% 
  mutate(mean_likelihood = mean(likelihood)) %>% 
  mutate(mean_likelihood = round(mean_likelihood, 2)) %>% 
  distinct(itemB, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(-c(subject_id, likelihood)) %>% 
  relocate(mean_likelihood, .after = counterfactual_type) %>% 
  relocate(causal_itemA_freesort_minus_causal, .after = mean_likelihood)
  
# View(dat_plot_distances_summarized)

```

# Distances - single x axis

```{r}
dat_plot_distances_summarized <- dat_plot_distances %>% 
  group_by(itemB, causal_itemA, similar_itemA, counterfactual_type) %>% 
  mutate(mean_likelihood = mean(likelihood)) %>% 
  mutate(mean_likelihood = round(mean_likelihood, 2)) %>% 
  distinct(itemB, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(-c(subject_id, likelihood)) %>% 
  relocate(mean_likelihood, .after = counterfactual_type) %>% 
  relocate(causal_itemA_freesort_minus_causal, .after = mean_likelihood)

dat_diff_distances <- dat_plot_distances_summarized %>%
  pivot_wider(names_from = counterfactual_type,
              values_from = mean_likelihood) %>% 
  mutate(mean_difference = causal - similar) %>% 
  # pivot_longer(cols = c(causal_itemA_freesort_minus_causal,
  #                       similar_itemA_freesort_minus_causal),
  #              names_to = "distance_name",
  #              values_to = "joint_distance") %>% 
  # mutate("distance_name" = ifelse(distance_name == "causal_itemA_freesort_minus_causal", 
  #                                 "causal", "similar"))
  mutate(diff_joint_distance = causal_itemA_freesort_minus_causal - similar_itemA_freesort_minus_causal)
  # mutate(diff_joint_distance = similar_itemA_freesort_minus_causal - causal_itemA_freesort_minus_causal)


dat_diff_distances %>% 
  # filter(counterfactual_type == "causal") %>% 
  ggplot(aes(y = mean_difference, x = diff_joint_distance)) +
  geom_point(alpha = .1) +
  stat_summary(fun.data = mean_se, geom = "point") +
  # stat_summary(fun.data = mean_se, geom = "errorbar", width = .001) +
  geom_smooth(method = "lm") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw() +
  labs(
  title = "Counterfactuals",
  color = "Choice Item",
  fill = "Choice Item",
  # x = "Joint Distance to Target Item\nMore similar, less causal                                                    More causal, less similar",
  # y = "Probability\nSimilar Item                                             Causal Item"
  y = "Raw mean difference (causal - similar)",
  x = "Direct item joint distance - Essential item joint distance"
  )

```

## Plot 1: Direct items only

The causal counterfactual always shows target event paired with causal item. 
So lets subset the data to show only the causals

```{r}
dat_plot_distances_summarized %>% 
  mutate(itemB = factor(itemB, levels = desired_order)) %>% 
  arrange(itemB) %>% 
  filter(counterfactual_type == "causal") %>% 
  ggplot(aes(y = mean_likelihood, x = causal_itemA_freesort_minus_causal)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood",
       x = "Freesort minus causal distance, Direct item",
       title = "Counterfactuals") +
  theme_bw()

# Plot 1, but with data points
dat_plot_distances %>% 
  filter(counterfactual_type == "causal") %>% 
  ggplot(aes(y = likelihood, x = causal_itemA_freesort_minus_causal)) +
  geom_point(alpha = .1) +
  stat_summary(fun.data = mean_se, geom = "point", color = "red") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .001) +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood",
       x = "Freesort minus causal distance, Direct item",
       title = "Counterfactuals") +
  # geom_text(label = itemB) +
  theme_bw()

```

## Plot 2: Latent items only
The similar counterfactual always shows target event paired with similar item

```{r}
dat_plot_distances_summarized %>% 
  filter(counterfactual_type == "similar") %>% 
  ggplot(aes(y = mean_likelihood, x = similar_itemA_freesort_minus_causal)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood, Latent Item ",
       x = "Freesort minus causal distance, Latent item",
       title = "Counterfactuals") +
  theme_bw()

# Plot 2, with data
dat_plot_distances %>% 
  filter(counterfactual_type == "similar") %>% 
  ggplot(aes(y = likelihood, x = similar_itemA_freesort_minus_causal)) +
  geom_point(alpha = .1) +
  stat_summary(fun.data = mean_se, geom = "point", color = "red") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .001) +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood",
       x = "Freesort minus causal distance, Latent item",
       title = "Counterfactuals") +
  # geom_text(label = itemB) +
  theme_bw()
```

## Joint Plots 
-- not sure, come back to this

```{r}
dat_plot_distances_summarized %>% 
  ggplot(aes(y = mean_likelihood, 
             x = similar_itemA_freesort_minus_causal,
             color = counterfactual_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood",
       x = "Freesort minus causal distance, Latent item",
       title = "Counterfactuals") +
  theme_bw()

dat_plot_distances_summarized %>% 
  ggplot(aes(y = mean_likelihood, 
             x = causal_itemA_freesort_minus_causal,
             color = counterfactual_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(y = "Counterfactual Likelihood",
       x = "Freesort minus causal distance, Direct item",
       title = "Counterfactuals") +
  theme_bw()

```

## Distance analysis models

```{r}
d_model_test_causal <- lmerTest::lmer(likelihood ~ causal_itemA_freesort_minus_causal +
                                        (1|subject_id), 
                                      data = dat_plot_distances %>% 
                                        filter(counterfactual_type == "causal"))

summary(d_model_test_causal)


d_model_test_similar <- lmerTest::lmer(likelihood ~ similar_itemA_freesort_minus_causal +
                                         (1|subject_id), 
                                       data = dat_plot_distances %>% 
                                         filter(counterfactual_type == "similar"))

summary(d_model_test_similar)

```

## Inspect distances dataframe 

```{r}
#only look at causals
d_test <- dat_plot_distances_summarized %>% 
  filter(counterfactual_type == "causal") %>% 
  arrange(causal_itemA_freesort_minus_causal)

d_test 
# View(d_test)
#looks fine to me
```




```{r}

```


